---
title: "Two-Stage Inference Paths in sglwqs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Two-Stage Inference Paths in sglwqs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Overview

`sglwqs` separates two related tasks:

1. estimating sparse WQS weights and directional coefficients
2. estimating downstream effect sizes for WQS composite indices

Those two layers can be combined in different ways through `bootstrap`,
`validation`, and `refit`.

This vignette summarizes what each configuration returns and where to find the
results.

## Core Output Paths

### 1. Point estimates only

Use this when you want sparse WQS weights without any uncertainty layer.

```{r}
fit <- sglwqs(
  X = X,
  y = y,
  bootstrap = FALSE,
  refit = "none"
)
```

Key outputs:

- `fit$pos_weights`, `fit$neg_weights`
- `fit$cov_coef`
- `fit$diagnostics`

### 2. Bootstrap-only summaries

Use this when you want weight stability and bootstrap summaries without running
a downstream GLM.

```{r}
fit <- sglwqs(
  X = X,
  y = y,
  bootstrap = TRUE,
  n_boot = 200,
  refit = "none"
)
```

Key outputs:

- `fit$boot_info$selection_freq_pos`, `fit$boot_info$selection_freq_neg`
- `fit$boot_info$mean_cov_coef`, `fit$boot_info$se_cov_coef`
- `fit$boot_info$mean_index_sum_pos`, `fit$boot_info$se_index_sum_pos`
- `fit$boot_info$mean_index_sum_by_group_pos`, `fit$boot_info$se_index_sum_by_group_pos`

Unified access:

```{r}
summary_inference(fit)
plot_inference_results(fit)
```

### 3. Full-data downstream GLM

Use this when `n` is too small for a validation split but you still want a
second-stage GLM with fixed WQS indices.

```{r}
fit <- sglwqs(
  X = X,
  y = y,
  refit = "full"
)
```

Key outputs:

- `fit$refit_info`
- `summary_inference(fit)`
- `plot_inference_results(fit)`

### 4. Validation-based downstream GLM

Use this when you want held-out downstream inference.

```{r}
fit <- sglwqs(
  X = X,
  y = y,
  validation = TRUE,
  train_prop = 0.6
)
```

Key outputs:

- `fit$validation_info`
- `summary_inference(fit)`
- `plot_inference_results(fit)`

## Multiple Imputation

`sglwqs_mice()` follows the same logic, but returns pooled results inside
`fit$pooled`.

```{r}
fit_mi <- sglwqs_mice(
  mids_obj = imp,
  exposure_vars = exp_vars,
  outcome_var = "y",
  bootstrap = TRUE,
  refit = "full"
)
```

Important pooled fields:

- `fit_mi$pooled$pos_weights`, `fit_mi$pooled$neg_weights`
- `fit_mi$pooled$inference`
- `fit_mi$pooled$covariates`
- `fit_mi$pooled$bootstrap_inference`

Backward-compatibility note:

- `fit_mi$pooled$validation` is retained when validation-based downstream
  inference is the active source.

## Coverage Summary

The table below summarizes the main combinations. `validation = TRUE` is
equivalent to `refit = "validation"`.

| MI | Bootstrap | Refit | Weight point estimates | Exposure / weight stability | Covariate uncertainty | WQS index uncertainty |
|----|-----------|-------|------------------------|-----------------------------|-----------------------|-----------------------|
| No | No  | none       | Yes | No  | No  | No  |
| No | Yes | none       | Yes | Bootstrap summaries | Bootstrap summaries | Bootstrap summaries |
| No | No  | full       | Yes | No  | Downstream GLM | Downstream GLM |
| No | No  | validation | Yes | No  | Downstream GLM | Downstream GLM |
| No | Yes | full       | Yes | Bootstrap summaries | Downstream GLM | Downstream GLM |
| No | Yes | validation | Yes | Bootstrap summaries | Downstream GLM | Downstream GLM |
| Yes| No  | none       | Rubin-pooled | No  | No  | No  |
| Yes| Yes | none       | Rubin-pooled | Rubin-pooled bootstrap summaries | Rubin-pooled bootstrap summaries | Rubin-pooled bootstrap summaries |
| Yes| No  | full       | Rubin-pooled | No  | Rubin-pooled downstream GLM | Rubin-pooled downstream GLM |
| Yes| No  | validation | Rubin-pooled | No  | Rubin-pooled downstream GLM | Rubin-pooled downstream GLM |
| Yes| Yes | full       | Rubin-pooled | Rubin-pooled bootstrap summaries | Rubin-pooled downstream GLM | Rubin-pooled downstream GLM |
| Yes| Yes | validation | Rubin-pooled | Rubin-pooled bootstrap summaries | Rubin-pooled downstream GLM | Rubin-pooled downstream GLM |

In practice, this means:

- `refit = "none"` with `bootstrap = TRUE` is the lightest path that still
  returns uncertainty summaries.
- `refit = "full"` is the natural small-sample alternative to a
  train/validation split.
- `summary_inference()` and `plot_inference_results()` are designed so that the
  active downstream or bootstrap-only path can be accessed through the same API.

## Diagnostics

Every fitted object also stores descriptive diagnostics.

```{r}
compute_diagnostics(fit)
compute_diagnostics(fit_mi)
```

These diagnostics report observed model characteristics such as sample-to-
predictor ratio, non-zero weight counts, bootstrap success rate, and active
inference source. They are intended as factual summaries rather than automatic
quality judgements.
