---
title: "SGL-WQS Alpha (asparse) Sensitivity Analysis"
subtitle: "Effect of Group vs Individual Sparsity Balance Across Sample Sizes"
author: "Supplementary Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 150,
  cache = TRUE
)

fig_dir <- "figures"
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)

N_BOOT <- 200
N_QUANTILES <- 4

# Grid: 4 sample sizes × 3 alphas × 10 seeds = 120 scenarios
SAMPLE_SIZES <- c(500, 1000, 5000, 10000)
ALPHAS <- c(0.05, 0.5, 0.95)  # group-heavy, balanced, individual-heavy
SEEDS <- c(71, 42, 123, 256, 314, 500, 617, 789, 888, 999,
              1001, 1123, 1234, 1357, 1500, 1618, 1729, 1847, 1963, 2048,
              2222, 2345, 2500, 2718, 2801, 3001, 3141, 3333, 3500, 3777)
N_SEEDS <- length(SEEDS)

N_WORKERS <- max(parallel::detectCores() - 1L, 1L)
cat(sprintf("Parallel workers: %d / %d cores\n", N_WORKERS, parallel::detectCores()))
```

# Overview

The sparse group lasso mixing parameter α (`asparse` in sparsegl) controls the balance between group-level (L₂) and individual-level (L₁) sparsity:

- **α → 0**: Pure group lasso. Entire groups are selected or dropped; within-group coefficients are dense.
- **α → 1**: Pure lasso. Individual variable selection only; group structure is ignored.
- **α = 0.5**: Balanced. Both group and individual sparsity operate.

The default in sparsegl (and thus SGL-WQS) is α = 0.05, emphasizing group structure. This analysis examines whether the optimal α depends on sample size.

**Grid:**

- Sample sizes: `r paste(format(SAMPLE_SIZES, big.mark=","), collapse = ", ")`
- Alpha values: `r paste(ALPHAS, collapse = ", ")`
- Seeds: `r N_SEEDS` per scenario
- Total scenarios: `r length(SAMPLE_SIZES) * length(ALPHAS) * N_SEEDS`

---

# Setup

```{r load-packages}
library(MASS)
library(sglwqs)
library(future)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(tictoc)
```

```{r data-generation}
generate_sglwqs_simdata <- function(n = 10000, seed = 71) {
  set.seed(seed)
  
  sex <- rbinom(n, 1, 0.5)
  age <- pmax(pmin(round(rnorm(n, 50, 12)), 80), 20)
  bmi <- pmax(pmin(round(22 + 0.05*age + 1.5*sex + rnorm(n, 0, 4), 1), 45), 15)
  
  cor_pcb <- matrix(c(1.00, 0.60, 0.70, 0.65, 0.60,
                      0.60, 1.00, 0.75, 0.70, 0.65,
                      0.70, 0.75, 1.00, 0.80, 0.70,
                      0.65, 0.70, 0.80, 1.00, 0.75,
                      0.60, 0.65, 0.70, 0.75, 1.00), 5, 5)
  
  pcb <- MASS::mvrnorm(n, c(3.5, 3.5, 4.0, 4.5, 3.0), 
                       diag(c(1.5, 1.5, 1.8, 2.0, 1.5)) %*% cor_pcb %*% diag(c(1.5, 1.5, 1.8, 2.0, 1.5)))
  colnames(pcb) <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
  
  cor_metal <- matrix(c(
    1.00, 0.60, 0.15, 0.10, 0.20,
    0.60, 1.00, 0.10, 0.15, 0.25,
    0.15, 0.10, 1.00, 0.55, 0.20,
    0.10, 0.15, 0.55, 1.00, 0.30,
    0.20, 0.25, 0.20, 0.30, 1.00
  ), 5, 5, byrow = TRUE)
  
  metal_raw <- MASS::mvrnorm(n, log(c(0.5, 2, 1, 100, 20)), 
                             diag(c(0.6, 0.8, 0.5, 0.3, 0.25)) %*% cor_metal %*% 
                               diag(c(0.6, 0.8, 0.5, 0.3, 0.25)))
  metal <- exp(metal_raw)
  colnames(metal) <- c("cd", "pb", "hg", "se", "mg")
  
  pfas <- pmax(MASS::mvrnorm(n, c(3, 1.5, 5), diag(c(2, 1, 3.5))), 0.1)
  colnames(pfas) <- c("PFOA", "PFNA", "PFOS")
  
  beta_pcb <- c(0.04, 0.15, 0.20, 0.08, 0.05)
  beta_metal <- c(-0.12, -0.18, +0.10, +0.14, -0.02)
  beta_pfas <- c(0, 0, 0)
  
  eta <- -3.0 + 
    scale(pcb) %*% beta_pcb + 
    scale(metal) %*% beta_metal +
    scale(pfas) %*% beta_pfas + 
    sex * 0.3 + (age - 50) / 10 * 0.02 + (bmi - 25) / 5 * 0.05
  
  Y <- rbinom(n, 1, 1 / (1 + exp(-eta)))
  
  result <- data.frame(pcb, metal, pfas, sex = sex, age = age, bmi = bmi, Y = Y)
  attr(result, "true_beta") <- list(
    pcb = setNames(beta_pcb, colnames(pcb)),
    metal = setNames(beta_metal, colnames(metal)),
    pfas = setNames(beta_pfas, colnames(pfas))
  )
  return(result)
}

# Variable definitions
PCBs <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
Metals <- c("cd", "pb", "hg", "se", "mg")
PFASs <- c("PFOA", "PFNA", "PFOS")
all_exposures <- c(PCBs, Metals, PFASs)
groups <- list(PCBs = PCBs, Metals = Metals, PFASs = PFASs)

true_directions <- data.frame(
  Variable = all_exposures,
  True_Beta = c(0.04, 0.15, 0.20, 0.08, 0.05, -0.12, -0.18, 0.10, 0.14, -0.02, 0, 0, 0),
  Group = c(rep("PCBs", 5), rep("Metals", 5), rep("PFASs", 3))
) %>%
  mutate(True_Direction = case_when(
    True_Beta > 0.01 ~ "Positive",
    True_Beta < -0.01 ~ "Negative",
    TRUE ~ "None"
  ))
```

---

# Run Analysis

```{r run-analysis, cache=TRUE}
tic("Total analysis time")

all_results <- list()
idx <- 1

for (n in SAMPLE_SIZES) {
  for (alpha in ALPHAS) {
    for (s in seq_along(SEEDS)) {
      seed <- SEEDS[s]
      cat(sprintf("n=%s, alpha=%.2f, seed=%d (%d/%d)...\n", 
                  format(n, big.mark=","), alpha, seed, s, N_SEEDS))
      
      tryCatch({
        simdata <- generate_sglwqs_simdata(n = n, seed = seed)
        
        plan(multisession, workers = N_WORKERS)
        
        sglwqs_fit <- sglwqs(
          X = simdata[, all_exposures], y = simdata$Y,
          covariates = simdata[, c("sex", "age", "bmi")],
          groups = groups, family = "binomial",
          n_quantiles = N_QUANTILES, bootstrap = TRUE,
          n_boot = N_BOOT, parallel = TRUE,
          validation = TRUE, train_prop = 0.6, seed = seed,
          asparse = alpha  # Key parameter being varied
        )
        
        plan(sequential)
        
        # --- Extract weights ---
        sw <- extract_weights(sglwqs_fit, direction = "both") %>%
          dplyr::select(Variable = variable, Weight = weight, Direction = direction) %>%
          mutate(Direction = tools::toTitleCase(Direction))
        
        # --- Direction detection ---
        sgl_dirs <- data.frame(Variable = all_exposures)
        pos_w <- sglwqs_fit$pos_weights
        neg_w <- sglwqs_fit$neg_weights
        sgl_dirs$Detected <- ifelse(pos_w[sgl_dirs$Variable] > neg_w[sgl_dirs$Variable], 
                                     "Positive", "Negative")
        sgl_dirs <- sgl_dirs %>% 
          left_join(true_directions %>% dplyr::select(Variable, True_Direction), by = "Variable")
        accuracy <- sum(sgl_dirs$Detected == sgl_dirs$True_Direction | 
                          sgl_dirs$True_Direction == "None") / nrow(sgl_dirs)
        
        # --- Group-level info ---
        grp_info <- data.frame()
        for (grp_name in names(groups)) {
          pos_idx <- sglwqs_fit$pos_index_sum_by_group[[grp_name]]
          neg_idx <- sglwqs_fit$neg_index_sum_by_group[[grp_name]]
          selected <- (!is.null(pos_idx) && pos_idx > 1e-6) || 
                      (!is.null(neg_idx) && neg_idx > 1e-6)
          
          grp_res <- sglwqs_fit$validation_info$group_results[[grp_name]]
          
          grp_info <- rbind(grp_info, data.frame(
            Group = grp_name, Selected = selected,
            Pos_Index = ifelse(is.null(pos_idx), 0, pos_idx),
            Neg_Index = ifelse(is.null(neg_idx), 0, neg_idx),
            Pos_Pvalue = if (!is.null(grp_res)) grp_res$pos_pvalue else NA,
            Neg_Pvalue = if (!is.null(grp_res)) grp_res$neg_pvalue else NA
          ))
        }
        
        # --- Lambda ---
        lambda_min <- sglwqs_fit$fit$lambda.min
        lambda_1se <- sglwqs_fit$fit$lambda.1se
        
        # --- Count non-zero variables ---
        n_nonzero_pos <- sum(sglwqs_fit$pos_weights > 1e-6)
        n_nonzero_neg <- sum(sglwqs_fit$neg_weights > 1e-6)
        
        all_results[[idx]] <- list(
          n = n, alpha = alpha, seed = seed,
          weights = sw,
          accuracy = accuracy,
          group_info = grp_info,
          lambda_min = lambda_min,
          lambda_1se = lambda_1se,
          n_nonzero_pos = n_nonzero_pos,
          n_nonzero_neg = n_nonzero_neg,
          pos_index = sglwqs_fit$pos_index_sum,
          neg_index = sglwqs_fit$neg_index_sum
        )
        idx <- idx + 1
        
      }, error = function(e) {
        cat("  FAILED:", e$message, "\n")
        plan(sequential)
      })
    }
  }
}

toc()
```

---

# Results

## Direction Detection Accuracy

```{r accuracy-table}
acc_df <- data.frame()
for (res in all_results) {
  acc_df <- rbind(acc_df, data.frame(
    n = res$n, Alpha = res$alpha, Seed = res$seed, Accuracy = res$accuracy
  ))
}

acc_summary <- acc_df %>%
  group_by(n, Alpha) %>%
  summarize(Mean = mean(Accuracy, na.rm = TRUE),
            SD = sd(Accuracy, na.rm = TRUE), .groups = "drop") %>%
  mutate(`Mean (SD)` = sprintf("%.1f%% (%.1f%%)", Mean * 100, SD * 100))

acc_wide <- acc_summary %>%
  dplyr::select(n, Alpha, `Mean (SD)`) %>%
  mutate(Alpha = paste0("α = ", Alpha)) %>%
  pivot_wider(names_from = Alpha, values_from = `Mean (SD)`)

kable(acc_wide,
      caption = paste0("Direction Detection Accuracy by α and Sample Size (", N_SEEDS, " seeds)")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r accuracy-plot, fig.height=6, fig.width=10}
acc_summary$Alpha_label <- factor(paste0("α = ", acc_summary$Alpha))

p_acc <- ggplot(acc_summary, aes(x = factor(n), y = Mean, color = Alpha_label, group = Alpha_label)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = pmax(Mean - SD, 0), ymax = pmin(Mean + SD, 1)),
                width = 0.15, linewidth = 0.7) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73"), name = "Alpha") +
  labs(title = paste0("Direction Detection Accuracy by α (", N_SEEDS, " seeds)"),
       subtitle = "α = 0.05 (group-heavy), 0.5 (balanced), 0.95 (individual-heavy)",
       x = "Sample Size", y = "Accuracy") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom")
print(p_acc)

ggsave(file.path(fig_dir, "Fig_alpha_accuracy.pdf"), p_acc,
       width = 180, height = 110, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_alpha_accuracy.tiff"), p_acc,
       width = 180, height = 110, units = "mm", dpi = 300, compression = "lzw")
```

## Group Selection

```{r group-selection}
grp_df <- data.frame()
for (res in all_results) {
  grp_df <- rbind(grp_df, res$group_info %>% 
                    mutate(n = res$n, Alpha = res$alpha, Seed = res$seed))
}

grp_sel <- grp_df %>%
  group_by(n, Alpha, Group) %>%
  summarise(Selection_Rate = mean(Selected), .groups = "drop")

grp_sel$Group <- factor(grp_sel$Group, levels = c("PCBs", "Metals", "PFASs"))

p_sel <- ggplot(grp_sel, aes(x = factor(n), y = Selection_Rate, 
                              fill = factor(Alpha), group = factor(Alpha))) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, alpha = 0.8) +
  facet_wrap(~Group) +
  geom_hline(yintercept = 1, linetype = "dashed", alpha = 0.3) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"),
                    name = "Alpha",
                    labels = c("0.05 (group)", "0.5 (balanced)", "0.95 (individual)")) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  labs(title = paste0("Group Selection Rate by α and Sample Size (", N_SEEDS, " seeds)"),
       subtitle = "PFASs (null group) should ideally be selected less often at higher α",
       x = "Sample Size", y = "Selection Rate") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom")
print(p_sel)

ggsave(file.path(fig_dir, "Fig_alpha_group_selection.pdf"), p_sel,
       width = 220, height = 120, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_alpha_group_selection.tiff"), p_sel,
       width = 220, height = 120, units = "mm", dpi = 300, compression = "lzw")
```

## Group Significance

```{r group-significance}
grp_sig <- grp_df %>%
  filter(Selected) %>%
  group_by(n, Alpha, Group) %>%
  summarise(
    N_Selected = n(),
    Pos_Sig_Rate = mean(Pos_Pvalue < 0.05, na.rm = TRUE),
    Neg_Sig_Rate = mean(Neg_Pvalue < 0.05, na.rm = TRUE),
    .groups = "drop"
  )

kable(grp_sig %>% 
        mutate(across(c(Pos_Sig_Rate, Neg_Sig_Rate), ~ sprintf("%.0f%%", . * 100))),
      caption = paste0("Significance Rate (p < 0.05) Among Selected Seeds by α"),
      col.names = c("n", "α", "Group", "N Selected", "Pos Sig %", "Neg Sig %")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Sparsity: Number of Non-Zero Variables

```{r sparsity, fig.height=6, fig.width=12}
sparse_df <- data.frame()
for (res in all_results) {
  sparse_df <- rbind(sparse_df, data.frame(
    n = res$n, Alpha = res$alpha, Seed = res$seed,
    N_Nonzero = res$n_nonzero_pos + res$n_nonzero_neg,
    N_Nonzero_Pos = res$n_nonzero_pos,
    N_Nonzero_Neg = res$n_nonzero_neg
  ))
}

sparse_summary <- sparse_df %>%
  group_by(n, Alpha) %>%
  summarize(Mean = mean(N_Nonzero, na.rm = TRUE),
            SD = sd(N_Nonzero, na.rm = TRUE), .groups = "drop")

p_sparse <- ggplot(sparse_summary, aes(x = factor(n), y = Mean, 
                                        fill = factor(Alpha), group = factor(Alpha))) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, alpha = 0.8) +
  geom_errorbar(aes(ymin = pmax(Mean - SD, 0), ymax = Mean + SD),
                position = position_dodge(width = 0.7), width = 0.2) +
  geom_hline(yintercept = 26, linetype = "dashed", color = "red", alpha = 0.5) +
  annotate("text", x = 0.5, y = 27, label = "Max (13 × 2 directions)", 
           color = "red", size = 3, hjust = 0) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"),
                    name = "Alpha",
                    labels = c("0.05 (group)", "0.5 (balanced)", "0.95 (individual)")) +
  labs(title = paste0("Number of Non-Zero Coefficients by α (", N_SEEDS, " seeds)"),
       subtitle = "Lower = more sparse. Total possible = 26 (13 variables × 2 directions)",
       x = "Sample Size", y = "Non-Zero Coefficients (Mean ± SD)") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom")
print(p_sparse)

ggsave(file.path(fig_dir, "Fig_alpha_sparsity.pdf"), p_sparse,
       width = 180, height = 110, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_alpha_sparsity.tiff"), p_sparse,
       width = 180, height = 110, units = "mm", dpi = 300, compression = "lzw")
```

## Lambda Stability

```{r lambda-stability}
lambda_df <- data.frame()
for (res in all_results) {
  lambda_df <- rbind(lambda_df, data.frame(
    n = res$n, Alpha = res$alpha, Seed = res$seed,
    Lambda_min = res$lambda_min, Lambda_1se = res$lambda_1se
  ))
}

lambda_summary <- lambda_df %>%
  group_by(n, Alpha) %>%
  summarise(
    Min_Mean = mean(Lambda_min, na.rm = TRUE),
    Min_CV = sd(Lambda_min, na.rm = TRUE) / mean(Lambda_min, na.rm = TRUE),
    .groups = "drop"
  )

kable(lambda_summary,
      caption = "Lambda.min Summary by α and Sample Size",
      digits = 4,
      col.names = c("n", "α", "λ.min Mean", "λ.min CV")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r lambda-plot, fig.height=6, fig.width=12}
p_lam <- ggplot(lambda_df, aes(x = factor(n), y = Lambda_min, fill = factor(Alpha))) +
  geom_violin(alpha = 0.3, position = position_dodge(width = 0.7), trim = FALSE) +
  geom_jitter(aes(color = factor(Alpha)), size = 1, alpha = 0.5,
              position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7)) +
  scale_y_log10() +
  scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"), name = "Alpha") +
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73"), name = "Alpha") +
  labs(title = paste0("Lambda.min Distribution by α (", N_SEEDS, " seeds)"),
       x = "Sample Size", y = expression(lambda[min] ~ "(log scale)")) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom")
print(p_lam)

ggsave(file.path(fig_dir, "Fig_alpha_lambda.pdf"), p_lam,
       width = 220, height = 110, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_alpha_lambda.tiff"), p_lam,
       width = 220, height = 110, units = "mm", dpi = 300, compression = "lzw")
```

## Weight Profiles by Alpha

```{r weights-extract}
all_wt <- data.frame()
for (res in all_results) {
  w <- res$weights
  w$n <- res$n
  w$Alpha <- res$alpha
  w$Seed <- res$seed
  all_wt <- rbind(all_wt, w)
}

all_wt <- all_wt %>%
  left_join(true_directions %>% dplyr::select(Variable, True_Beta, Group, True_Direction), 
            by = "Variable")
```

```{r weight-heatmap, fig.height=10, fig.width=14}
wt_mean <- all_wt %>%
  filter(Direction %in% c("Positive", "Negative")) %>%
  group_by(Variable, Direction, n, Alpha, Group) %>%
  summarise(Mean_Weight = mean(Weight, na.rm = TRUE), .groups = "drop")

wt_mean$Group <- factor(wt_mean$Group, levels = c("PCBs", "Metals", "PFASs"))
wt_mean$Alpha_label <- paste0("α = ", wt_mean$Alpha)

# Show for n = 1000 and n = 10000 as representative
for (nn in c(1000, 10000)) {
  p <- wt_mean %>%
    filter(n == nn) %>%
    ggplot(aes(x = Alpha_label, y = Variable, fill = Mean_Weight)) +
    geom_tile(color = "white", linewidth = 0.3) +
    facet_grid(Group ~ Direction, scales = "free_y", space = "free_y") +
    scale_fill_distiller(palette = "YlOrRd", direction = 1, name = "Mean\nWeight") +
    labs(title = paste0("SGL-WQS Mean Weight by α (n = ", format(nn, big.mark=","), 
                        ", ", N_SEEDS, " seeds)"),
         x = NULL, y = NULL) +
    theme_minimal(base_size = 13) +
    theme(strip.text = element_text(face = "bold"),
          axis.text.y = element_text(size = 9))
  print(p)
  
  ggsave(file.path(fig_dir, paste0("Fig_alpha_weights_n", nn, ".pdf")), p,
         width = 200, height = 180, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, paste0("Fig_alpha_weights_n", nn, ".tiff")), p,
         width = 200, height = 180, units = "mm", dpi = 300, compression = "lzw")
}
```

## Mixture Effect Estimates

```{r effects, fig.height=6, fig.width=12}
eff_df <- data.frame()
for (res in all_results) {
  eff_df <- rbind(eff_df, data.frame(
    n = res$n, Alpha = res$alpha, Seed = res$seed,
    Pos_Index = res$pos_index, Neg_Index = res$neg_index
  ))
}

eff_long <- eff_df %>%
  pivot_longer(cols = c(Pos_Index, Neg_Index),
               names_to = "Direction", values_to = "Estimate") %>%
  mutate(Direction = ifelse(Direction == "Pos_Index", "Positive", "Negative"))

p_eff <- ggplot(eff_long, aes(x = factor(n), y = Estimate, fill = factor(Alpha))) +
  geom_violin(alpha = 0.3, position = position_dodge(width = 0.7), trim = FALSE) +
  geom_jitter(size = 0.8, alpha = 0.5,
              position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~Direction) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9", "#009E73"),
                    name = "Alpha",
                    labels = c("0.05 (group)", "0.5 (balanced)", "0.95 (individual)")) +
  labs(title = paste0("Mixture Effect Estimates by α (", N_SEEDS, " seeds)"),
       x = "Sample Size", y = "Index Sum") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom")
print(p_eff)

ggsave(file.path(fig_dir, "Fig_alpha_effects.pdf"), p_eff,
       width = 220, height = 110, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_alpha_effects.tiff"), p_eff,
       width = 220, height = 110, units = "mm", dpi = 300, compression = "lzw")
```

---

# Summary

```{r summary-table}
combined <- acc_df %>%
  left_join(sparse_df %>% dplyr::select(n, Alpha, Seed, N_Nonzero), 
            by = c("n", "Alpha", "Seed")) %>%
  left_join(lambda_df %>% dplyr::select(n, Alpha, Seed, Lambda_min),
            by = c("n", "Alpha", "Seed")) %>%
  group_by(n, Alpha) %>%
  summarise(
    Accuracy = sprintf("%.1f%% (%.1f%%)", mean(Accuracy)*100, sd(Accuracy)*100),
    Nonzero = sprintf("%.1f (%.1f)", mean(N_Nonzero), sd(N_Nonzero)),
    Lambda_CV = sprintf("%.3f", sd(Lambda_min) / mean(Lambda_min)),
    .groups = "drop"
  )

kable(combined,
      caption = paste0("Summary: α Sensitivity Across Sample Sizes (", N_SEEDS, " seeds)"),
      col.names = c("n", "α", "Accuracy Mean (SD)", "Non-Zero Mean (SD)", "λ.min CV")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# Session Info

```{r session-info}
sessionInfo()
```
