---
title: "High-Dimensional Group and Truth-Structure Sensitivity (Checkpointed)"
subtitle: "qgcomp vs gWQS vs groupWQS vs SGL-WQS under modest group/truth perturbations"
author: "Revision Simulation Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 150,
  cache = TRUE
)

parse_int_env <- function(name, default) {
  value <- Sys.getenv(name, unset = "")
  if (!nzchar(value)) return(default)
  parsed <- suppressWarnings(as.integer(value))
  if (is.na(parsed)) default else parsed
}

parse_numeric_vector_env <- function(name, default) {
  value <- Sys.getenv(name, unset = "")
  if (!nzchar(value)) return(default)
  parsed <- suppressWarnings(as.numeric(strsplit(value, ",", fixed = TRUE)[[1]]))
  parsed <- parsed[!is.na(parsed)]
  if (length(parsed) == 0L) default else parsed
}

parse_logical_env <- function(name, default = FALSE) {
  value <- tolower(Sys.getenv(name, unset = ""))
  if (!nzchar(value)) return(default)
  value %in% c("1", "true", "t", "yes", "y")
}

N_BOOT <- parse_int_env("GT_N_BOOT", 100L)
N_QUANTILES <- parse_int_env("GT_N_QUANTILES", 4L)

SEEDS_FULL <- c(71, 42, 123, 256, 314, 500, 617, 789, 888, 999,
                1001, 1123, 1234, 1357, 1500, 1618, 1729, 1847, 1963, 2048,
                2222, 2345, 2500, 2718, 2801, 3001, 3141, 3333, 3500, 3777)
N_SEEDS_REQUESTED <- parse_int_env("GT_N_SEEDS", 10L)
SEEDS <- SEEDS_FULL[seq_len(min(N_SEEDS_REQUESTED, length(SEEDS_FULL)))]
N_SEEDS <- length(SEEDS)

DETECTED_CORES <- parallel::detectCores()
N_WORKERS <- max(1L, parse_int_env("GT_N_WORKERS", 6L))
FORCE_RERUN <- parse_logical_env("GT_FORCE_RERUN", FALSE)

SENS_SCENARIOS <- data.frame(
  Scenario = c(
    "p100_g05_baseline3_main10",
    "p100_g10_baseline3_main10",
    "p100_g20_baseline3_main10",
    "p100_g10_weak3_main10",
    "p100_g10_strong3_main10",
    "p100_g05_weak3_orth5",
    "p100_g05_strong3_orth5",
    "p100_g20_weak3_orth5",
    "p100_g20_strong3_orth5"
  ),
  n = rep(1000L, 9L),
  p = rep(100L, 9L),
  n_groups = c(5L, 10L, 20L, 10L, 10L, 5L, 5L, 20L, 20L),
  truth_profile = c("baseline3", "baseline3", "baseline3",
                    "weak3", "strong3",
                    "weak3", "strong3", "weak3", "strong3"),
  seed_count = c(10L, 10L, 10L, 10L, 10L, 5L, 5L, 5L, 5L),
  stringsAsFactors = FALSE
)

if (parse_logical_env("GT_SMOKE_SMALL", FALSE)) {
  SENS_SCENARIOS <- data.frame(
    Scenario = "smoke_p050_g05_sparse3",
    n = 120L,
    p = 50L,
    n_groups = 5L,
    truth_profile = "sparse3",
    seed_count = 1L,
    stringsAsFactors = FALSE
  )
}

scenario_filter <- Sys.getenv("GT_SCENARIO_NAMES", unset = "")
if (nzchar(scenario_filter)) {
  keep_scenarios <- trimws(strsplit(scenario_filter, ",", fixed = TRUE)[[1]])
  SENS_SCENARIOS <- SENS_SCENARIOS[SENS_SCENARIOS$Scenario %in% keep_scenarios, , drop = FALSE]
  if (nrow(SENS_SCENARIOS) == 0L) {
    stop("GT_SCENARIO_NAMES did not match any configured sensitivity scenario.")
  }
}

scenario_levels <- SENS_SCENARIOS$Scenario
P_VALUES <- sort(unique(SENS_SCENARIOS$p))

fig_dir <- file.path("figures", "highdim_group_truth_checkpointed")
cache_dir <- file.path("analysis_cache", "highdim_group_truth_checkpointed")
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)
dir.create(cache_dir, showWarnings = FALSE, recursive = TRUE)

cat(sprintf("scenarios = %d; max seeds = %d; planned scenario-seeds = %d; bootstraps = %d\n",
            nrow(SENS_SCENARIOS), N_SEEDS, sum(pmin(SENS_SCENARIOS$seed_count, N_SEEDS)), N_BOOT))
cat(sprintf("Parallel workers requested: %d; detected cores: %s\n",
            N_WORKERS,
            ifelse(is.na(DETECTED_CORES), "unknown", as.character(DETECTED_CORES))))
```

# Overview

This simulation supplements the main high-dimensional exposure-count analysis by perturbing the number of exposure groups and signal strength at p = 100. The main group-count and signal-strength scenarios use 10 seeds, while selected orthogonal group-count/signal-strength corners use 5 seeds. The grid is checkpointed so that completed scenario/seed results can be recovered incrementally.

**Methods compared:** qgcomp, gWQS, groupWQS, and SGL-WQS.

**Design choices:**

- Variables are anonymized as `X001`, `X002`, ... because this simulation targets dimensionality rather than a specific chemical panel.
- The baseline setting uses 10 groups and three active groups.
- Additional scenarios vary group count, active-component sparsity/density, and include a small p > n stress setting.
- The remaining groups are null and are used to assess weight leakage and false positive behavior.
- The outer simulation grid is parallelized over `r N_WORKERS` workers. Method-level bootstrap parallelism is disabled to avoid nested oversubscription.
- The checkpointed runner saves each scenario/seed result immediately, then writes scenario-specific and full combined result files.

Environment overrides for smoke tests or reruns:

```r
Sys.setenv(
  GT_N_SEEDS = "1",
  GT_N_BOOT = "5",
  GT_N_WORKERS = "1",
  GT_FORCE_RERUN = "true"
)
```

# Setup

```{r load-packages, cache=FALSE}
library(MASS)
library(qgcomp)
library(gWQS)
library(groupWQS)
library(sglwqs)
library(future)
library(future.apply)
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(knitr)
library(kableExtra)
library(tictoc)
```

# Simulation Specification

```{r simulation-specification}
make_group_definitions <- function(p, n_groups = 10L) {
  stopifnot(p >= n_groups)
  vars <- sprintf("X%03d", seq_len(p))
  group_ids <- cut(seq_len(p),
                   breaks = n_groups,
                   labels = sprintf("G%02d", seq_len(n_groups)),
                   include.lowest = TRUE)
  split(vars, group_ids)
}

make_truth <- function(p, n_groups = 10L, truth_profile = "baseline3") {
  groups <- make_group_definitions(p, n_groups)
  vars <- unlist(groups, use.names = FALSE)
  beta <- setNames(rep(0, length(vars)), vars)

  add_group_effect <- function(group_index, direction, n_active, magnitude = c(0.08, 0.14)) {
    if (group_index > length(groups) || n_active <= 0L) return(invisible(NULL))
    group_vars <- groups[[group_index]]
    n_use <- min(length(group_vars), n_active)
    if (n_use <= 0L) return(invisible(NULL))
    effect <- signal_scale * seq(magnitude[1], magnitude[2], length.out = n_use)
    if (identical(direction, "negative")) effect <- -rev(effect)
    beta[group_vars[seq_len(n_use)]] <<- effect
    invisible(NULL)
  }

  add_mixed_group <- function(group_index, n_neg, n_pos) {
    if (group_index > length(groups)) return(invisible(NULL))
    group_vars <- groups[[group_index]]
    n_neg <- min(length(group_vars), n_neg)
    remaining <- max(length(group_vars) - n_neg, 0L)
    n_pos <- min(remaining, n_pos)
    if (n_neg > 0L) {
      beta[group_vars[seq_len(n_neg)]] <<- signal_scale * seq(-0.16, -0.11, length.out = n_neg)
    }
    if (n_pos > 0L) {
      pos_idx <- seq.int(n_neg + 1L, n_neg + n_pos)
      beta[group_vars[pos_idx]] <<- signal_scale * seq(0.10, 0.14, length.out = n_pos)
    }
    invisible(NULL)
  }

  profile <- match.arg(truth_profile, c("weak3", "baseline3", "strong3",
                                        "sparse3", "dense3", "many5"))
  signal_scale <- switch(
    profile,
    weak3 = 0.60,
    strong3 = 1.60,
    1.00
  )

  if (profile %in% c("weak3", "baseline3", "strong3")) {
    g1 <- groups[[1]]
    g2 <- groups[[2]]
    g3 <- groups[[3]]
    add_group_effect(1, "positive", max(3L, ceiling(length(g1) * 0.15)), c(0.08, 0.12))
    add_mixed_group(2,
                    max(2L, floor(length(g2) * 0.08)),
                    max(2L, floor(length(g2) * 0.06)))
    add_group_effect(3, "negative", max(2L, ceiling(length(g3) * 0.08)), c(0.10, 0.14))
  } else if (profile == "sparse3") {
    add_group_effect(1, "positive", 2L, c(0.10, 0.13))
    add_mixed_group(2, 1L, 1L)
    add_group_effect(3, "negative", 2L, c(0.10, 0.13))
  } else if (profile == "dense3") {
    g1 <- groups[[1]]
    g2 <- groups[[2]]
    g3 <- groups[[3]]
    add_group_effect(1, "positive", max(4L, ceiling(length(g1) * 0.30)), c(0.06, 0.11))
    add_mixed_group(2,
                    max(3L, ceiling(length(g2) * 0.15)),
                    max(3L, ceiling(length(g2) * 0.15)))
    add_group_effect(3, "negative", max(4L, ceiling(length(g3) * 0.20)), c(0.07, 0.12))
  } else if (profile == "many5") {
    active_groups <- seq_len(min(5L, length(groups)))
    for (idx in active_groups) {
      direction <- if (idx %% 2L == 0L) "negative" else "positive"
      add_group_effect(idx, direction, 2L, c(0.09, 0.13))
    }
  }

  truth <- data.frame(
    Variable = vars,
    True_Beta = as.numeric(beta),
    Group = rep(names(groups), lengths(groups)),
    stringsAsFactors = FALSE
  ) %>%
    mutate(
      True_Direction = case_when(
        True_Beta > 0.01 ~ "Positive",
        True_Beta < -0.01 ~ "Negative",
        TRUE ~ "None"
      ),
      IsActive = True_Direction != "None",
      IsActiveGroup = as.logical(ave(IsActive, Group, FUN = any))
    )

  list(
    groups = groups,
    all_exposures = vars,
    beta = beta,
    truth = truth,
    truth_profile = profile
  )
}

scenario_table <- purrr::pmap_dfr(SENS_SCENARIOS, function(Scenario, n, p, n_groups, truth_profile, seed_count) {
  spec <- make_truth(p = p, n_groups = n_groups, truth_profile = truth_profile)
  data.frame(
    Scenario = Scenario,
    n = n,
    p = p,
    truth_profile = truth_profile,
    planned_seeds = min(seed_count, N_SEEDS),
    n_groups = length(spec$groups),
    min_group_size = min(lengths(spec$groups)),
    max_group_size = max(lengths(spec$groups)),
    active_components = sum(spec$truth$IsActive),
    active_groups = sum(tapply(spec$truth$IsActive, spec$truth$Group, any))
  )
})

kable(scenario_table, caption = "High-dimensional simulation scenarios") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r true-effect-summary}
truth_preview <- purrr::pmap_dfr(SENS_SCENARIOS, function(Scenario, n, p, n_groups, truth_profile, seed_count) {
  spec <- make_truth(p = p, n_groups = n_groups, truth_profile = truth_profile)
  spec$truth %>%
    filter(IsActive) %>%
    count(Scenario = Scenario, p = p, n_groups = n_groups, truth_profile = truth_profile,
          Group, True_Direction, name = "Active_Components")
})

kable(truth_preview, caption = "Active components by p, group, and direction") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r true-effect-plot, fig.height=7, fig.width=12}
truth_for_plot <- purrr::pmap_dfr(SENS_SCENARIOS, function(Scenario, n, p, n_groups, truth_profile, seed_count) {
  make_truth(p = p, n_groups = n_groups, truth_profile = truth_profile)$truth %>%
    filter(IsActive) %>%
    mutate(Scenario = factor(Scenario, levels = scenario_levels))
})

ggplot(truth_for_plot, aes(x = Variable, y = True_Beta, fill = Group)) +
  geom_col(width = 0.75) +
  geom_hline(yintercept = 0, color = "gray30") +
  facet_wrap(~ Scenario, scales = "free_x", ncol = 2) +
  labs(
    title = "True Nonzero Component Effects",
    subtitle = "Only active components are shown; variables are anonymized.",
    x = NULL,
    y = "True beta"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom"
  )
```

# Data Generation

```{r data-generation-function}
generate_highdim_p_data <- function(p,
                                    n = 1000L,
                                    seed = 71,
                                    n_groups = 10L,
                                    truth_profile = "baseline3",
                                    within_rho = 0.45,
                                    cross_rho = 0.05,
                                    noise_sd = 4.0) {
  set.seed(seed)
  spec <- make_truth(p, n_groups, truth_profile)
  groups <- spec$groups
  vars <- spec$all_exposures
  beta <- spec$beta

  sex <- rbinom(n, 1, 0.5)
  age <- pmax(pmin(round(rnorm(n, 50, 12)), 80), 20)
  bmi <- pmax(pmin(round(22 + 0.05 * age + 1.5 * sex + rnorm(n, 0, 4), 1), 45), 15)

  global_factor <- rnorm(n)
  group_factors <- matrix(rnorm(n * length(groups)), nrow = n, ncol = length(groups))
  colnames(group_factors) <- names(groups)

  Xz <- matrix(NA_real_, nrow = n, ncol = length(vars), dimnames = list(NULL, vars))
  for (g in seq_along(groups)) {
    group_vars <- groups[[g]]
    idx <- match(group_vars, vars)
    eps <- matrix(rnorm(n * length(group_vars)), nrow = n, ncol = length(group_vars))
    latent <- sqrt(cross_rho) * global_factor +
      sqrt(within_rho) * group_factors[, g] +
      sqrt(1 - within_rho - cross_rho) * eps
    Xz[, idx] <- latent
  }

  group_shift <- rep(seq(-0.3, 0.3, length.out = length(groups)), lengths(groups))
  X <- exp(0.45 * sweep(Xz, 2, group_shift, "+"))
  colnames(X) <- vars

  X_scaled <- scale(X)
  eta <- 50 +
    as.numeric(X_scaled %*% beta) +
    sex * 2.0 +
    (age - 50) / 10 * 1.5 +
    (bmi - 25) / 5 * 3.0

  Y <- eta + rnorm(n, mean = 0, sd = noise_sd)

  out <- data.frame(X, sex = sex, age = age, bmi = bmi, Y = Y, check.names = FALSE)
  attr(out, "truth") <- spec$truth
  attr(out, "groups") <- groups
  attr(out, "beta") <- beta
  attr(out, "truth_profile") <- truth_profile
  out
}
```

```{r verify-data, cache=FALSE}
verification <- purrr::pmap_dfr(SENS_SCENARIOS, function(Scenario, n, p, n_groups, truth_profile, seed_count) {
  dat <- generate_highdim_p_data(
    p = p,
    n = n,
    seed = 42,
    n_groups = n_groups,
    truth_profile = truth_profile
  )
  truth <- attr(dat, "truth")
  active_vars <- truth$Variable[truth$IsActive]
  null_vars <- truth$Variable[!truth$IsActive]
  active_cor <- if (length(active_vars) > 1L) {
    mean(abs(cor(dat[, active_vars, drop = FALSE]))[upper.tri(cor(dat[, active_vars, drop = FALSE]))])
  } else {
    NA_real_
  }
  data.frame(
    Scenario = Scenario,
    p = p,
    n_groups = n_groups,
    truth_profile = truth_profile,
    n = nrow(dat),
    outcome_mean = mean(dat$Y),
    outcome_sd = sd(dat$Y),
    active_mean_abs_cor = active_cor,
    null_sample_size = length(null_vars)
  )
})

kable(verification, digits = 3, caption = "Generated data checks") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

# Method Wrappers

```{r helper-functions}
time_it <- function(expr) {
  start <- proc.time()[["elapsed"]]
  out <- tryCatch(
    list(ok = TRUE, value = force(expr), error = NA_character_),
    error = function(e) list(ok = FALSE, value = NULL, error = conditionMessage(e))
  )
  out$elapsed <- proc.time()[["elapsed"]] - start
  out
}

calc_active_direction_accuracy <- function(weights_df, truth) {
  if (is.null(weights_df) || nrow(weights_df) == 0L) return(NA_real_)

  wide <- weights_df %>%
    filter(Direction %in% c("Positive", "Negative")) %>%
    group_by(Variable, Direction) %>%
    summarize(Weight = sum(Weight, na.rm = TRUE), .groups = "drop") %>%
    tidyr::pivot_wider(names_from = Direction, values_from = Weight, values_fill = 0)

  scored <- truth %>%
    filter(IsActive) %>%
    left_join(wide, by = "Variable") %>%
    mutate(
      Positive = replace_na(Positive, 0),
      Negative = replace_na(Negative, 0),
      Detected = if_else(Positive >= Negative, "Positive", "Negative")
    )

  mean(scored$Detected == scored$True_Direction)
}

calc_groupwqs_active_direction_accuracy <- function(group_coefs, groups, truth) {
  if (is.null(group_coefs) || length(group_coefs) == 0L) return(NA_real_)
  n_coef <- min(length(group_coefs), length(groups))
  group_dir <- setNames(ifelse(group_coefs[seq_len(n_coef)] >= 0, "Positive", "Negative"),
                        names(groups)[seq_len(n_coef)])
  scored <- truth %>%
    filter(IsActive, Group %in% names(group_dir)) %>%
    mutate(Detected = unname(group_dir[Group]))
  mean(scored$Detected == scored$True_Direction)
}

extract_sglwqs_weights <- function(fit, p, seed) {
  extract_weights(fit, direction = "both") %>%
    dplyr::select(Variable = variable, Weight = weight, Direction = direction) %>%
    mutate(
      Direction = tools::toTitleCase(Direction),
      Method = "SGL-WQS",
      p = p,
      Seed = seed
    )
}

extract_sglwqs_selection <- function(fit, p, seed, truth) {
  if (is.null(fit$boot_info) ||
      is.null(fit$boot_info$selection_freq_pos) ||
      is.null(fit$boot_info$selection_freq_neg)) {
    return(NULL)
  }

  bind_rows(
    data.frame(
      Variable = names(fit$boot_info$selection_freq_pos),
      Direction = "Positive",
      SelFreq = as.numeric(fit$boot_info$selection_freq_pos),
      stringsAsFactors = FALSE
    ),
    data.frame(
      Variable = names(fit$boot_info$selection_freq_neg),
      Direction = "Negative",
      SelFreq = as.numeric(fit$boot_info$selection_freq_neg),
      stringsAsFactors = FALSE
    )
  ) %>%
    left_join(truth, by = "Variable") %>%
    mutate(Method = "SGL-WQS", p = p, Seed = seed)
}

build_weight_share_table <- function(weights_df, truth) {
  if (is.null(weights_df) || nrow(weights_df) == 0L) return(NULL)

  weights_df %>%
    group_by(Method, p, Seed, Variable) %>%
    summarize(MaxWeight = max(Weight, na.rm = TRUE), .groups = "drop") %>%
    left_join(truth, by = "Variable") %>%
    group_by(Method, p, Seed) %>%
    mutate(
      TotalWeight = sum(MaxWeight, na.rm = TRUE),
      NormWeight = if_else(TotalWeight > 0, MaxWeight / TotalWeight, NA_real_)
    ) %>%
    ungroup()
}
```

```{r analysis-function}
run_one_scenario <- function(p,
                             seed,
                             n = 1000L,
                             n_groups = 10L,
                             truth_profile = "baseline3",
                             scenario = sprintf("p%d_g%d_%s", p, n_groups, truth_profile)) {
  dat <- generate_highdim_p_data(
    p = p,
    n = n,
    seed = seed,
    n_groups = n_groups,
    truth_profile = truth_profile
  )
  truth <- attr(dat, "truth")
  groups <- attr(dat, "groups")
  all_exposures <- unlist(groups, use.names = FALSE)
  covars <- c("sex", "age", "bmi")

  result <- list(
    Scenario = scenario,
    p = p,
    n = n,
    n_groups = n_groups,
    truth_profile = truth_profile,
    seed = seed,
    weights = list(),
    effects = list(),
    accuracy = list(),
    timing = list(),
    errors = list(),
    selection = list()
  )

  # qgcomp
  qgcomp_res <- time_it({
    qgcomp_formula <- as.formula(
      paste("Y ~", paste(all_exposures, collapse = " + "), "+ sex + age + bmi")
    )
    fit <- qgcomp.glm.noboot(qgcomp_formula,
                             expnms = all_exposures,
                             data = dat,
                             family = gaussian(),
                             q = N_QUANTILES)
    weights <- data.frame(
      Variable = c(names(fit$pos.weights), names(fit$neg.weights)),
      Weight = c(fit$pos.weights, fit$neg.weights),
      Direction = c(rep("Positive", length(fit$pos.weights)),
                    rep("Negative", length(fit$neg.weights))),
      Method = "qgcomp",
      p = p,
      Seed = seed,
      stringsAsFactors = FALSE
    )
    list(
      weights = weights,
      effects = data.frame(
        Method = "qgcomp",
        p = p,
        Seed = seed,
        Effect_Type = c("Overall", "Positive", "Negative"),
        Estimate = c(fit$psi, fit$pos.psi, fit$neg.psi)
      ),
      active_direction_accuracy = calc_active_direction_accuracy(weights, truth)
    )
  })
  result$timing$qgcomp <- qgcomp_res$elapsed
  if (qgcomp_res$ok) {
    result$weights$qgcomp <- qgcomp_res$value$weights
    result$effects$qgcomp <- qgcomp_res$value$effects
    result$accuracy$qgcomp <- qgcomp_res$value$active_direction_accuracy
  } else {
    result$errors$qgcomp <- qgcomp_res$error
  }

  # gWQS, two-index
  gwqs_res <- time_it({
    gwqs_formula <- as.formula("Y ~ pwqs + nwqs + sex + age + bmi")
    fit <- withCallingHandlers(
      gwqs(gwqs_formula,
           mix_name = all_exposures,
           data = dat,
           q = N_QUANTILES,
           validation = 0.4,
           b = N_BOOT,
           b1_pos = TRUE,
           rh = 1,
           family = "gaussian",
           seed = seed,
           plan_strategy = "sequential"),
      warning = function(w) {
        if (grepl("Using formula\\(x\\) is deprecated|formula\\.character",
                  conditionMessage(w))) {
          invokeRestart("muffleWarning")
        }
      }
    )
    fw <- fit$final_weights
    weights <- bind_rows(
      data.frame(
        Variable = fw$mix_name,
        Weight = fw$mean_weight_p,
        Direction = "Positive",
        Method = "gWQS",
        p = p,
        Seed = seed,
        stringsAsFactors = FALSE
      ),
      data.frame(
        Variable = fw$mix_name,
        Weight = fw$mean_weight_n,
        Direction = "Negative",
        Method = "gWQS",
        p = p,
        Seed = seed,
        stringsAsFactors = FALSE
      )
    )
    coef_vec <- coef(fit$fit)
    list(
      weights = weights,
      effects = data.frame(
        Method = "gWQS",
        p = p,
        Seed = seed,
        Effect_Type = c("Positive", "Negative"),
        Estimate = c(unname(coef_vec["pwqs"]), unname(coef_vec["nwqs"]))
      ),
      active_direction_accuracy = calc_active_direction_accuracy(weights, truth)
    )
  })
  result$timing$gWQS <- gwqs_res$elapsed
  if (gwqs_res$ok) {
    result$weights$gWQS <- gwqs_res$value$weights
    result$effects$gWQS <- gwqs_res$value$effects
    result$accuracy$gWQS <- gwqs_res$value$active_direction_accuracy
  } else {
    result$errors$gWQS <- gwqs_res$error
  }

  # groupWQS
  groupwqs_res <- time_it({
    group_list <- unname(groups)
    X_gw <- make.X(dat, num.groups = length(group_list), groups = group_list)
    x_s <- make.x.s(dat, num.groups = length(group_list), groups = group_list)

    n_train <- round(nrow(dat) * 0.6)
    set.seed(seed)
    train_idx <- sample(seq_len(nrow(dat)), size = n_train)
    valid_idx <- setdiff(seq_len(nrow(dat)), train_idx)

    fit <- gwqs.fit(
      y = dat$Y[valid_idx],
      y.train = dat$Y[train_idx],
      x = X_gw[valid_idx, ],
      x.train = X_gw[train_idx, ],
      z = dat[valid_idx, covars, drop = FALSE],
      z.train = dat[train_idx, covars, drop = FALSE],
      x.s = x_s,
      B = N_BOOT,
      n.quantiles = N_QUANTILES,
      func = "continuous"
    )

    weights <- purrr::imap_dfr(fit$weights, function(w, i) {
      data.frame(
        Variable = names(w),
        Weight = as.numeric(w),
        Direction = "Combined",
        Method = "groupWQS",
        p = p,
        Seed = seed,
        stringsAsFactors = FALSE
      )
    })
    group_coefs <- coef(fit$fit)[grep("^GWQS", names(coef(fit$fit)))]

    list(
      weights = weights,
      effects = data.frame(
        Method = "groupWQS",
        p = p,
        Seed = seed,
        Effect_Type = names(group_coefs),
        Estimate = as.numeric(group_coefs)
      ),
      group_coefs = group_coefs,
      active_direction_accuracy = calc_groupwqs_active_direction_accuracy(group_coefs, groups, truth)
    )
  })
  result$timing$groupWQS <- groupwqs_res$elapsed
  if (groupwqs_res$ok) {
    result$weights$groupWQS <- groupwqs_res$value$weights
    result$effects$groupWQS <- groupwqs_res$value$effects
    result$accuracy$groupWQS <- groupwqs_res$value$active_direction_accuracy
  } else {
    result$errors$groupWQS <- groupwqs_res$error
  }

  # SGL-WQS
  sglwqs_res <- time_it({
    fit <- sglwqs(
      X = dat[, all_exposures, drop = FALSE],
      y = dat$Y,
      covariates = dat[, covars, drop = FALSE],
      groups = groups,
      family = "gaussian",
      n_quantiles = N_QUANTILES,
      bootstrap = TRUE,
      n_boot = N_BOOT,
      parallel = FALSE,
      validation = TRUE,
      train_prop = 0.6,
      seed = seed,
      verbose = FALSE
    )
    weights <- extract_sglwqs_weights(fit, p, seed)
    list(
      weights = weights,
      effects = data.frame(
        Method = "SGL-WQS",
        p = p,
        Seed = seed,
        Effect_Type = c("Positive", "Negative"),
        Estimate = c(fit$pos_index_sum, -fit$neg_index_sum)
      ),
      active_direction_accuracy = calc_active_direction_accuracy(weights, truth),
      selection = extract_sglwqs_selection(fit, p, seed, truth)
    )
  })
  result$timing$`SGL-WQS` <- sglwqs_res$elapsed
  if (sglwqs_res$ok) {
    result$weights$`SGL-WQS` <- sglwqs_res$value$weights
    result$effects$`SGL-WQS` <- sglwqs_res$value$effects
    result$accuracy$`SGL-WQS` <- sglwqs_res$value$active_direction_accuracy
    result$selection$`SGL-WQS` <- sglwqs_res$value$selection
  } else {
    result$errors$`SGL-WQS` <- sglwqs_res$error
  }

  result
}
```

# Run Analysis

```{r run-analysis, cache=FALSE}
results_file <- file.path(
  cache_dir,
  sprintf("highdim_group_truth_checkpointed_boot%d_seeds%d.rds", N_BOOT, N_SEEDS)
)

scenario_dir <- file.path(
  cache_dir,
  sprintf("scenarios_boot%d_seeds%d", N_BOOT, N_SEEDS)
)
scenario_result_dir <- file.path(
  cache_dir,
  sprintf("by_scenario_boot%d_seeds%d", N_BOOT, N_SEEDS)
)
dir.create(scenario_dir, showWarnings = FALSE, recursive = TRUE)
dir.create(scenario_result_dir, showWarnings = FALSE, recursive = TRUE)

scenario_grid <- purrr::pmap_dfr(
  SENS_SCENARIOS,
  function(Scenario, n, p, n_groups, truth_profile, seed_count) {
    scenario_seeds <- SEEDS[seq_len(min(as.integer(seed_count), length(SEEDS)))]
    data.frame(
      Scenario = Scenario,
      n = n,
      p = p,
      n_groups = n_groups,
      truth_profile = truth_profile,
      seed_count = as.integer(seed_count),
      Seed = scenario_seeds,
      stringsAsFactors = FALSE
    )
  }
) %>%
  mutate(Scenario = factor(Scenario, levels = scenario_levels)) %>%
  arrange(Scenario, Seed) %>%
  mutate(Scenario = as.character(Scenario))

scenario_file <- function(scenario, seed) {
  safe_scenario <- gsub("[^A-Za-z0-9_]+", "_", scenario)
  file.path(scenario_dir, sprintf("%s_seed%d.rds", safe_scenario, as.integer(seed)))
}

status_file <- file.path(
  cache_dir,
  sprintf("highdim_group_truth_checkpointed_status_boot%d_seeds%d.csv", N_BOOT, N_SEEDS)
)

write_checkpoint_status <- function() {
  files <- purrr::map2_chr(scenario_grid$Scenario, scenario_grid$Seed, scenario_file)
  info <- file.info(files)
  status <- scenario_grid %>%
    mutate(
      Scenario_File = files,
      Completed = file.exists(files),
      Size_Bytes = ifelse(Completed, info$size, NA_real_),
      Modified = ifelse(Completed, format(info$mtime, "%Y-%m-%d %H:%M:%S %Z"), NA_character_)
    )
  write.csv(status, status_file, row.names = FALSE)
  invisible(status)
}

run_or_load_checkpointed_scenario <- function(row_i, index_i, total_i) {
  out_file <- scenario_file(row_i$Scenario, row_i$Seed)
  if (file.exists(out_file) && !FORCE_RERUN) {
    cat(sprintf("[load] %s, seed=%d (%d/%d)\n",
                row_i$Scenario, row_i$Seed, index_i, total_i))
    return(readRDS(out_file))
  }

  cat(sprintf("[run] %s, seed=%d (%d/%d)\n",
              row_i$Scenario, row_i$Seed, index_i, total_i))
  result <- tryCatch(
    run_one_scenario(
      p = row_i$p,
      seed = row_i$Seed,
      n = row_i$n,
      n_groups = row_i$n_groups,
      truth_profile = row_i$truth_profile,
      scenario = row_i$Scenario
    ),
    error = function(e) {
      list(
        Scenario = row_i$Scenario,
        p = row_i$p,
        n = row_i$n,
        n_groups = row_i$n_groups,
        truth_profile = row_i$truth_profile,
        seed = row_i$Seed,
        weights = list(),
        effects = list(),
        accuracy = list(),
        timing = list(),
        errors = setNames(
          rep(conditionMessage(e), 4L),
          c("qgcomp", "gWQS", "groupWQS", "SGL-WQS")
        ),
        selection = list()
      )
    }
  )

  tmp_file <- paste0(out_file, ".tmp.", Sys.getpid())
  saveRDS(result, tmp_file)
  if (!file.rename(tmp_file, out_file)) {
    file.copy(tmp_file, out_file, overwrite = TRUE)
    unlink(tmp_file)
  }
  result
}

tic("Total group/truth sensitivity analysis time")

old_plan <- future::plan()
on.exit(future::plan(old_plan), add = TRUE)
options(future.globals.maxSize = 8 * 1024^3)
options(parallelly.maxWorkers.localhost = N_WORKERS)
future::plan(future::multisession, workers = N_WORKERS)

write_checkpoint_status()
all_results <- list()

for (scenario_i in scenario_levels) {
  scenario_grid_i <- scenario_grid %>% filter(Scenario == scenario_i)
  cat(sprintf("\n[%s] processing %d seeds with %d workers\n",
              scenario_i, nrow(scenario_grid_i), N_WORKERS))

  scenario_results <- future.apply::future_lapply(
    seq_len(nrow(scenario_grid_i)),
    function(i) {
      run_or_load_checkpointed_scenario(
        row_i = scenario_grid_i[i, , drop = FALSE],
        index_i = i,
        total_i = nrow(scenario_grid_i)
      )
    },
    future.seed = TRUE,
    future.packages = c(
      "MASS", "qgcomp", "gWQS", "groupWQS", "sglwqs",
      "dplyr", "tidyr", "purrr"
    )
  )

  scenario_file_out <- file.path(
    scenario_result_dir,
    sprintf("%s_results.rds", gsub("[^A-Za-z0-9_]+", "_", scenario_i))
  )
  saveRDS(scenario_results, scenario_file_out)
  all_results <- c(all_results, scenario_results)
  status_now <- write_checkpoint_status()
  completed_scenario <- sum(status_now$Completed[status_now$Scenario == scenario_i])
  cat(sprintf("[%s] checkpointed %d/%d scenario files\n",
              scenario_i, completed_scenario, nrow(scenario_grid_i)))
}

future::plan(future::sequential)

all_files <- purrr::map2_chr(scenario_grid$Scenario, scenario_grid$Seed, scenario_file)
if (all(file.exists(all_files))) {
  all_results <- lapply(all_files, readRDS)
  saveRDS(all_results, results_file)
  cat("Saved combined results to:", results_file, "\n")
} else {
  missing <- scenario_grid[!file.exists(all_files), , drop = FALSE]
  cat("Combined results not saved because scenario files are missing:\n")
  print(missing)
}

write_checkpoint_status()
toc()

cat(sprintf("Completed result objects: %d\n", length(all_results)))
```

# Results

```{r aggregate-results, cache=FALSE}
method_levels <- c("qgcomp", "gWQS", "groupWQS", "SGL-WQS")

accuracy_df <- purrr::map_dfr(all_results, function(res) {
  purrr::imap_dfr(res$accuracy, function(acc, method) {
    data.frame(
      Scenario = res$Scenario,
      p = res$p,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile,
      Seed = res$seed,
      Method = method,
      Active_Direction_Accuracy = as.numeric(acc),
      stringsAsFactors = FALSE
    )
  })
}) %>%
  mutate(Method = factor(Method, levels = method_levels))

weights_df <- purrr::map_dfr(all_results, function(res) {
  bind_rows(res$weights) %>%
    mutate(
      Scenario = res$Scenario,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile
    )
})

effects_df <- purrr::map_dfr(all_results, function(res) {
  bind_rows(res$effects) %>%
    mutate(
      Scenario = res$Scenario,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile
    )
}) %>%
  mutate(Method = factor(Method, levels = method_levels))

timing_df <- purrr::map_dfr(all_results, function(res) {
  purrr::imap_dfr(res$timing, function(elapsed, method) {
    data.frame(
      Scenario = res$Scenario,
      p = res$p,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile,
      Seed = res$seed,
      Method = method,
      Seconds = as.numeric(elapsed),
      stringsAsFactors = FALSE
    )
  })
}) %>%
  mutate(Method = factor(Method, levels = method_levels))

error_df <- purrr::map_dfr(all_results, function(res) {
  if (length(res$errors) == 0L) {
    return(data.frame())
  }
  purrr::imap_dfr(res$errors, function(msg, method) {
    data.frame(
      Scenario = res$Scenario,
      p = res$p,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile,
      Seed = res$seed,
      Method = method,
      Error = msg,
      stringsAsFactors = FALSE
    )
  })
})
if (nrow(error_df) == 0L) {
  error_df <- data.frame(
    Scenario = character(),
    p = integer(),
    n = integer(),
    n_groups = integer(),
    truth_profile = character(),
    Seed = numeric(),
    Method = factor(levels = method_levels),
    Error = character()
  )
} else {
  error_df <- error_df %>%
    mutate(Method = factor(Method, levels = method_levels))
}

selection_df <- purrr::map_dfr(all_results, function(res) {
  bind_rows(res$selection) %>%
    mutate(
      Scenario = res$Scenario,
      n = res$n,
      n_groups = res$n_groups,
      truth_profile = res$truth_profile
    )
})

truth_df <- purrr::pmap_dfr(SENS_SCENARIOS, function(Scenario, n, p, n_groups, truth_profile, seed_count) {
  make_truth(p = p, n_groups = n_groups, truth_profile = truth_profile)$truth %>%
    mutate(
      Scenario = Scenario,
      p = p,
      n = n,
      n_groups = n_groups,
      truth_profile = truth_profile,
      seed_count = seed_count
    )
})

weight_share_df <- purrr::map_dfr(split(weights_df, weights_df$Scenario), function(w_df) {
  scenario_i <- unique(w_df$Scenario)
  build_weight_share_table(
    w_df,
    truth_df %>%
      filter(Scenario == scenario_i) %>%
      select(Variable, True_Beta, Group, True_Direction, IsActive, IsActiveGroup)
  ) %>%
    mutate(
      Scenario = scenario_i,
      n = unique(w_df$n),
      n_groups = unique(w_df$n_groups),
      truth_profile = unique(w_df$truth_profile)
    )
})
```

## Failure and Convergence Summary

```{r failure-summary, cache=FALSE}
attempts_df <- purrr::map_dfr(method_levels, function(method) {
  scenario_grid %>%
    select(Scenario, p, n, n_groups, truth_profile, seed_count, Seed) %>%
    mutate(Method = method)
})

failure_summary <- attempts_df %>%
  left_join(error_df %>% mutate(Failed = TRUE),
            by = c("Scenario", "p", "n", "n_groups", "truth_profile", "Seed", "Method")) %>%
  mutate(Failed = replace_na(Failed, FALSE)) %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method) %>%
  summarize(
    Attempts = n(),
    Failures = sum(Failed),
    Failure_Rate = Failures / Attempts,
    .groups = "drop"
  )

kable(failure_summary, digits = 3,
      caption = "Method failures by group/truth sensitivity scenario") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

if (nrow(error_df) > 0L) {
  kable(error_df %>% arrange(Scenario, Method, Seed),
        caption = "Failure messages") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

```{r failure-plot, fig.height=6, fig.width=10, cache=FALSE}
p_failure <- ggplot(failure_summary,
                    aes(x = factor(Scenario, levels = scenario_levels),
                        y = Failure_Rate, fill = Method)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Failure Rate by Group/Truth Scenario",
    x = NULL,
    y = "Failure rate"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

p_failure
ggsave(file.path(fig_dir, "Fig_group_truth_failure_rate.pdf"), p_failure, width = 12, height = 6)
ggsave(file.path(fig_dir, "Fig_group_truth_failure_rate.tiff"), p_failure, width = 12, height = 6, dpi = 300)
```

## Active Direction Detection

```{r active-direction-summary, cache=FALSE}
accuracy_summary <- accuracy_df %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method) %>%
  summarize(
    Mean = mean(Active_Direction_Accuracy, na.rm = TRUE),
    SD = sd(Active_Direction_Accuracy, na.rm = TRUE),
    N = sum(!is.na(Active_Direction_Accuracy)),
    .groups = "drop"
  )

kable(accuracy_summary, digits = 3,
      caption = "Active-component direction accuracy") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r active-direction-plot, fig.height=7, fig.width=10, cache=FALSE}
p_acc <- ggplot(accuracy_summary,
                aes(x = factor(Scenario, levels = scenario_levels),
                    y = Mean, color = Method, group = Method)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = pmin(1, Mean + SD)),
                width = 0.25, alpha = 0.6,
                position = position_dodge(width = 0.35)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Active-Component Direction Accuracy",
    subtitle = "Accuracy is calculated only among truly active components.",
    x = NULL,
    y = "Mean accuracy +/- SD"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

p_acc
ggsave(file.path(fig_dir, "Fig_group_truth_active_direction_accuracy.pdf"), p_acc, width = 12, height = 7)
ggsave(file.path(fig_dir, "Fig_group_truth_active_direction_accuracy.tiff"), p_acc, width = 12, height = 7, dpi = 300)
```

## Weight Concentration

```{r weight-concentration-summary, cache=FALSE}
active_weight_share <- weight_share_df %>%
  group_by(Scenario, Method, p, n, n_groups, truth_profile, Seed, IsActive) %>%
  summarize(WeightShare = sum(NormWeight, na.rm = TRUE), .groups = "drop") %>%
  filter(IsActive) %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method) %>%
  summarize(
    Mean = mean(WeightShare, na.rm = TRUE),
    SD = sd(WeightShare, na.rm = TRUE),
    N = n(),
    .groups = "drop"
  )

kable(active_weight_share, digits = 3,
      caption = "Normalized weight share assigned to truly active components") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r weight-concentration-plot, fig.height=7, fig.width=10, cache=FALSE}
p_weight <- ggplot(active_weight_share,
                   aes(x = factor(Scenario, levels = scenario_levels),
                       y = Mean, color = Method, group = Method)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = pmin(1, Mean + SD)),
                width = 0.25, alpha = 0.6,
                position = position_dodge(width = 0.35)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Weight Concentration on Active Components",
    subtitle = "Weights are normalized within each method, scenario, and seed before summarization.",
    x = NULL,
    y = "Active-component weight share"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

p_weight
ggsave(file.path(fig_dir, "Fig_group_truth_active_weight_share.pdf"), p_weight, width = 12, height = 7)
ggsave(file.path(fig_dir, "Fig_group_truth_active_weight_share.tiff"), p_weight, width = 12, height = 7, dpi = 300)
```

```{r null-group-leakage, fig.height=7, fig.width=11, cache=FALSE}
group_weight_share <- weight_share_df %>%
  group_by(Scenario, Method, p, n, n_groups, truth_profile, Seed, Group, IsActiveGroup) %>%
  summarize(GroupWeightShare = sum(NormWeight, na.rm = TRUE), .groups = "drop")

null_group_leakage <- group_weight_share %>%
  group_by(Scenario, Method, p, n, n_groups, truth_profile, Seed, IsActiveGroup) %>%
  summarize(TotalShare = sum(GroupWeightShare, na.rm = TRUE), .groups = "drop") %>%
  filter(!IsActiveGroup) %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method) %>%
  summarize(
    Mean = mean(TotalShare, na.rm = TRUE),
    SD = sd(TotalShare, na.rm = TRUE),
    .groups = "drop"
  )

kable(null_group_leakage, digits = 3,
      caption = "Total normalized weight share assigned to null groups") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

p_null <- ggplot(null_group_leakage,
                 aes(x = factor(Scenario, levels = scenario_levels),
                     y = Mean, color = Method, group = Method)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = pmin(1, Mean + SD)),
                width = 0.25, alpha = 0.6,
                position = position_dodge(width = 0.35)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Weight Leakage to Null Groups",
    x = NULL,
    y = "Null-group weight share"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

p_null
ggsave(file.path(fig_dir, "Fig_group_truth_null_group_leakage.pdf"), p_null, width = 12, height = 7)
ggsave(file.path(fig_dir, "Fig_group_truth_null_group_leakage.tiff"), p_null, width = 12, height = 7, dpi = 300)
```

## SGL-WQS Bootstrap Selection Frequency

```{r sglwqs-selection-frequency, fig.height=7, fig.width=10, cache=FALSE}
if (nrow(selection_df) > 0L) {
  sgl_selection_summary <- selection_df %>%
    group_by(Scenario, p, n, n_groups, truth_profile, Seed, IsActive) %>%
    summarize(MeanSelFreq = mean(SelFreq, na.rm = TRUE), .groups = "drop") %>%
    group_by(Scenario, p, n, n_groups, truth_profile, IsActive) %>%
    summarize(
      Mean = mean(MeanSelFreq, na.rm = TRUE),
      SD = sd(MeanSelFreq, na.rm = TRUE),
      .groups = "drop"
    )

  kable(sgl_selection_summary, digits = 3,
        caption = "SGL-WQS mean bootstrap selection frequency") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

  p_sel <- ggplot(sgl_selection_summary,
                  aes(x = factor(Scenario, levels = scenario_levels),
                      y = Mean, color = IsActive, group = IsActive)) +
    geom_point(size = 2.5) +
    geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = pmin(1, Mean + SD)),
                  width = 0.25, alpha = 0.6,
                  position = position_dodge(width = 0.35)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
    labs(
      title = "SGL-WQS Bootstrap Selection Frequency",
      x = NULL,
      y = "Mean selection frequency",
      color = "Truly active"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

  p_sel
  ggsave(file.path(fig_dir, "Fig_group_truth_sglwqs_selection_frequency.pdf"), p_sel, width = 12, height = 7)
  ggsave(file.path(fig_dir, "Fig_group_truth_sglwqs_selection_frequency.tiff"), p_sel, width = 12, height = 7, dpi = 300)
} else {
  cat("No SGL-WQS selection frequency data were available.\n")
}
```

## Runtime

```{r runtime-summary, cache=FALSE}
runtime_summary <- timing_df %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method) %>%
  summarize(
    Median_Seconds = median(Seconds, na.rm = TRUE),
    Mean_Seconds = mean(Seconds, na.rm = TRUE),
    SD_Seconds = sd(Seconds, na.rm = TRUE),
    .groups = "drop"
  )

kable(runtime_summary, digits = 2,
      caption = "Per-scenario runtime by method") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r runtime-plot, fig.height=7, fig.width=10, cache=FALSE}
p_runtime <- ggplot(runtime_summary,
                    aes(x = factor(Scenario, levels = scenario_levels),
                        y = Median_Seconds, color = Method, group = Method)) +
  geom_point(size = 2.5) +
  scale_y_log10() +
  labs(
    title = "Median Runtime per Scenario",
    subtitle = "Log-scaled y-axis.",
    x = NULL,
    y = "Median seconds"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 35, hjust = 1))

p_runtime
ggsave(file.path(fig_dir, "Fig_group_truth_runtime.pdf"), p_runtime, width = 12, height = 7)
ggsave(file.path(fig_dir, "Fig_group_truth_runtime.tiff"), p_runtime, width = 12, height = 7, dpi = 300)
```

## Effect Estimate Summary

```{r effect-summary, cache=FALSE}
effect_summary <- effects_df %>%
  group_by(Scenario, p, n, n_groups, truth_profile, Method, Effect_Type) %>%
  summarize(
    Mean = mean(Estimate, na.rm = TRUE),
    SD = sd(Estimate, na.rm = TRUE),
    N = sum(!is.na(Estimate)),
    .groups = "drop"
  )

kable(effect_summary, digits = 3,
      caption = "Mixture/index effect estimates by method and sensitivity scenario") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

# Notes for Manuscript Use

The primary manuscript table should emphasize:

- failure/convergence rates across p;
- active-component direction accuracy;
- active-component weight concentration;
- weight leakage to null groups;
- runtime as a scalability diagnostic.

For qgcomp, weights are interpreted as post-hoc decomposition of the fitted overall mixture effect rather than as direct evidence of sparse component discovery. For groupWQS, one coefficient sign is assigned to all components within a group, so the mixed-direction group creates an expected structural ceiling for active-component direction accuracy.

# Session Information

```{r session-info, cache=FALSE}
sessionInfo()
```
