---
title: "NHANES VOC Survey Demo"
subtitle: "Urinary VOC metabolites, log-GGT, and survey refit"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  fig.width = 11,
  fig.height = 7,
  out.width = "100%",
  dpi = 150,
  warning = TRUE,
  message = TRUE
)

cwd_norm <- normalizePath(getwd(), mustWork = TRUE)
PROJECT_ROOT <- if (basename(cwd_norm) == "analysis") dirname(cwd_norm) else cwd_norm

fig_dir <- file.path(PROJECT_ROOT, "analysis", "figures", "nhanes_voc_demo")
out_dir <- file.path(PROJECT_ROOT, "analysis", "outputs")
cache_dir <- file.path(PROJECT_ROOT, "analysis", "cache")
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
dir.create(cache_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r parameters}
RUN_MODE <- Sys.getenv("SGLWQS_RUN_MODE", "smoke")
IS_SMOKE <- identical(tolower(RUN_MODE), "smoke")

N_QUANTILES <- as.integer(Sys.getenv("SGLWQS_N_QUANTILES", "4"))
N_BOOT <- as.integer(Sys.getenv("SGLWQS_N_BOOT", if (IS_SMOKE) "5" else "200"))
N_WORKERS <- as.integer(Sys.getenv("SGLWQS_N_WORKERS", "8"))
N_FOLDS <- as.integer(Sys.getenv("SGLWQS_NFOLDS", if (IS_SMOKE) "3" else "10"))
SGL_BOOTSTRAP <- tolower(Sys.getenv("SGLWQS_BOOTSTRAP", if (IS_SMOKE) "false" else "true")) %in% c("true", "1", "yes")
SMOKE_MAX_N <- as.integer(Sys.getenv("NHANES_VOC_SMOKE_N", if (IS_SMOKE) "600" else "0"))

SEEDS <- if (IS_SMOKE) {
  c(101)
} else {
  c(71, 42, 123, 256, 314, 500, 617, 789, 888, 999,
    1001, 1123, 1234, 1357, 1500, 1618, 1729, 1847, 1963, 2048,
    2222, 2345, 2500, 2718, 2801, 3001, 3141, 3333, 3500, 3777)
}
seed_override <- Sys.getenv("SGLWQS_SEEDS", "")
if (nzchar(seed_override)) {
  SEEDS <- as.integer(strsplit(seed_override, ",", fixed = TRUE)[[1]])
}

PRIMARY_OUTCOME <- Sys.getenv("NHANES_VOC_OUTCOME", "log_ggt")
PRIMARY_DIRECTION <- Sys.getenv("NHANES_VOC_PRIMARY_DIRECTION", "Positive")
COVARIATE_SET <- Sys.getenv("NHANES_VOC_COVARIATE_SET", "dag_primary")
OUTPUT_STEM <- Sys.getenv("NHANES_VOC_OUTPUT_STEM", "nhanes_voc_demo")
REFRESH_NHANES <- tolower(Sys.getenv("NHANES_REFRESH", "false")) %in% c("true", "1", "yes")
SHOW_WEIGHT_TABLES <- tolower(Sys.getenv("NHANES_VOC_SHOW_WEIGHT_TABLES", "false")) %in% c("true", "1", "yes")
SHOW_WEIGHT_FIGURES <- tolower(Sys.getenv("NHANES_VOC_SHOW_WEIGHT_FIGURES", "true")) %in% c("true", "1", "yes")

lambda_env <- Sys.getenv("SGLWQS_LAMBDA", "0")
SGL_LAMBDA <- if (lambda_env %in% c("0", "0.0")) 0 else lambda_env

RUN_QGCOMP <- tolower(Sys.getenv("RUN_QGCOMP", "true")) %in% c("true", "1", "yes")
RUN_GWQS <- tolower(Sys.getenv("RUN_GWQS", "true")) %in% c("true", "1", "yes")
RUN_GROUPWQS <- tolower(Sys.getenv("RUN_GROUPWQS", "true")) %in% c("true", "1", "yes")
RUN_SGLWQS <- tolower(Sys.getenv("RUN_SGLWQS", "true")) %in% c("true", "1", "yes")
RUN_SGLWQS_UNWEIGHTED <- tolower(Sys.getenv("RUN_SGLWQS_UNWEIGHTED", "true")) %in% c("true", "1", "yes")
RUN_SGLWQS_SURVEY <- tolower(Sys.getenv("RUN_SGLWQS_SURVEY", "true")) %in% c("true", "1", "yes")
RUN_SGLWQS_LAMBDA_COMPARISON <- tolower(Sys.getenv("RUN_SGLWQS_LAMBDA_COMPARISON", "false")) %in%
  c("true", "1", "yes")
SGL_COMPARE_BOOTSTRAP <- tolower(Sys.getenv("SGLWQS_COMPARE_BOOTSTRAP", "false")) %in%
  c("true", "1", "yes")
USE_MODEL_CACHE <- tolower(Sys.getenv("NHANES_VOC_USE_MODEL_CACHE", "true")) %in% c("true", "1", "yes")
REFRESH_MODEL_CACHE <- tolower(Sys.getenv("NHANES_VOC_REFRESH_MODEL_CACHE", "false")) %in% c("true", "1", "yes")

survey_lambda_path_values <- Sys.getenv("SGLWQS_SURVEY_LAMBDA_PATH", "")
use_survey_explicit_lambda_path <- tolower(Sys.getenv("SGLWQS_SURVEY_EXPLICIT_LAMBDA_PATH", "false")) %in%
  c("true", "1", "yes") || RUN_SGLWQS_LAMBDA_COMPARISON
SGL_SURVEY_LAMBDA_PATH <- NULL
if (nzchar(survey_lambda_path_values)) {
  SGL_SURVEY_LAMBDA_PATH <- as.numeric(strsplit(survey_lambda_path_values, ",", fixed = TRUE)[[1]])
} else if (use_survey_explicit_lambda_path) {
  survey_lambda_max <- as.numeric(Sys.getenv("SGLWQS_SURVEY_LAMBDA_MAX", "0.1"))
  survey_lambda_min <- as.numeric(Sys.getenv("SGLWQS_SURVEY_LAMBDA_MIN", if (RUN_SGLWQS_LAMBDA_COMPARISON) "1e-8" else "1e-6"))
  survey_lambda_n <- as.integer(Sys.getenv("SGLWQS_SURVEY_LAMBDA_N", "80"))
  SGL_SURVEY_LAMBDA_PATH <- exp(seq(log(survey_lambda_max), log(survey_lambda_min), length.out = survey_lambda_n))
}

survey_lambda_path_summary <- if (is.null(SGL_SURVEY_LAMBDA_PATH)) {
  "NULL"
} else {
  sprintf(
    "explicit n=%d, range=[%.3g, %.3g]",
    length(SGL_SURVEY_LAMBDA_PATH),
    min(SGL_SURVEY_LAMBDA_PATH),
    max(SGL_SURVEY_LAMBDA_PATH)
  )
}

covariate_sets <- list(
  minimal = c("age", "sex", "race"),
  ucr = c("age", "sex", "race", "log_ucr"),
  bmi_ucr = c("age", "sex", "race", "bmi", "log_ucr"),
  dag_primary = c("age", "sex", "race", "pir", "log_cotinine", "bmi", "log_ucr"),
  dag_no_tobacco = c("age", "sex", "race", "pir", "bmi", "log_ucr"),
  survey_reduced = c("age", "sex", "race4", "bmi", "log_ucr")
)
if (!COVARIATE_SET %in% names(covariate_sets)) {
  stop("Unknown NHANES_VOC_COVARIATE_SET: ", COVARIATE_SET,
       ". Available: ", paste(names(covariate_sets), collapse = ", "),
       call. = FALSE)
}

settings_tbl <- data.frame(
  setting = c("RUN_MODE", "N_BOOT", "N_SEEDS", "N_WORKERS", "N_FOLDS",
              "N_QUANTILES", "SGL_BOOTSTRAP", "SMOKE_MAX_N", "PRIMARY_OUTCOME",
              "PRIMARY_DIRECTION", "COVARIATE_SET", "OUTPUT_STEM",
              "SGL_LAMBDA", "RUN_SGLWQS_UNWEIGHTED", "RUN_SGLWQS_SURVEY",
              "RUN_SGLWQS_LAMBDA_COMPARISON", "SGL_COMPARE_BOOTSTRAP",
              "SGL_SURVEY_LAMBDA_PATH", "USE_MODEL_CACHE",
              "REFRESH_MODEL_CACHE", "SHOW_WEIGHT_TABLES", "SHOW_WEIGHT_FIGURES"),
  value = c(RUN_MODE, N_BOOT, length(SEEDS), N_WORKERS, N_FOLDS,
            N_QUANTILES, SGL_BOOTSTRAP, SMOKE_MAX_N, PRIMARY_OUTCOME,
            PRIMARY_DIRECTION, COVARIATE_SET, OUTPUT_STEM,
            as.character(SGL_LAMBDA), RUN_SGLWQS_UNWEIGHTED, RUN_SGLWQS_SURVEY,
            RUN_SGLWQS_LAMBDA_COMPARISON, SGL_COMPARE_BOOTSTRAP,
            survey_lambda_path_summary, USE_MODEL_CACHE,
            REFRESH_MODEL_CACHE, SHOW_WEIGHT_TABLES, SHOW_WEIGHT_FIGURES)
)
knitr::kable(settings_tbl)
```

# Overview

This R Markdown file is a public-data method demonstration using urinary
VOC metabolites from NHANES 2017-2020 pre-pandemic data. The default outcome is
log-transformed gamma-glutamyl transferase (`log_ggt`), a liver-related marker
for which larger values are interpreted as less favorable. The prespecified
primary mixture direction is therefore positive: higher VOC-mixture burden is
expected to correspond to higher `log_ggt`.

Negative-index estimates are still retained for two-index methods, but they are
treated as secondary/descriptive. The VOC classes defined below are the a priori
chemical/metabolic groups used by groupWQS and SGL-WQS; for qgcomp and gWQS,
the same classes are only analyte annotations and are not separate group-level
estimands.

Because the exposures are measured in the P_UVOC subsample, the complex-survey
refit uses the VOC subsample weight (`WTSAPRP`) with NHANES PSU and strata.
Changing the continuous outcome from the nutrient example to `log_ggt` changes
the complete-case analytic sample, but not the survey design variables.

The default covariate set is `dag_primary`, which adds the DAG-based adjustment
variables plus urinary creatinine for dilution adjustment. `dag_no_tobacco` is
available as a sensitivity setting when the goal is to retain tobacco-related
VOC burden as part of the mixture contrast rather than adjust for cotinine.
`survey_reduced` collapses race/ethnicity and omits PIR/cotinine for a lower
degree-of-freedom survey sensitivity run. The default SGL-WQS setting uses
`lambda = 0`, turning sparse selection off for a transparent survey/refit
validation aligned with the exact-match checks; `SGLWQS_LAMBDA=lambda.min` can
be set for a sparse-selection sensitivity run.

The main comparison includes:

- qgcomp, gWQS, and groupWQS on the analysis dataset without survey design.
- SGL-WQS without survey design.
- SGL-WQS with `survey::svydesign()` using the VOC subsample weight.

The SGL-WQS survey analysis uses the current API with `survey_design` and
`analysis_id`. For local development, this Rmd can load the source tree or the
tarball `sglwqs_0.8.13.9001.tar.gz`.

# Packages

```{r packages}
required_pkgs <- c(
  "nhanesA", "survey", "qgcomp", "gWQS", "groupWQS",
  "dagitty", "dplyr", "tidyr", "ggplot2", "knitr", "kableExtra",
  "future", "future.apply"
)
missing_pkgs <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_pkgs) > 0) {
  stop("Install missing package(s): ", paste(missing_pkgs, collapse = ", "), call. = FALSE)
}

load_sglwqs <- function() {
  mode <- Sys.getenv("SGLWQS_LOAD_MODE", "installed")
  source_dir <- Sys.getenv("SGLWQS_SOURCE_DIR", "")
  tarball <- Sys.getenv("SGLWQS_PACKAGE_TARBALL", "")

  if (identical(mode, "source") && dir.exists(source_dir)) {
    if (!requireNamespace("pkgload", quietly = TRUE)) {
      stop("Package 'pkgload' is required for SGLWQS_LOAD_MODE=source.", call. = FALSE)
    }
    pkgload::load_all(source_dir, quiet = TRUE)
    return(invisible("source"))
  }

  if (identical(mode, "tarball") && file.exists(tarball)) {
    local_lib <- Sys.getenv(
      "SGLWQS_LOCAL_LIB",
      file.path(PROJECT_ROOT, "analysis", "_r_libs", "sglwqs_0.8.13.9001")
    )
    dir.create(local_lib, showWarnings = FALSE, recursive = TRUE)
    utils::install.packages(tarball, repos = NULL, type = "source", lib = local_lib, quiet = TRUE)
    .libPaths(c(local_lib, .libPaths()))
    suppressPackageStartupMessages(library(sglwqs))
    return(invisible("tarball"))
  }

  suppressPackageStartupMessages(library(sglwqs))
  invisible("installed")
}

sglwqs_load_mode <- load_sglwqs()

suppressPackageStartupMessages({
  library(nhanesA)
  library(survey)
  library(qgcomp)
  library(gWQS)
  library(groupWQS)
  library(dagitty)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(future)
  library(future.apply)
})

options(survey.lonely.psu = "adjust")

package_tbl <- data.frame(
  package = c(required_pkgs, "sglwqs"),
  version = vapply(c(required_pkgs, "sglwqs"), function(pkg) {
    as.character(utils::packageVersion(pkg))
  }, character(1)),
  stringsAsFactors = FALSE
)
package_tbl$loaded_from <- ifelse(package_tbl$package == "sglwqs", sglwqs_load_mode, "")
knitr::kable(package_tbl)
```

# DAG And Covariates

The primary covariate set is based on a simple causal DAG for urinary VOC
metabolites and log-GGT. Age, sex, race/ethnicity, socioeconomic position,
smoking, and BMI are treated as potential common causes of VOC biomarker levels
and liver-related outcome variation. Urinary creatinine is handled separately as
a measurement/dilution covariate for urinary VOC concentrations.

```{r dag-covariates, fig.width=8, fig.height=5}
voc_dag <- dagitty::dagitty('dag {
Age [pos="0,2"]
Sex [pos="0,1"]
RaceEthnicity [pos="0,0"]
SES [pos="1,0"]
Smoking [pos="1,2"]
BMI [pos="2,2"]
UrineDilution [pos="2,0"]
VOC [exposure,pos="3,1"]
GGT [outcome,pos="5,1"]

Age -> BMI
Age -> GGT
Age -> UrineDilution
Age -> VOC
Sex -> BMI
Sex -> GGT
Sex -> UrineDilution
Sex -> VOC
RaceEthnicity -> GGT
RaceEthnicity -> SES
RaceEthnicity -> Smoking
RaceEthnicity -> VOC
SES -> GGT
SES -> Smoking
SES -> VOC
Smoking -> GGT
Smoking -> VOC
BMI -> GGT
BMI -> UrineDilution
BMI -> VOC
UrineDilution -> VOC
VOC -> GGT
}')

plot(voc_dag)

pdf(file.path(fig_dir, paste0(OUTPUT_STEM, "_dag.pdf")), width = 8, height = 5)
plot(voc_dag)
invisible(dev.off())

dag_sets <- dagitty::adjustmentSets(voc_dag, exposure = "VOC", outcome = "GGT", type = "minimal")
dag_set_tbl <- data.frame(
  set = seq_along(dag_sets),
  variables = vapply(dag_sets, function(x) paste(x, collapse = ", "), character(1)),
  stringsAsFactors = FALSE
)
knitr::kable(dag_set_tbl, caption = "DAGitty minimal adjustment set(s) for VOC -> GGT.")

dag_variable_map <- data.frame(
  dag_node = c("Age", "Sex", "RaceEthnicity", "SES", "Smoking", "BMI", "UrineDilution"),
  nhanes_variable = c("RIDAGEYR", "RIAGENDR", "RIDRETH3", "INDFMPIR", "LBXCOT", "BMXBMI", "URXUCR"),
  model_variable = c("age", "sex", "race", "pir", "log_cotinine", "bmi", "log_ucr"),
  role = c(rep("DAG adjustment", 6), "Urinary dilution adjustment"),
  stringsAsFactors = FALSE
)
knitr::kable(dag_variable_map, caption = "Mapping from DAG nodes to NHANES/model covariates.")

covariate_set_tbl <- data.frame(
  set = names(covariate_sets),
  variables = vapply(covariate_sets, function(x) paste(x, collapse = ", "), character(1)),
  stringsAsFactors = FALSE
)
knitr::kable(covariate_set_tbl, caption = "Implemented covariate set options.")
```

# VOC Data

```{r voc-map}
voc_groups <- list(
  Aromatic_hydrocarbons = c("URX2MH", "URX34M", "URXBMA", "URXMAD", "URXPHG"),
  Dienes_alkenes_epoxides = c("URXDHB", "URXMB3", "URXIPM3", "URXHP2"),
  Nitrile_amide_cyanide_related = c("URXAAM", "URXAMC", "URXCEM", "URXCYM", "URXATC"),
  Reactive_aldehydes = c("URXHPM", "URXPMM")
)

voc_exposures <- unname(unlist(voc_groups, use.names = FALSE))

voc_group_map <- data.frame(
  variable = voc_exposures,
  group = rep(names(voc_groups), lengths(voc_groups)),
  stringsAsFactors = FALSE
) |>
  dplyr::mutate(
    group_label = dplyr::recode(
      group,
      Aromatic_hydrocarbons = "Aromatic hydrocarbons",
      Dienes_alkenes_epoxides = "Dienes/alkenes/epoxides",
      Nitrile_amide_cyanide_related = "Nitrile/amide/cyanide-related",
      Reactive_aldehydes = "Reactive aldehydes"
    )
  )

voc_names <- c(
  URX2MH = "2-methylhippuric acid",
  URX34M = "3-/4-methylhippuric acid",
  URXBMA = "N-acetyl-S-(benzyl)-L-cysteine",
  URXMAD = "Mandelic acid",
  URXPHG = "Phenylglyoxylic acid",
  URXDHB = "N-acetyl-S-(3,4-dihydroxybutyl)-L-cysteine",
  URXMB3 = "N-acetyl-S-(4-hydroxy-2-butenyl)-L-cysteine",
  URXIPM3 = "N-acetyl-S-(4-hydroxy-2-methyl-2-buten-1-yl)-L-cysteine",
  URXHP2 = "N-acetyl-S-(2-hydroxypropyl)-L-cysteine",
  URXAAM = "N-acetyl-S-(2-carbamoylethyl)-L-cysteine",
  URXAMC = "N-acetyl-S-(N-methylcarbamoyl)-L-cysteine",
  URXCEM = "N-acetyl-S-(2-carboxyethyl)-L-cysteine",
  URXCYM = "N-acetyl-S-(2-cyanoethyl)-L-cysteine",
  URXATC = "2-aminothiazoline-4-carboxylic acid",
  URXHPM = "N-acetyl-S-(3-hydroxypropyl)-L-cysteine",
  URXPMM = "N-acetyl-S-(3-hydroxypropyl-1-methyl)-L-cysteine"
)

parent_proxy <- c(
  URX2MH = "o-xylene",
  URX34M = "m-/p-xylene",
  URXBMA = "toluene",
  URXMAD = "styrene/ethylbenzene",
  URXPHG = "styrene/ethylbenzene",
  URXDHB = "1,3-butadiene",
  URXMB3 = "1,3-butadiene",
  URXIPM3 = "isoprene",
  URXHP2 = "propylene oxide",
  URXAAM = "acrylamide",
  URXAMC = "N,N-dimethylformamide",
  URXCEM = "acrylonitrile/acrolein-related",
  URXCYM = "acrylonitrile",
  URXATC = "cyanide-related exposure",
  URXHPM = "acrolein",
  URXPMM = "crotonaldehyde"
)

voc_annotation <- voc_group_map |>
  dplyr::mutate(
    metabolite = unname(voc_names[variable]),
    parent_proxy = unname(parent_proxy[variable])
  ) |>
  dplyr::select(variable, metabolite, parent_proxy, group_label)

knitr::kable(voc_annotation, caption = "Selected P_UVOC analytes: unweighted detection >= 75%; URXBPM excluded.")
```

```{r data-download}
nhanes_cache_file <- file.path(cache_dir, "nhanes_puvoc_2017_2020_tables.rds")

download_nhanes_tables <- function(refresh = FALSE) {
  if (file.exists(nhanes_cache_file) && !isTRUE(refresh)) {
    return(readRDS(nhanes_cache_file))
  }

  tabs <- c("P_UVOC", "P_DEMO", "P_BIOPRO", "P_HSCRP", "P_BMX", "P_ALB_CR", "P_COT")
  dat <- lapply(tabs, function(tab) {
    message("Downloading NHANES table: ", tab)
    nhanesA::nhanes(tab, translated = FALSE)
  })
  names(dat) <- tabs
  saveRDS(dat, nhanes_cache_file)
  dat
}

nhanes_tables <- download_nhanes_tables(refresh = REFRESH_NHANES)
vapply(nhanes_tables, nrow, integer(1))
```

```{r build-data}
left_merge <- function(x, y) merge(x, y, by = "SEQN", all.x = TRUE, sort = FALSE)

nh <- nhanes_tables$P_UVOC
for (tab in c("P_DEMO", "P_BIOPRO", "P_HSCRP", "P_BMX", "P_ALB_CR", "P_COT")) {
  nh <- left_merge(nh, nhanes_tables[[tab]])
}

nh$.analysis_id <- nh$SEQN
nh$log_ggt <- log(nh$LBXSGTSI)
nh$log_crp <- log(nh$LBXHSCRP)
nh$log_ucr <- log(nh$URXUCR)
nh$log_cotinine <- log1p(nh$LBXCOT)
nh$age <- nh$RIDAGEYR
nh$sex <- factor(nh$RIAGENDR, levels = c(1, 2), labels = c("Male", "Female"))
nh$race <- factor(nh$RIDRETH3)
nh$race4 <- factor(
  dplyr::case_when(
    nh$RIDRETH3 %in% c(1, 2) ~ "Hispanic",
    nh$RIDRETH3 == 3 ~ "NH_White",
    nh$RIDRETH3 == 4 ~ "NH_Black",
    nh$RIDRETH3 %in% c(6, 7) ~ "NH_Asian_Other",
    TRUE ~ NA_character_
  ),
  levels = c("NH_White", "NH_Black", "Hispanic", "NH_Asian_Other")
)
nh$bmi <- nh$BMXBMI
nh$pir <- nh$INDFMPIR

base_covariates <- covariate_sets[[COVARIATE_SET]]

analysis_vars <- c(
  ".analysis_id", "SEQN", "SDMVPSU", "SDMVSTRA", "WTSAPRP",
  PRIMARY_OUTCOME, voc_exposures, base_covariates
)

analysis_df <- nh |>
  dplyr::filter(!is.na(WTSAPRP), WTSAPRP > 0, RIDAGEYR >= 20) |>
  dplyr::filter(stats::complete.cases(dplyr::across(dplyr::all_of(analysis_vars)))) |>
  dplyr::filter(.data[[PRIMARY_OUTCOME]] > -Inf, is.finite(.data[[PRIMARY_OUTCOME]])) |>
  as.data.frame()

full_analysis_n <- nrow(analysis_df)
if (SMOKE_MAX_N > 0 && nrow(analysis_df) > SMOKE_MAX_N) {
  set.seed(20260622)
  smoke_idx <- sort(sample(seq_len(nrow(analysis_df)), size = SMOKE_MAX_N))
  analysis_df <- analysis_df[smoke_idx, , drop = FALSE]
}

covariate_model_df <- analysis_df[, base_covariates, drop = FALSE]
covariate_matrix <- stats::model.matrix(~ ., data = covariate_model_df)
covariate_matrix <- covariate_matrix[, colnames(covariate_matrix) != "(Intercept)", drop = FALSE]
colnames(covariate_matrix) <- make.names(colnames(covariate_matrix), unique = TRUE)
covariate_df <- as.data.frame(covariate_matrix)

model_df <- cbind(
  analysis_df[, c(".analysis_id", "SEQN", "SDMVPSU", "SDMVSTRA", "WTSAPRP", PRIMARY_OUTCOME, voc_exposures)],
  covariate_df
)
model_df$outcome <- model_df[[PRIMARY_OUTCOME]]
rownames(model_df) <- as.character(model_df$.analysis_id)

covariate_terms <- colnames(covariate_df)

nhanes_design <- survey::svydesign(
  ids = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTSAPRP,
  nest = TRUE,
  data = model_df
)

data_summary <- data.frame(
  item = c("NHANES table", "sample", "age restriction", "outcome",
           "covariate set", "base covariates", "full complete-case n",
           "analysis n used", "VOC analytes", "covariate terms", "survey df"),
  value = c("P_UVOC + P_DEMO/P_BIOPRO/P_HSCRP/P_BMX/P_ALB_CR/P_COT",
            "WTSAPRP > 0", "RIDAGEYR >= 20", PRIMARY_OUTCOME,
            COVARIATE_SET, paste(base_covariates, collapse = ", "),
            full_analysis_n, nrow(model_df), length(voc_exposures), length(covariate_terms),
            survey::degf(nhanes_design))
)
knitr::kable(data_summary, caption = "Analysis dataset summary")
```

```{r detection-summary}
comment_codes <- c(
  URX2MH = "URD2MHLC",
  URX34M = "URD34MLC",
  URXAAM = "URDAAMLC",
  URXAMC = "URDAMCLC",
  URXATC = "URDATCLC",
  URXBMA = "URDBMALC",
  URXCEM = "URDCEMLC",
  URXCYM = "URDCYMLC",
  URXDHB = "URDDHBLC",
  URXHPM = "URDHPMLC",
  URXHP2 = "URDHP2LC",
  URXIPM3 = "URDPM3LC",
  URXMAD = "URDMADLC",
  URXMB3 = "URDMB3LC",
  URXPHG = "URDPHGLC",
  URXPMM = "URDPMMLC"
)

screen_df <- nh |>
  dplyr::filter(!is.na(WTSAPRP), WTSAPRP > 0)

detection_summary <- lapply(voc_exposures, function(v) {
  cc <- screen_df[[comment_codes[[v]]]]
  wt <- screen_df$WTSAPRP
  ok <- !is.na(cc) & !is.na(wt) & wt > 0
  data.frame(
    variable = v,
    metabolite = unname(voc_names[[v]]),
    group = voc_group_map$group_label[match(v, voc_group_map$variable)],
    n_nonmissing = sum(!is.na(screen_df[[v]])),
    missing_rate = mean(is.na(screen_df[[v]])),
    detect_rate_unweighted = mean(cc[ok] == 0),
    detect_rate_weighted = sum(wt[ok] * (cc[ok] == 0)) / sum(wt[ok]),
    stringsAsFactors = FALSE
  )
}) |>
  dplyr::bind_rows() |>
  dplyr::arrange(group, dplyr::desc(detect_rate_unweighted))

readr_available <- requireNamespace("readr", quietly = TRUE)
if (readr_available) {
  readr::write_csv(detection_summary, file.path(out_dir, paste0(OUTPUT_STEM, "_detection_summary.csv")))
} else {
  utils::write.csv(detection_summary, file.path(out_dir, paste0(OUTPUT_STEM, "_detection_summary.csv")), row.names = FALSE)
}

knitr::kable(
  detection_summary |>
    dplyr::mutate(dplyr::across(c(missing_rate, detect_rate_unweighted, detect_rate_weighted), round, 3)),
  caption = "Detection summary for selected VOC metabolites"
)
```

# Helper Functions

```{r helpers}
`%||%` <- function(x, y) {
  if (is.null(x)) y else x
}

empty_weights <- function() {
  data.frame(
    method = character(),
    seed = integer(),
    variable = character(),
    group = character(),
    direction = character(),
    weight = numeric(),
    stringsAsFactors = FALSE
  )
}

empty_effects <- function() {
  data.frame(
    method = character(),
    seed = integer(),
    term = character(),
    group = character(),
    direction = character(),
    estimate = numeric(),
    std_error = numeric(),
    p_value = numeric(),
    stringsAsFactors = FALSE
  )
}

empty_errors <- function() {
  data.frame(
    method = character(),
    seed = integer(),
    message = character(),
    stringsAsFactors = FALSE
  )
}

empty_survey_diagnostics <- function() {
  data.frame(
    method = character(),
    fit_type = character(),
    seed = integer(),
    survey_degf = numeric(),
    refit_residual_df = numeric(),
    refit_coef_rows = integer(),
    retained_effect_rows = integer(),
    nonzero_positive_coef = integer(),
    nonzero_negative_coef = integer(),
    nonzero_positive_weights = integer(),
    nonzero_negative_weights = integer(),
    positive_weight_sum = numeric(),
    negative_weight_sum = numeric(),
    lambda_path_source = character(),
    lambda_path_length = integer(),
    lambda_path_min = numeric(),
    lambda_path_max = numeric(),
    selected_lambda = numeric(),
    selected_lambda_at_path_boundary = logical(),
    backend_jerr = integer(),
    backend_warnings = character(),
    retained_terms = character(),
    note = character(),
    stringsAsFactors = FALSE
  )
}

weight_group <- function(variable) {
  voc_group_map$group_label[match(variable, voc_group_map$variable)]
}

extract_qgcomp_weights <- function(fit, seed) {
  vars <- c(names(fit$pos.weights), names(fit$neg.weights))
  if (length(vars) == 0) return(empty_weights())
  data.frame(
    method = "qgcomp",
    seed = seed,
    variable = vars,
    group = NA_character_,
    direction = c(rep("Positive", length(fit$pos.weights)), rep("Negative", length(fit$neg.weights))),
    weight = c(as.numeric(fit$pos.weights), as.numeric(fit$neg.weights)),
    stringsAsFactors = FALSE
  )
}

extract_qgcomp_effects <- function(fit, seed) {
  pval <- fit$pval
  pval_psi <- if (!is.null(names(pval)) && "psi1" %in% names(pval)) {
    pval[["psi1"]]
  } else {
    utils::tail(as.numeric(pval), 1)
  }
  data.frame(
    method = "qgcomp",
    seed = seed,
    term = "psi1",
    group = "Overall mixture",
    direction = "Net",
    estimate = as.numeric(fit$psi),
    std_error = sqrt(as.numeric(fit$var.psi)),
    p_value = as.numeric(pval_psi),
    stringsAsFactors = FALSE
  )
}

extract_gwqs_weights <- function(fit, seed) {
  fw <- fit$final_weights
  out <- empty_weights()
  if ("mean_weight_p" %in% names(fw)) {
    out <- dplyr::bind_rows(out, data.frame(
      method = "gWQS",
      seed = seed,
      variable = fw$mix_name,
      group = NA_character_,
      direction = "Positive",
      weight = as.numeric(fw$mean_weight_p),
      stringsAsFactors = FALSE
    ))
  }
  if ("mean_weight_n" %in% names(fw)) {
    out <- dplyr::bind_rows(out, data.frame(
      method = "gWQS",
      seed = seed,
      variable = fw$mix_name,
      group = NA_character_,
      direction = "Negative",
      weight = as.numeric(fw$mean_weight_n),
      stringsAsFactors = FALSE
    ))
  }
  out
}

extract_gwqs_effects <- function(fit, seed) {
  coef_table <- tryCatch(summary(fit$fit)$coefficients, error = function(e) NULL)
  if (is.null(coef_table)) return(empty_effects())
  terms <- intersect(c("pwqs", "nwqs"), rownames(coef_table))
  if (length(terms) == 0) return(empty_effects())
  p_col <- intersect(c("Pr(>|t|)", "Pr(>|z|)", "Pr(>|W|)"), colnames(coef_table))[1]
  data.frame(
    method = "gWQS",
    seed = seed,
    term = terms,
    group = "Overall mixture",
    direction = ifelse(terms == "pwqs", "Positive", "Negative"),
    estimate = coef_table[terms, "Estimate"],
    std_error = coef_table[terms, "Std. Error"],
    p_value = if (!is.na(p_col)) coef_table[terms, p_col] else NA_real_,
    stringsAsFactors = FALSE
  )
}

extract_groupwqs_weights <- function(fit, seed) {
  out <- empty_weights()
  for (i in seq_along(fit$weights)) {
    wi <- fit$weights[[i]]
    out <- dplyr::bind_rows(out, data.frame(
      method = "groupWQS",
      seed = seed,
      variable = names(wi),
      group = weight_group(names(wi)),
      direction = "Combined",
      weight = as.numeric(wi),
      stringsAsFactors = FALSE
    ))
  }
  out
}

extract_groupwqs_effects <- function(fit, seed) {
  coef_table <- tryCatch(summary(fit$fit)$coefficients, error = function(e) NULL)
  if (is.null(coef_table)) return(empty_effects())
  terms <- intersect(paste0("GWQS", seq_along(voc_groups)), rownames(coef_table))
  if (length(terms) == 0) return(empty_effects())
  p_col <- intersect(c("Pr(>|t|)", "Pr(>|z|)", "Pr(>|W|)"), colnames(coef_table))[1]
  data.frame(
    method = "groupWQS",
    seed = seed,
    term = terms,
    group = voc_group_map |>
      dplyr::distinct(group, group_label) |>
      dplyr::arrange(match(group, names(voc_groups))) |>
      dplyr::pull(group_label) |>
      utils::head(length(terms)),
    direction = "Combined",
    estimate = coef_table[terms, "Estimate"],
    std_error = coef_table[terms, "Std. Error"],
    p_value = if (!is.na(p_col)) coef_table[terms, p_col] else NA_real_,
    stringsAsFactors = FALSE
  )
}

extract_sgl_weights <- function(fit, method_label, seed) {
  w <- tryCatch(sglwqs::extract_weights(fit, direction = "both"), error = function(e) NULL)
  if (is.null(w) || nrow(w) == 0) return(empty_weights())
  data.frame(
    method = method_label,
    seed = seed,
    variable = w$variable,
    group = weight_group(w$variable),
    direction = tools::toTitleCase(w$direction),
    weight = w$weight,
    stringsAsFactors = FALSE
  )
}

extract_sgl_effects <- function(fit, method_label, seed) {
  coef_table <- fit$refit_info$coef_table
  if (is.null(coef_table) || nrow(coef_table) == 0) return(empty_effects())
  rn <- rownames(coef_table)
  keep <- grepl("(_pos|_neg)$|^(wqs_pos|wqs_neg)$", rn)
  if (!any(keep)) return(empty_effects())
  p_col <- intersect(c("Pr(>|t|)", "Pr(>|z|)", "Pr(>|W|)", "p.value"), colnames(coef_table))[1]
  terms <- rn[keep]
  group_from_term <- function(term) {
    raw <- sub("(_pos|_neg)$", "", term)
    raw <- sub("^wqs$", "Overall mixture", raw)
    label_map <- voc_group_map |>
      dplyr::distinct(group, group_label)
    out <- label_map$group_label[match(raw, label_map$group)]
    ifelse(is.na(out), raw, out)
  }
  data.frame(
    method = method_label,
    seed = seed,
    term = terms,
    group = vapply(terms, group_from_term, character(1)),
    direction = ifelse(grepl("(_pos$|wqs_pos$)", terms), "Positive", "Negative"),
    estimate = coef_table[keep, "Estimate"],
    std_error = coef_table[keep, "Std. Error"],
    p_value = if (!is.na(p_col)) coef_table[keep, p_col] else NA_real_,
    stringsAsFactors = FALSE
  )
}

extract_sgl_diagnostics <- function(fit, method_label, fit_type, seed,
                                    weight_rows, effect_rows,
                                    survey_design = NULL, note = "") {
  coef_table <- tryCatch(fit$refit_info$coef_table, error = function(e) NULL)
  refit_fit <- tryCatch(fit$refit_info$refit_fit, error = function(e) NULL)
  if (is.null(refit_fit)) {
    refit_fit <- tryCatch(fit$refit_info$fit, error = function(e) NULL)
  }
  residual_df <- tryCatch(stats::df.residual(refit_fit), error = function(e) NA_real_)

  nonzero_positive_coef <- sum(abs(fit$pos_coef) > 1e-12, na.rm = TRUE)
  nonzero_negative_coef <- sum(abs(fit$neg_coef) > 1e-12, na.rm = TRUE)
  nonzero_positive <- sum(weight_rows$direction == "Positive" & weight_rows$weight > 0, na.rm = TRUE)
  nonzero_negative <- sum(weight_rows$direction == "Negative" & weight_rows$weight > 0, na.rm = TRUE)
  positive_weight_sum <- sum(weight_rows$weight[weight_rows$direction == "Positive"], na.rm = TRUE)
  negative_weight_sum <- sum(weight_rows$weight[weight_rows$direction == "Negative"], na.rm = TRUE)
  retained_terms <- if (nrow(effect_rows) > 0) paste(effect_rows$term, collapse = "; ") else ""
  sel_diag <- fit$selection_diagnostics %||% list()
  backend_warnings <- sel_diag$backend_warnings %||% character(0)

  if (!nzchar(note) && nrow(effect_rows) == 0 && (nonzero_positive + nonzero_negative) > 0) {
    note <- "nonzero training weights but no downstream survey-refit index retained; inspect minor-direction threshold, rank, and survey df"
  } else if (!nzchar(note) && nrow(effect_rows) == 0 &&
             (nonzero_positive_coef + nonzero_negative_coef) == 0) {
    note <- "survey-weighted SGL selection returned all-zero exposure coefficients; no downstream survey-refit index retained"
  } else if (!nzchar(note) && nrow(effect_rows) == 0) {
    note <- "no downstream survey-refit index retained"
  }

  data.frame(
    method = method_label,
    fit_type = fit_type,
    seed = seed,
    survey_degf = if (!is.null(survey_design)) survey::degf(survey_design) else NA_real_,
    refit_residual_df = as.numeric(residual_df),
    refit_coef_rows = if (!is.null(coef_table)) nrow(coef_table) else 0L,
    retained_effect_rows = nrow(effect_rows),
    nonzero_positive_coef = nonzero_positive_coef,
    nonzero_negative_coef = nonzero_negative_coef,
    nonzero_positive_weights = nonzero_positive,
    nonzero_negative_weights = nonzero_negative,
    positive_weight_sum = positive_weight_sum,
    negative_weight_sum = negative_weight_sum,
    lambda_path_source = sel_diag$lambda_path_source %||% NA_character_,
    lambda_path_length = sel_diag$lambda_path_length %||% NA_integer_,
    lambda_path_min = sel_diag$lambda_path_min %||% NA_real_,
    lambda_path_max = sel_diag$lambda_path_max %||% NA_real_,
    selected_lambda = sel_diag$selected_lambda %||% NA_real_,
    selected_lambda_at_path_boundary = sel_diag$selected_lambda_at_path_boundary %||% NA,
    backend_jerr = sel_diag$backend_jerr %||% NA_integer_,
    backend_warnings = if (length(backend_warnings) > 0) paste(backend_warnings, collapse = " | ") else "",
    retained_terms = retained_terms,
    note = note,
    stringsAsFactors = FALSE
  )
}

make_sgl_error_diagnostic <- function(method_label, fit_type, seed,
                                      lambda_path = NULL,
                                      survey_design = NULL,
                                      note = "") {
  data.frame(
    method = method_label,
    fit_type = fit_type,
    seed = seed,
    survey_degf = if (!is.null(survey_design)) survey::degf(survey_design) else NA_real_,
    refit_residual_df = NA_real_,
    refit_coef_rows = 0L,
    retained_effect_rows = 0L,
    nonzero_positive_coef = 0L,
    nonzero_negative_coef = 0L,
    nonzero_positive_weights = 0L,
    nonzero_negative_weights = 0L,
    positive_weight_sum = 0,
    negative_weight_sum = 0,
    lambda_path_source = if (is.null(lambda_path)) "sparsegl_auto" else "user_explicit",
    lambda_path_length = if (is.null(lambda_path)) NA_integer_ else length(lambda_path),
    lambda_path_min = if (is.null(lambda_path)) NA_real_ else min(lambda_path),
    lambda_path_max = if (is.null(lambda_path)) NA_real_ else max(lambda_path),
    selected_lambda = NA_real_,
    selected_lambda_at_path_boundary = NA,
    backend_jerr = NA_integer_,
    backend_warnings = "",
    retained_terms = "",
    note = note,
    stringsAsFactors = FALSE
  )
}

safe_fit <- function(method, seed, expr) {
  tryCatch(
    list(result = force(expr), error = NULL),
    error = function(e) list(result = NULL, error = data.frame(
      method = method,
      seed = seed,
      message = conditionMessage(e),
      stringsAsFactors = FALSE
    ))
  )
}
```

# Model Fits

```{r run-models, cache=FALSE}
all_weights <- empty_weights()
all_effects <- empty_effects()
all_errors <- empty_errors()
all_survey_diagnostics <- empty_survey_diagnostics()
model_cache_file <- file.path(cache_dir, paste0(OUTPUT_STEM, "_model_results.rds"))

if (USE_MODEL_CACHE && file.exists(model_cache_file) && !REFRESH_MODEL_CACHE) {
  cached_results <- readRDS(model_cache_file)
  all_weights <- cached_results$all_weights
  all_effects <- cached_results$all_effects
  all_errors <- cached_results$all_errors
  all_survey_diagnostics <- cached_results$all_survey_diagnostics
  message("Loaded cached model results from: ", model_cache_file)
} else {

exposure_formula_part <- paste(voc_exposures, collapse = " + ")
covariate_formula_part <- if (length(covariate_terms) > 0) {
  paste(covariate_terms, collapse = " + ")
} else {
  NULL
}
full_rhs <- paste(c(exposure_formula_part, covariate_formula_part), collapse = " + ")

qgcomp_formula <- stats::as.formula(paste("outcome ~", full_rhs))
gwqs_formula <- stats::as.formula(
  paste("outcome ~ pwqs + nwqs", if (!is.null(covariate_formula_part)) paste("+", covariate_formula_part) else "")
)

sgl_unweighted_specs <- if (RUN_SGLWQS_LAMBDA_COMPARISON) {
  list(
    list(
      label = "SGL-WQS (unweighted, lambda=0)",
      lambda = 0,
      lambda_path = NULL,
      bootstrap = SGL_COMPARE_BOOTSTRAP
    ),
    list(
      label = "SGL-WQS (unweighted, lambda.min path)",
      lambda = "lambda.min",
      lambda_path = SGL_SURVEY_LAMBDA_PATH,
      bootstrap = SGL_COMPARE_BOOTSTRAP
    )
  )
} else {
  list(
    list(
      label = "SGL-WQS (unweighted)",
      lambda = SGL_LAMBDA,
      lambda_path = NULL,
      bootstrap = SGL_BOOTSTRAP
    )
  )
}

sgl_survey_specs <- if (RUN_SGLWQS_LAMBDA_COMPARISON) {
  list(
    list(
      label = "SGL-WQS (survey, lambda=0)",
      lambda = 0,
      lambda_path = NULL,
      bootstrap = FALSE
    ),
    list(
      label = "SGL-WQS (survey, lambda.min path)",
      lambda = "lambda.min",
      lambda_path = SGL_SURVEY_LAMBDA_PATH,
      bootstrap = FALSE
    )
  )
} else {
  list(
    list(
      label = "SGL-WQS (survey)",
      lambda = SGL_LAMBDA,
      lambda_path = SGL_SURVEY_LAMBDA_PATH,
      bootstrap = FALSE
    )
  )
}

method_levels <- c(
  "qgcomp", "gWQS", "groupWQS",
  vapply(sgl_unweighted_specs, `[[`, character(1), "label"),
  vapply(sgl_survey_specs, `[[`, character(1), "label")
)

if (RUN_QGCOMP) {
  qc <- safe_fit("qgcomp", NA_integer_, {
    qgcomp::qgcomp.glm.noboot(
      f = qgcomp_formula,
      expnms = voc_exposures,
      data = model_df[, c("outcome", voc_exposures, covariate_terms), drop = FALSE],
      family = gaussian(),
      q = N_QUANTILES
    )
  })
  if (is.null(qc$error)) {
    all_weights <- dplyr::bind_rows(all_weights, extract_qgcomp_weights(qc$result, seed = NA_integer_))
    all_effects <- dplyr::bind_rows(all_effects, extract_qgcomp_effects(qc$result, seed = NA_integer_))
  } else {
    all_errors <- dplyr::bind_rows(all_errors, qc$error)
  }
}

run_seed_models <- function(seed) {
  old_survey_options <- options(survey.lonely.psu = "adjust")
  on.exit(options(old_survey_options), add = TRUE)

  message("Seed: ", seed)
  seed_weights <- empty_weights()
  seed_effects <- empty_effects()
  seed_errors <- empty_errors()
  seed_survey_diagnostics <- empty_survey_diagnostics()

  if (RUN_GWQS) {
    fit_gwqs <- safe_fit("gWQS", seed, {
      gWQS::gwqs(
        formula = gwqs_formula,
        mix_name = voc_exposures,
        data = model_df[, c("outcome", voc_exposures, covariate_terms), drop = FALSE],
        q = N_QUANTILES,
        validation = 0.4,
        b = N_BOOT,
        b1_pos = TRUE,
        rh = 1,
        family = "gaussian",
        seed = seed,
        plan_strategy = "sequential"
      )
    })
    if (is.null(fit_gwqs$error)) {
      seed_weights <- dplyr::bind_rows(seed_weights, extract_gwqs_weights(fit_gwqs$result, seed))
      seed_effects <- dplyr::bind_rows(seed_effects, extract_gwqs_effects(fit_gwqs$result, seed))
    } else {
      seed_errors <- dplyr::bind_rows(seed_errors, fit_gwqs$error)
    }
  }

  if (RUN_GROUPWQS) {
    fit_groupwqs <- safe_fit("groupWQS", seed, {
      group_list <- unname(voc_groups)
      x_gw <- groupWQS::make.X(model_df, num.groups = length(group_list), groups = group_list)
      x_s <- groupWQS::make.x.s(model_df, num.groups = length(group_list), groups = group_list)
      z <- if (length(covariate_terms) > 0) {
        as.matrix(model_df[, covariate_terms, drop = FALSE])
      } else {
        NULL
      }
      set.seed(seed)
      train_idx <- sort(sample(seq_len(nrow(model_df)), size = round(nrow(model_df) * 0.6)))
      valid_idx <- setdiff(seq_len(nrow(model_df)), train_idx)
      groupWQS::gwqs.fit(
        y = model_df$outcome[valid_idx],
        y.train = model_df$outcome[train_idx],
        x = x_gw[valid_idx, , drop = FALSE],
        x.train = x_gw[train_idx, , drop = FALSE],
        z = if (!is.null(z)) z[valid_idx, , drop = FALSE] else NULL,
        z.train = if (!is.null(z)) z[train_idx, , drop = FALSE] else NULL,
        x.s = x_s,
        B = N_BOOT,
        n.quantiles = N_QUANTILES,
        func = "continuous"
      )
    })
    if (is.null(fit_groupwqs$error)) {
      seed_weights <- dplyr::bind_rows(seed_weights, extract_groupwqs_weights(fit_groupwqs$result, seed))
      seed_effects <- dplyr::bind_rows(seed_effects, extract_groupwqs_effects(fit_groupwqs$result, seed))
    } else {
      seed_errors <- dplyr::bind_rows(seed_errors, fit_groupwqs$error)
    }
  }

  if (RUN_SGLWQS && RUN_SGLWQS_UNWEIGHTED) {
    for (sgl_spec in sgl_unweighted_specs) {
      fit_sgl_unweighted <- safe_fit(sgl_spec$label, seed, {
        sglwqs::sglwqs(
          X = model_df[, voc_exposures, drop = FALSE],
          y = model_df$outcome,
          covariates = if (length(covariate_terms) > 0) model_df[, covariate_terms, drop = FALSE] else NULL,
          groups = voc_groups,
          n_quantiles = N_QUANTILES,
          family = "gaussian",
          lambda = sgl_spec$lambda,
          lambda_path = sgl_spec$lambda_path,
          nfolds = N_FOLDS,
          bootstrap = sgl_spec$bootstrap,
          n_boot = N_BOOT,
          parallel = FALSE,
          refit = "full",
          refit_engine = "glm",
          seed = seed,
          verbose = FALSE
        )
      })
      if (is.null(fit_sgl_unweighted$error)) {
        unweighted_weights <- extract_sgl_weights(fit_sgl_unweighted$result, sgl_spec$label, seed)
        unweighted_effects <- extract_sgl_effects(fit_sgl_unweighted$result, sgl_spec$label, seed)
        seed_weights <- dplyr::bind_rows(seed_weights, unweighted_weights)
        seed_effects <- dplyr::bind_rows(seed_effects, unweighted_effects)
        seed_survey_diagnostics <- dplyr::bind_rows(
          seed_survey_diagnostics,
          extract_sgl_diagnostics(
            fit_sgl_unweighted$result, sgl_spec$label, "unweighted", seed,
            unweighted_weights, unweighted_effects
          )
        )
      } else {
        seed_errors <- dplyr::bind_rows(seed_errors, fit_sgl_unweighted$error)
        seed_survey_diagnostics <- dplyr::bind_rows(
          seed_survey_diagnostics,
          make_sgl_error_diagnostic(
            method_label = sgl_spec$label,
            fit_type = "unweighted",
            seed = seed,
            lambda_path = sgl_spec$lambda_path,
            note = paste("unweighted fit error:", fit_sgl_unweighted$error$message)
          )
        )
      }
    }
  }

  if (RUN_SGLWQS && RUN_SGLWQS_SURVEY) {
    for (sgl_spec in sgl_survey_specs) {
      fit_sgl_survey <- safe_fit(sgl_spec$label, seed, {
        sglwqs::sglwqs(
          X = model_df[, voc_exposures, drop = FALSE],
          y = model_df$outcome,
          covariates = if (length(covariate_terms) > 0) model_df[, covariate_terms, drop = FALSE] else NULL,
          groups = voc_groups,
          n_quantiles = N_QUANTILES,
          family = "gaussian",
          lambda = sgl_spec$lambda,
          lambda_path = sgl_spec$lambda_path,
          nfolds = N_FOLDS,
          bootstrap = sgl_spec$bootstrap,
          n_boot = N_BOOT,
          parallel = FALSE,
          refit = "full",
          refit_engine = "svyglm",
          survey_design = nhanes_design,
          analysis_id = model_df$.analysis_id,
          seed = seed,
          verbose = FALSE
        )
      })
      if (is.null(fit_sgl_survey$error)) {
        survey_weights <- extract_sgl_weights(fit_sgl_survey$result, sgl_spec$label, seed)
        survey_effects <- extract_sgl_effects(fit_sgl_survey$result, sgl_spec$label, seed)
        seed_weights <- dplyr::bind_rows(seed_weights, survey_weights)
        seed_effects <- dplyr::bind_rows(seed_effects, survey_effects)
        seed_survey_diagnostics <- dplyr::bind_rows(
          seed_survey_diagnostics,
          extract_sgl_diagnostics(
            fit_sgl_survey$result, sgl_spec$label, "survey", seed,
            survey_weights, survey_effects, survey_design = nhanes_design
          )
        )
      } else {
        seed_errors <- dplyr::bind_rows(seed_errors, fit_sgl_survey$error)
        seed_survey_diagnostics <- dplyr::bind_rows(
          seed_survey_diagnostics,
          make_sgl_error_diagnostic(
            method_label = sgl_spec$label,
            fit_type = "survey",
            seed = seed,
            lambda_path = sgl_spec$lambda_path,
            survey_design = nhanes_design,
            note = paste("survey fit error:", fit_sgl_survey$error$message)
          )
        )
      }
    }
  }

  list(
    weights = seed_weights,
    effects = seed_effects,
    errors = seed_errors,
    survey_diagnostics = seed_survey_diagnostics
  )
}

with_future_plan <- function(workers, expr) {
  old_plan <- future::plan()
  on.exit(future::plan(old_plan), add = TRUE)
  future::plan(future::multisession, workers = workers)
  force(expr)
}

run_seed_results <- list()
if (length(SEEDS) > 0 && (RUN_GWQS || RUN_GROUPWQS || RUN_SGLWQS)) {
  seed_workers <- min(N_WORKERS, length(SEEDS))
  can_parallelize_seeds <- seed_workers > 1 && !identical(sglwqs_load_mode, "source")

  if (can_parallelize_seeds) {
    message("Running seed-level models with ", seed_workers, " workers.")
    run_seed_results <- with_future_plan(seed_workers, {
      future.apply::future_lapply(
        SEEDS,
        run_seed_models,
        future.seed = TRUE,
        future.scheduling = Inf,
        future.packages = c("gWQS", "groupWQS", "sglwqs", "dplyr", "survey")
      )
    })
  } else {
    if (seed_workers > 1 && identical(sglwqs_load_mode, "source")) {
      message("SGLWQS_LOAD_MODE=source detected; running seed-level models sequentially.")
    }
    run_seed_results <- lapply(SEEDS, run_seed_models)
  }

  all_weights <- dplyr::bind_rows(all_weights, dplyr::bind_rows(lapply(run_seed_results, `[[`, "weights")))
  all_effects <- dplyr::bind_rows(all_effects, dplyr::bind_rows(lapply(run_seed_results, `[[`, "effects")))
  all_errors <- dplyr::bind_rows(all_errors, dplyr::bind_rows(lapply(run_seed_results, `[[`, "errors")))
  all_survey_diagnostics <- dplyr::bind_rows(
    all_survey_diagnostics,
    dplyr::bind_rows(lapply(run_seed_results, `[[`, "survey_diagnostics"))
  )
}

saveRDS(
  list(
    settings = settings_tbl,
    all_weights = all_weights,
    all_effects = all_effects,
    all_errors = all_errors,
    all_survey_diagnostics = all_survey_diagnostics,
    method_levels = method_levels
  ),
  model_cache_file
)
message("Saved model results cache to: ", model_cache_file)
}

method_levels <- unique(c(
  "qgcomp", "gWQS", "groupWQS",
  as.character(all_weights$method),
  as.character(all_effects$method),
  as.character(all_survey_diagnostics$method)
))

all_weights <- all_weights |>
  dplyr::mutate(
    method = factor(method, levels = method_levels)
  )

all_effects <- all_effects |>
  dplyr::mutate(
    method = factor(method, levels = method_levels)
  )

utils::write.csv(all_weights, file.path(out_dir, paste0(OUTPUT_STEM, "_weights.csv")), row.names = FALSE)
utils::write.csv(all_effects, file.path(out_dir, paste0(OUTPUT_STEM, "_effects.csv")), row.names = FALSE)
utils::write.csv(all_errors, file.path(out_dir, paste0(OUTPUT_STEM, "_errors.csv")), row.names = FALSE)
utils::write.csv(all_survey_diagnostics, file.path(out_dir, paste0(OUTPUT_STEM, "_survey_diagnostics.csv")), row.names = FALSE)

cat("Weights rows:", nrow(all_weights), "\n")
cat("Effects rows:", nrow(all_effects), "\n")
cat("Errors rows:", nrow(all_errors), "\n")
cat("Survey diagnostic rows:", nrow(all_survey_diagnostics), "\n")
```

```{r errors}
if (nrow(all_errors) > 0) {
  knitr::kable(all_errors, caption = "Model errors")
} else {
  cat("No model errors recorded.\n")
}
```

```{r survey-diagnostics}
if (nrow(all_survey_diagnostics) > 0) {
  knitr::kable(
    all_survey_diagnostics |>
      dplyr::mutate(dplyr::across(c(survey_degf, refit_residual_df, positive_weight_sum, negative_weight_sum), ~ round(.x, 2))),
    caption = "SGL-WQS selection/refit diagnostics"
  )
  survey_diag <- all_survey_diagnostics |>
    dplyr::filter(fit_type == "survey")
  if (nrow(survey_diag) > 0 &&
      all(survey_diag$nonzero_positive_weights == 0 &
          survey_diag$nonzero_negative_weights == 0)) {
    cat("\n\nAll SGL-WQS survey rows have zero exposure weights in this run. ",
        "Treat the survey branch as a diagnostic failure of survey-weighted selection, ",
        "not as a substantive survey-refit comparison.\n", sep = "")
  }
} else {
  cat("No SGL-WQS survey diagnostics recorded.\n")
}
```

# Results

```{r weight-summary-table}
weight_summary <- all_weights |>
  dplyr::mutate(voc_class = weight_group(variable)) |>
  dplyr::group_by(method, direction, group, variable, voc_class) |>
  dplyr::summarise(
    mean_weight = mean(weight, na.rm = TRUE),
    sd_weight = stats::sd(weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::arrange(method, direction, group, variable)

plot_weight_summary <- weight_summary |>
  dplyr::mutate(
    voc_class = factor(voc_class, levels = unique(voc_group_map$group_label)),
    direction = factor(direction, levels = c("Positive", "Negative", "Combined", "Net"))
  ) |>
  dplyr::filter(!is.na(voc_class), !is.na(direction))

if (SHOW_WEIGHT_TABLES) {
  knitr::kable(
    plot_weight_summary |>
      dplyr::mutate(dplyr::across(c(mean_weight, sd_weight), ~ round(.x, 4))),
    caption = "Variable-level weights by VOC class and direction. qgcomp/gWQS use VOC class only as analyte annotation."
  )
} else {
  cat("Variable-level weight tables are not printed in this HTML. Full weights are saved to `analysis/outputs/", OUTPUT_STEM, "_weights.csv`.\n", sep = "")
}
```

```{r weight-plot, fig.height=10, fig.width=14}
if (SHOW_WEIGHT_FIGURES && nrow(plot_weight_summary) > 0) {
  p_weights <- ggplot(plot_weight_summary, aes(x = variable, y = mean_weight, fill = method)) +
    geom_col(position = position_dodge(width = 0.72), width = 0.66, alpha = 0.85) +
    geom_errorbar(
      aes(ymin = pmax(mean_weight - sd_weight, 0), ymax = mean_weight + sd_weight),
      position = position_dodge(width = 0.72),
      width = 0.18,
      linewidth = 0.25,
      na.rm = TRUE
    ) +
    coord_flip() +
    facet_grid(voc_class ~ direction, scales = "free_y", space = "free_y") +
    labs(
      title = paste0("NHANES VOC demo: Weights by Direction (", length(SEEDS), " seed", ifelse(length(SEEDS) == 1, "", "s"), ")"),
      subtitle = paste0(
        "Modeled after the gWQS::tiwqs_data comparison output. Outcome: ", PRIMARY_OUTCOME,
        "; n = ", nrow(model_df), "; bootstrap B = ", N_BOOT,
        ". groupWQS reports Combined weights; SGL-WQS survey uses design-weighted selection/refit. ",
        "For qgcomp/gWQS, VOC class is analyte annotation only."
      ),
      x = NULL,
      y = "Mean weight"
    ) +
    theme_bw(base_size = 12) +
    theme(
      legend.position = "bottom",
      strip.background = element_rect(fill = "gray95"),
      strip.text = element_text(face = "bold"),
      axis.text.y = element_text(size = 8)
    )
  print(p_weights)

  ggsave(file.path(fig_dir, paste0(OUTPUT_STEM, "_weights.pdf")), p_weights,
         width = 280, height = 260, units = "mm", dpi = 300)
} else {
  cat("Variable-level weight plot is omitted.\n")
}
```

```{r heatmap, fig.height=10, fig.width=12}
if (SHOW_WEIGHT_FIGURES && nrow(plot_weight_summary) > 0) {
  p_heat <- ggplot(plot_weight_summary, aes(x = method, y = variable, fill = mean_weight)) +
    geom_tile(color = "white", linewidth = 0.25) +
    facet_grid(voc_class ~ direction, scales = "free_y", space = "free_y") +
    scale_fill_distiller(palette = "YlOrRd", direction = 1, name = "Mean\nweight") +
    labs(
      title = paste0("NHANES VOC demo: Mean Weight Heatmap (", length(SEEDS), " seed", ifelse(length(SEEDS) == 1, "", "s"), ")"),
      subtitle = "Modeled after the gWQS::tiwqs_data mean-weight heatmap; Combined denotes groupWQS. SGL-WQS survey uses design-weighted selection/refit. For qgcomp/gWQS, VOC class is analyte annotation only.",
      x = NULL,
      y = NULL
    ) +
    theme_minimal(base_size = 12) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.text.y = element_text(size = 8),
      strip.text = element_text(face = "bold")
    )
  print(p_heat)

  ggsave(file.path(fig_dir, paste0(OUTPUT_STEM, "_weight_heatmap.pdf")), p_heat,
         width = 250, height = 260, units = "mm", dpi = 300)
} else {
  cat("Variable-level weight heatmap is omitted.\n")
}
```

```{r weight-stability, fig.height=6, fig.width=12}
weight_cv <- all_weights |>
  dplyr::mutate(voc_class = weight_group(variable)) |>
  dplyr::filter(!is.na(voc_class), !is.na(seed), direction %in% c("Positive", "Negative", "Combined")) |>
  dplyr::group_by(method, variable, voc_class) |>
  dplyr::summarise(
    mean_weight = mean(weight, na.rm = TRUE),
    sd_weight = stats::sd(weight, na.rm = TRUE),
    cv = ifelse(mean_weight > 0.01, sd_weight / mean_weight, NA_real_),
    n = dplyr::n(),
    .groups = "drop"
  ) |>
  dplyr::filter(!is.na(cv), n > 1)

if (SHOW_WEIGHT_FIGURES && nrow(weight_cv) > 0) {
  weight_cv <- weight_cv |>
    dplyr::mutate(voc_class = factor(voc_class, levels = unique(voc_group_map$group_label)))

  p_cv <- ggplot(weight_cv, aes(x = method, y = cv, fill = method)) +
    geom_boxplot(alpha = 0.45, outlier.size = 1) +
    geom_jitter(width = 0.15, size = 1, alpha = 0.55) +
    facet_wrap(~voc_class, nrow = 1) +
    labs(
      title = paste0("NHANES VOC demo: Weight Stability (CV) by Method (", length(SEEDS), " seeds)"),
      subtitle = "Lower CV indicates more stable weights across seeds.",
      x = NULL,
      y = "Coefficient of variation"
    ) +
    theme_bw(base_size = 12) +
    theme(legend.position = "none", axis.text.x = element_text(angle = 30, hjust = 1))
  print(p_cv)

  ggsave(file.path(fig_dir, paste0(OUTPUT_STEM, "_weight_stability_cv.pdf")), p_cv,
         width = 250, height = 120, units = "mm", dpi = 300)
} else {
  cat("Weight stability CV plot requires at least two non-missing seeds per method/variable.\n")
}
```

```{r effect-table}
cat(
  "For SGL-WQS, this table shows indices retained in the downstream refit. ",
  "Directions with non-zero training weights can still be omitted from the refit ",
  "when their index mass is below the minor-direction threshold; variable-level ",
  "weights remain available in the weights CSV.\n",
  sep = ""
)

fmt_p <- function(p_value) {
  ifelse(is.na(p_value), "NA", format.pval(p_value, digits = 3, eps = 0.001))
}

fmt_single_effect <- function(label, estimate, std_error, p_value) {
  sprintf("%s = %.3f (SE = %.3f, p = %s)", label, estimate, std_error, fmt_p(p_value))
}

fmt_seed_summary <- function(label, median_est, q1, q3, se_med, sig_n, n) {
  sprintf(
    "%s: %.3f [%.3f, %.3f] (SE = %.3f), sig %d/%d",
    label, median_est, q1, q3, se_med, sig_n, n
  )
}

effect_stats <- all_effects |>
  dplyr::group_by(method, group, direction, term) |>
  dplyr::summarise(
    n = dplyr::n(),
    median_est = stats::median(estimate, na.rm = TRUE),
    q1 = stats::quantile(estimate, 0.25, na.rm = TRUE),
    q3 = stats::quantile(estimate, 0.75, na.rm = TRUE),
    se_med = stats::median(std_error, na.rm = TRUE),
    sig_n = sum(p_value < 0.05, na.rm = TRUE),
    p_med = stats::median(p_value, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    median_est = ifelse(is.nan(median_est), NA_real_, median_est),
    q1 = ifelse(is.nan(q1), NA_real_, q1),
    q3 = ifelse(is.nan(q3), NA_real_, q3),
    se_med = ifelse(is.nan(se_med), NA_real_, se_med),
    p_med = ifelse(is.nan(p_med), NA_real_, p_med)
  )

format_grouped_stats <- function(dat, empty_message) {
  if (nrow(dat) == 0) return(empty_message)
  dat <- dat |>
    dplyr::mutate(
      scope = ifelse(is.na(group) | group == "", "Overall mixture", group),
      direction = factor(direction, levels = c("Positive", "Negative", "Combined", "Net")),
      effect_label = dplyr::case_when(
        scope == "Overall mixture" & term %in% c("pwqs", "nwqs", "psi1") ~ term,
        TRUE ~ as.character(direction)
      ),
      prefix = ifelse(scope == "Overall mixture", "", paste0(scope, " "))
    ) |>
    dplyr::arrange(scope, direction, term)

  paste(
    sprintf(
      "%s%s",
      dat$prefix,
      mapply(
        fmt_seed_summary,
        label = dat$effect_label,
        median_est = dat$median_est,
        q1 = dat$q1,
        q3 = dat$q3,
        se_med = dat$se_med,
        sig_n = dat$sig_n,
        n = dat$n,
        SIMPLIFY = TRUE
      )
    ),
    collapse = ";<br>"
  )
}

qgcomp_row <- all_effects |>
  dplyr::filter(method == "qgcomp") |>
  dplyr::slice(1)
qgcomp_str <- if (nrow(qgcomp_row) > 0) {
  fmt_single_effect("ψ", qgcomp_row$estimate, qgcomp_row$std_error, qgcomp_row$p_value)
} else {
  "Not run or failed"
}

gwqs_str <- format_grouped_stats(
  effect_stats |> dplyr::filter(method == "gWQS"),
  "Not run or failed"
)

groupwqs_str <- format_grouped_stats(
  effect_stats |> dplyr::filter(method == "groupWQS"),
  "Not run, failed, or no group coefficient returned"
)

sgl_methods <- method_levels[grepl("^SGL-WQS", method_levels)]
sgl_rows <- lapply(sgl_methods, function(m) {
  data.frame(
    Method = m,
    `Estimand / Reporting` = if (grepl("survey", m, ignore.case = TRUE)) {
      "Group × direction-specific survey refit<br>median [IQR], sig/n"
    } else {
      "Group × direction-specific refit<br>median [IQR], sig/n"
    },
    `Key estimates` = format_grouped_stats(
      effect_stats |> dplyr::filter(method == m),
      "No downstream refit index retained in this run"
    ),
    check.names = FALSE
  )
})

method_summary <- dplyr::bind_rows(
  data.frame(
    Method = c("qgcomp", "gWQS", "groupWQS"),
    `Estimand / Reporting` = c(
    "Net mixture effect ψ<br>(unweighted, deterministic)",
    "Two-index overall mixture<br>median [IQR] across seeds",
    "Group-specific β<br>Combined direction, median [IQR]"
    ),
    `Key estimates` = c(qgcomp_str, gwqs_str, groupwqs_str),
    check.names = FALSE
  ),
  dplyr::bind_rows(sgl_rows)
)

knitr::kable(
  method_summary,
  format = "html",
  caption = paste0(
    "NHANES VOC mixture example: effect estimates across methods. ",
    "Output layout follows the gWQS::tiwqs_data comparison table."
  ),
  escape = FALSE
) |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  kableExtra::column_spec(1, bold = TRUE, width = "10em") |>
  kableExtra::column_spec(2, width = "18em") |>
  kableExtra::column_spec(3, width = "52em")
```

```{r sgl-survey-compare, fig.height=6, fig.width=10}
sgl_effects <- all_effects |>
  dplyr::filter(grepl("^SGL-WQS", as.character(method)))

if (nrow(sgl_effects) > 0) {
  p_sgl_eff <- ggplot(sgl_effects, aes(x = group, y = estimate, color = method)) +
    geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.3) +
    geom_point(position = position_dodge(width = 0.45), size = 2) +
    facet_wrap(~direction) +
    coord_flip() +
    labs(
      title = "SGL-WQS downstream refit estimates by analysis variant",
      x = NULL,
      y = "Refit estimate"
    ) +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom")
  print(p_sgl_eff)
  ggsave(file.path(fig_dir, paste0(OUTPUT_STEM, "_sglwqs_survey_vs_unweighted.pdf")),
         p_sgl_eff, width = 220, height = 120, units = "mm", dpi = 300)
} else {
  cat("No SGL-WQS effects available to plot.\n")
}
```

# Notes for Manuscript Use

This analysis is intended as a demonstration rather than a new etiologic claim.
The 16-analyte set keeps only P_UVOC metabolites with at least 75% unweighted
detection among participants with positive VOC subsample weights; quartile
scoring then reduces sensitivity to left-censoring concentrated in the lower
tail. Survey design does not remove LOD/tie issues, but it is relevant for
population-weighted cutpoints, selection weights, and downstream variance
estimation.

The cleanest text framing is:

> We used NHANES 2017-2020 urinary VOC metabolites as a public-data
> demonstration of survey-aware SGL-WQS refitting and bootstrap-based
> uncertainty estimation in an environmental-mixture setting.
