---
title: "n = 100 Rare-Event Sensitivity for Mixture Method Fits"
subtitle: "Original baseline event rate vs increased baseline event rate"
author: "Validation Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    df_print: paged
params:
  run_analysis: true
  n_boot: 200
  n_quantiles: 4
  train_prop: 0.6
  sglwqs_lib: ""
  output_dir: "analysis/outputs/n100_rare_event_failure_sensitivity"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)

Sys.setenv(
  OMP_NUM_THREADS = "1",
  OPENBLAS_NUM_THREADS = "1",
  MKL_NUM_THREADS = "1",
  VECLIB_MAXIMUM_THREADS = "1"
)

input_path <- normalizePath(knitr::current_input(dir = TRUE), mustWork = TRUE)
analysis_dir <- dirname(input_path)
repo_root <- dirname(analysis_dir)
resolve_repo_path <- function(path) {
  if (grepl("^/", path)) normalizePath(path, mustWork = FALSE) else file.path(repo_root, path)
}

if (nzchar(params$sglwqs_lib) && dir.exists(resolve_repo_path(params$sglwqs_lib))) {
  .libPaths(c(normalizePath(resolve_repo_path(params$sglwqs_lib)), .libPaths()))
}

suppressPackageStartupMessages({
  library(MASS)
  library(qgcomp)
  library(gWQS)
  library(groupWQS)
  library(sglwqs)
  library(future)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
  library(kableExtra)
  library(readr)
  library(purrr)
  library(stringr)
})

future::plan(future::sequential)

N_BOOT <- params$n_boot
N_QUANTILES <- params$n_quantiles
TRAIN_PROP <- params$train_prop
OUT_DIR <- resolve_repo_path(params$output_dir)
MANIFEST_DIR <- file.path(OUT_DIR, "manifests")
TABLE_DIR <- file.path(OUT_DIR, "tables")
dir.create(MANIFEST_DIR, recursive = TRUE, showWarnings = FALSE)
dir.create(TABLE_DIR, recursive = TRUE, showWarnings = FALSE)

SEEDS <- c(
  71, 42, 123, 256, 314, 500, 617, 789, 888, 999,
  1001, 1123, 1234, 1357, 1500, 1618, 1729, 1847, 1963, 2048,
  2222, 2345, 2500, 2718, 2801, 3001, 3141, 3333, 3500, 3777
)

SCENARIOS <- tibble::tibble(
  scenario = c("original_rare", "higher_baseline"),
  scenario_label = c("Original rare-event baseline", "Higher baseline event rate"),
  n = 100L,
  intercept = c(-3.0, -1.3)
)

METHODS <- c("qgcomp", "gWQS", "groupWQS", "SGL-WQS")

PCBs <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
Metals <- c("cd", "pb", "hg", "se", "mg")
PFASs <- c("PFOA", "PFNA", "PFOS")
all_exposures <- c(PCBs, Metals, PFASs)
groups <- list(PCBs = PCBs, Metals = Metals, PFASs = PFASs)
group_list <- list(PCBs, Metals, PFASs)

true_directions <- tibble::tibble(
  Variable = all_exposures,
  True_Beta = c(
    0.04, 0.15, 0.20, 0.08, 0.05,
    -0.12, -0.18, 0.10, 0.14, -0.02,
    0, 0, 0
  ),
  Group = c(rep("PCBs", 5), rep("Metals", 5), rep("PFASs", 3))
) |>
  mutate(
    True_Direction = case_when(
      True_Beta > 0.01 ~ "Positive",
      True_Beta < -0.01 ~ "Negative",
      TRUE ~ "None"
    )
  )
```

# Purpose

This targeted sensitivity analysis separates two issues in the previous
sample-size simulation:

1. `n = 100` as a small-sample setting.
2. The extremely small number of outcome events induced by the original
   binary-outcome intercept.

The original scenario uses the same DGM and method settings as
`final_res/compare_mixture_methods_by_samplesize_30seeds.Rmd` for `n = 100`.
The only change in the sensitivity scenario is the outcome intercept, increased
from `-3.0` to `-1.3` to produce a non-rare binary outcome. Bootstrap size,
quantization, train/validation split, covariates, exposures, correlations, and
the 30 seeds are otherwise unchanged.

# Functions

```{r functions}
generate_sglwqs_simdata <- function(n = 100, seed = 71, intercept = -3.0) {
  set.seed(seed)

  sex <- rbinom(n, 1, 0.5)
  age <- pmax(pmin(round(rnorm(n, 50, 12)), 80), 20)
  bmi <- pmax(pmin(round(22 + 0.05 * age + 1.5 * sex + rnorm(n, 0, 4), 1), 45), 15)

  cor_pcb <- matrix(c(
    1.00, 0.60, 0.70, 0.65, 0.60,
    0.60, 1.00, 0.75, 0.70, 0.65,
    0.70, 0.75, 1.00, 0.80, 0.70,
    0.65, 0.70, 0.80, 1.00, 0.75,
    0.60, 0.65, 0.70, 0.75, 1.00
  ), 5, 5)

  pcb <- MASS::mvrnorm(
    n, c(3.5, 3.5, 4.0, 4.5, 3.0),
    diag(c(1.5, 1.5, 1.8, 2.0, 1.5)) %*%
      cor_pcb %*% diag(c(1.5, 1.5, 1.8, 2.0, 1.5))
  )
  colnames(pcb) <- PCBs

  cor_metal <- matrix(c(
    1.00, 0.60, 0.15, 0.10, 0.20,
    0.60, 1.00, 0.10, 0.15, 0.25,
    0.15, 0.10, 1.00, 0.55, 0.20,
    0.10, 0.15, 0.55, 1.00, 0.30,
    0.20, 0.25, 0.20, 0.30, 1.00
  ), 5, 5, byrow = TRUE)

  metal_raw <- MASS::mvrnorm(
    n, log(c(0.5, 2, 1, 100, 20)),
    diag(c(0.6, 0.8, 0.5, 0.3, 0.25)) %*%
      cor_metal %*% diag(c(0.6, 0.8, 0.5, 0.3, 0.25))
  )
  metal <- exp(metal_raw)
  colnames(metal) <- Metals

  pfas <- pmax(MASS::mvrnorm(n, c(3, 1.5, 5), diag(c(2, 1, 3.5))), 0.1)
  colnames(pfas) <- PFASs

  beta_pcb <- c(0.04, 0.15, 0.20, 0.08, 0.05)
  beta_metal <- c(-0.12, -0.18, 0.10, 0.14, -0.02)
  beta_pfas <- c(0, 0, 0)

  eta <- as.numeric(
    intercept +
      scale(pcb) %*% beta_pcb +
      scale(metal) %*% beta_metal +
      scale(pfas) %*% beta_pfas +
      sex * 0.3 + (age - 50) / 10 * 0.02 + (bmi - 25) / 5 * 0.05
  )

  Y <- rbinom(n, 1, stats::plogis(eta))

  result <- data.frame(pcb, metal, pfas, sex = sex, age = age, bmi = bmi, Y = Y)
  attr(result, "true_beta") <- list(
    pcb = setNames(beta_pcb, PCBs),
    metal = setNames(beta_metal, Metals),
    pfas = setNames(beta_pfas, PFASs)
  )
  result
}

make_validation_split <- function(y, train_prop, seed) {
  set.seed(seed)
  ns <- asNamespace("sglwqs")
  if (exists(".stratified_validation_train_idx", envir = ns, inherits = FALSE)) {
    fn <- get(".stratified_validation_train_idx", envir = ns, inherits = FALSE)
    return(fn(y, train_prop = train_prop, n = length(y)))
  }
  sample(seq_along(y), floor(length(y) * train_prop))
}

event_summary <- function(dat, seed) {
  train_idx <- make_validation_split(dat$Y, train_prop = TRAIN_PROP, seed = seed)
  valid_idx <- setdiff(seq_len(nrow(dat)), train_idx)
  tibble::tibble(
    event_rate = mean(dat$Y),
    total_events = sum(dat$Y),
    train_n = length(train_idx),
    valid_n = length(valid_idx),
    train_events = sum(dat$Y[train_idx]),
    valid_events = sum(dat$Y[valid_idx]),
    train_non_events = sum(dat$Y[train_idx] == 0),
    valid_non_events = sum(dat$Y[valid_idx] == 0)
  )
}

with_captured_warnings <- function(expr) {
  warnings <- character()
  value <- withCallingHandlers(
    expr,
    warning = function(w) {
      warnings <<- c(warnings, conditionMessage(w))
      invokeRestart("muffleWarning")
    }
  )
  list(value = value, warnings = unique(warnings))
}

direction_accuracy <- function(detected) {
  chk <- tibble::tibble(
    Variable = names(detected),
    Detected = unname(detected)
  ) |>
    left_join(true_directions |> select(Variable, True_Direction), by = "Variable")
  mean(chk$Detected == chk$True_Direction | chk$True_Direction == "None", na.rm = TRUE)
}

manifest_path <- function(scenario, seed, method) {
  safe_method <- gsub("[^A-Za-z0-9]+", "_", method)
  file.path(MANIFEST_DIR, sprintf("%s_seed%04d_%s.rds", scenario, seed, safe_method))
}

base_result <- function(scenario_row, seed, method, dat, ev) {
  tibble::tibble(
    scenario = scenario_row$scenario,
    scenario_label = scenario_row$scenario_label,
    n = scenario_row$n,
    intercept = scenario_row$intercept,
    seed = seed,
    method = method,
    event_rate = ev$event_rate,
    total_events = ev$total_events,
    train_n = ev$train_n,
    valid_n = ev$valid_n,
    train_events = ev$train_events,
    valid_events = ev$valid_events,
    train_non_events = ev$train_non_events,
    valid_non_events = ev$valid_non_events,
    fit_success = FALSE,
    direction_accuracy = NA_real_,
    estimate_pos = NA_real_,
    estimate_neg = NA_real_,
    sgl_all_zero_exposure = NA,
    sgl_boot_success_rate = NA_real_,
    warning_messages = NA_character_,
    error_message = NA_character_,
    runtime_sec = NA_real_
  )
}

fit_qgcomp <- function(dat, seed) {
  form <- as.formula(paste("Y ~", paste(all_exposures, collapse = " + "), "+ sex + age + bmi"))
  fit <- qgcomp::qgcomp.glm.noboot(
    form,
    expnms = all_exposures,
    data = dat,
    family = binomial(),
    q = N_QUANTILES
  )
  detected <- setNames(rep("Negative", length(all_exposures)), all_exposures)
  detected[names(fit$pos.weights)] <- "Positive"
  list(
    fit = fit,
    direction_accuracy = direction_accuracy(detected),
    estimate_pos = unname(fit$pos.psi %||% NA_real_),
    estimate_neg = unname(fit$neg.psi %||% NA_real_)
  )
}

fit_gwqs <- function(dat, seed) {
  form <- Y ~ pwqs + nwqs + sex + age + bmi
  fit <- gWQS::gwqs(
    form,
    mix_name = all_exposures,
    data = dat,
    q = N_QUANTILES,
    validation = 0.4,
    b = N_BOOT,
    b1_pos = TRUE,
    rh = 1,
    family = "binomial",
    seed = seed,
    plan_strategy = "sequential"
  )
  fw <- fit$final_weights
  detected <- setNames(
    ifelse(fw$mean_weight_p >= fw$mean_weight_n, "Positive", "Negative"),
    fw$mix_name
  )
  co <- stats::coef(fit$fit)
  list(
    fit = fit,
    direction_accuracy = direction_accuracy(detected[all_exposures]),
    estimate_pos = unname(co["pwqs"] %||% NA_real_),
    estimate_neg = unname(co["nwqs"] %||% NA_real_)
  )
}

fit_groupwqs <- function(dat, seed) {
  X_gw <- groupWQS::make.X(dat, num.groups = 3, groups = group_list)
  x_s <- groupWQS::make.x.s(dat, num.groups = 3, groups = group_list)
  n_total <- nrow(dat)
  n_train <- round(n_total * TRAIN_PROP)
  set.seed(seed)
  train_idx <- sample(seq_len(n_total), size = n_train)
  valid_idx <- setdiff(seq_len(n_total), train_idx)
  fit <- groupWQS::gwqs.fit(
    y = dat$Y[valid_idx],
    y.train = dat$Y[train_idx],
    x = X_gw[valid_idx, ],
    x.train = X_gw[train_idx, ],
    x.s = x_s,
    B = N_BOOT,
    n.quantiles = N_QUANTILES,
    func = "binary"
  )
  co <- stats::coef(fit$fit)
  group_coefs <- co[grep("^GWQS", names(co))]
  detected <- c(
    setNames(rep(ifelse(group_coefs[1] >= 0, "Positive", "Negative"), length(PCBs)), PCBs),
    setNames(rep(ifelse(group_coefs[2] >= 0, "Positive", "Negative"), length(Metals)), Metals),
    setNames(rep(ifelse(group_coefs[3] >= 0, "Positive", "Negative"), length(PFASs)), PFASs)
  )
  list(
    fit = fit,
    direction_accuracy = direction_accuracy(detected[all_exposures]),
    estimate_pos = NA_real_,
    estimate_neg = NA_real_
  )
}

fit_sglwqs <- function(dat, seed) {
  fit <- sglwqs::sglwqs(
    X = dat[, all_exposures],
    y = dat$Y,
    covariates = dat[, c("sex", "age", "bmi")],
    groups = groups,
    family = "binomial",
    n_quantiles = N_QUANTILES,
    bootstrap = TRUE,
    n_boot = N_BOOT,
    parallel = FALSE,
    validation = TRUE,
    train_prop = TRAIN_PROP,
    seed = seed
  )
  pos_w <- fit$pos_weights %||% setNames(rep(0, length(all_exposures)), all_exposures)
  neg_w <- fit$neg_weights %||% setNames(rep(0, length(all_exposures)), all_exposures)
  detected <- setNames(
    ifelse(pos_w[all_exposures] > neg_w[all_exposures], "Positive", "Negative"),
    all_exposures
  )
  boot_success_rate <- NA_real_
  if (!is.null(fit$boot_info$n_success) && !is.null(fit$boot_info$n_boot)) {
    boot_success_rate <- fit$boot_info$n_success / fit$boot_info$n_boot
  } else if (!is.null(fit$boot_info$successful_bootstraps)) {
    boot_success_rate <- mean(fit$boot_info$successful_bootstraps)
  }
  list(
    fit = fit,
    direction_accuracy = direction_accuracy(detected),
    estimate_pos = unname(fit$pos_index_sum %||% NA_real_),
    estimate_neg = unname(fit$neg_index_sum %||% NA_real_),
    sgl_all_zero_exposure = isTRUE(sum(abs(pos_w), na.rm = TRUE) == 0 && sum(abs(neg_w), na.rm = TRUE) == 0),
    sgl_boot_success_rate = boot_success_rate
  )
}

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x

run_one_method <- function(scenario_row, seed, method) {
  dat <- generate_sglwqs_simdata(n = scenario_row$n, seed = seed, intercept = scenario_row$intercept)
  ev <- event_summary(dat, seed)
  out <- base_result(scenario_row, seed, method, dat, ev)
  start_time <- Sys.time()

  ans <- tryCatch(
    with_captured_warnings({
      if (identical(method, "qgcomp")) {
        fit_qgcomp(dat, seed)
      } else if (identical(method, "gWQS")) {
        fit_gwqs(dat, seed)
      } else if (identical(method, "groupWQS")) {
        fit_groupwqs(dat, seed)
      } else if (identical(method, "SGL-WQS")) {
        fit_sglwqs(dat, seed)
      } else {
        stop("Unknown method: ", method)
      }
    }),
    error = function(e) {
      list(error = conditionMessage(e), warnings = character())
    }
  )

  out$runtime_sec <- as.numeric(difftime(Sys.time(), start_time, units = "secs"))

  if (!is.null(ans$error)) {
    out$error_message <- ans$error
    out$warning_messages <- paste(ans$warnings, collapse = " | ")
    return(out)
  }

  val <- ans$value
  out$fit_success <- TRUE
  out$direction_accuracy <- val$direction_accuracy %||% NA_real_
  out$estimate_pos <- val$estimate_pos %||% NA_real_
  out$estimate_neg <- val$estimate_neg %||% NA_real_
  out$sgl_all_zero_exposure <- val$sgl_all_zero_exposure %||% NA
  out$sgl_boot_success_rate <- val$sgl_boot_success_rate %||% NA_real_
  out$warning_messages <- paste(ans$warnings, collapse = " | ")
  out
}
```

# Run or Resume Analysis

```{r run-analysis}
jobs <- tidyr::crossing(SCENARIOS, seed = SEEDS, method = METHODS)
jobs <- jobs |>
  mutate(path = pmap_chr(list(scenario, seed, method), manifest_path))

cat("sglwqs package:", as.character(utils::packageVersion("sglwqs")), "\n")
cat("sglwqs path:", system.file(package = "sglwqs"), "\n")
cat("Total jobs:", nrow(jobs), "\n")
cat("Existing manifests:", sum(file.exists(jobs$path)), "\n")

if (isTRUE(params$run_analysis)) {
  for (i in seq_len(nrow(jobs))) {
    if (file.exists(jobs$path[i])) next
    cat(sprintf(
      "[%03d/%03d] %s seed=%d method=%s\n",
      i, nrow(jobs), jobs$scenario[i], jobs$seed[i], jobs$method[i]
    ))
    row <- jobs[i, ]
    result <- run_one_method(row, row$seed, row$method)
    saveRDS(result, row$path)
  }
}

cat("Completed manifests:", sum(file.exists(jobs$path)), "\n")
```

# Results

```{r collect-results}
result_files <- list.files(MANIFEST_DIR, pattern = "[.]rds$", full.names = TRUE)
if (!length(result_files)) {
  cat("No completed manifests are available yet. Re-render with params$run_analysis = TRUE.\n")
  knitr::knit_exit()
}
results <- purrr::map_dfr(result_files, readRDS)
readr::write_csv(results, file.path(TABLE_DIR, "n100_rare_event_method_results.csv"))

event_results <- results |>
  distinct(
    scenario, scenario_label, n, intercept, seed,
    event_rate, total_events, train_n, valid_n, train_events, valid_events,
    train_non_events, valid_non_events
  )
readr::write_csv(event_results, file.path(TABLE_DIR, "n100_rare_event_event_counts.csv"))

event_summary_tbl <- event_results |>
  group_by(scenario, scenario_label, intercept) |>
  summarise(
    seeds = n(),
    event_rate_mean = mean(event_rate),
    event_rate_sd = sd(event_rate),
    total_events_mean = mean(total_events),
    total_events_min = min(total_events),
    total_events_max = max(total_events),
    train_events_mean = mean(train_events),
    train_events_min = min(train_events),
    train_events_max = max(train_events),
    valid_events_mean = mean(valid_events),
    valid_events_min = min(valid_events),
    valid_events_max = max(valid_events),
    seeds_train_events_le_2 = sum(train_events <= 2),
    seeds_valid_events_le_2 = sum(valid_events <= 2),
    .groups = "drop"
  )
readr::write_csv(event_summary_tbl, file.path(TABLE_DIR, "n100_rare_event_event_summary.csv"))

method_summary <- results |>
  group_by(scenario, scenario_label, intercept, method) |>
  summarise(
    attempted = n(),
    fit_success = sum(fit_success, na.rm = TRUE),
    fit_failure = attempted - fit_success,
    fit_failure_rate = fit_failure / attempted,
    direction_accuracy_mean = mean(direction_accuracy, na.rm = TRUE),
    direction_accuracy_sd = sd(direction_accuracy, na.rm = TRUE),
    runtime_median_sec = median(runtime_sec, na.rm = TRUE),
    sgl_all_zero_rate = mean(sgl_all_zero_exposure %in% TRUE, na.rm = TRUE),
    sgl_boot_success_rate_mean = mean(sgl_boot_success_rate, na.rm = TRUE),
    .groups = "drop"
  )
readr::write_csv(method_summary, file.path(TABLE_DIR, "n100_rare_event_method_summary.csv"))

failure_details <- results |>
  filter(!fit_success | !is.na(error_message) & nzchar(error_message)) |>
  select(scenario, scenario_label, seed, method, total_events, train_events, valid_events, error_message, warning_messages)
readr::write_csv(failure_details, file.path(TABLE_DIR, "n100_rare_event_failure_details.csv"))
```

## Event Counts

```{r event-summary-table}
event_summary_tbl |>
  mutate(
    event_rate = sprintf("%.1f%% (SD %.1f%%)", 100 * event_rate_mean, 100 * event_rate_sd),
    total_events = sprintf("%.1f [%d, %d]", total_events_mean, total_events_min, total_events_max),
    train_events = sprintf("%.1f [%d, %d]", train_events_mean, train_events_min, train_events_max),
    valid_events = sprintf("%.1f [%d, %d]", valid_events_mean, valid_events_min, valid_events_max)
  ) |>
  select(
    Scenario = scenario_label,
    Intercept = intercept,
    Seeds = seeds,
    `Event rate` = event_rate,
    `Total events mean [min,max]` = total_events,
    `Training events mean [min,max]` = train_events,
    `Validation events mean [min,max]` = valid_events,
    `Seeds with <=2 training events` = seeds_train_events_le_2,
    `Seeds with <=2 validation events` = seeds_valid_events_le_2
  ) |>
  kable(caption = "Outcome event counts by scenario", align = "lrrrrrrr") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r event-count-plot}
ggplot(event_results, aes(x = scenario_label, y = train_events, fill = scenario_label)) +
  geom_boxplot(width = 0.55, outlier.shape = NA, alpha = 0.65) +
  geom_jitter(width = 0.08, height = 0, size = 2, alpha = 0.8) +
  geom_hline(yintercept = 2, linetype = "dashed", color = "firebrick") +
  scale_fill_brewer(palette = "Set2") +
  labs(x = NULL, y = "Training-set event count", fill = NULL) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Fit Success and Failure

```{r method-summary-table}
method_summary |>
  mutate(
    `Failure rate` = sprintf("%d/%d (%.1f%%)", fit_failure, attempted, 100 * fit_failure_rate),
    `Accuracy mean (SD)` = ifelse(
      is.nan(direction_accuracy_mean),
      NA_character_,
      sprintf("%.1f%% (%.1f%%)", 100 * direction_accuracy_mean, 100 * direction_accuracy_sd)
    ),
    `Median runtime, sec` = sprintf("%.1f", runtime_median_sec),
    `SGL all-zero rate` = ifelse(
      method == "SGL-WQS",
      sprintf("%.1f%%", 100 * sgl_all_zero_rate),
      NA_character_
    ),
    `SGL bootstrap success` = ifelse(
      method == "SGL-WQS",
      sprintf("%.1f%%", 100 * sgl_boot_success_rate_mean),
      NA_character_
    )
  ) |>
  select(
    Scenario = scenario_label,
    Method = method,
    `Failure rate`,
    `Accuracy mean (SD)`,
    `Median runtime, sec`,
    `SGL all-zero rate`,
    `SGL bootstrap success`
  ) |>
  arrange(Scenario, Method) |>
  kable(caption = "Method fit success/failure by n = 100 event-rate scenario") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r failure-details-table}
if (nrow(failure_details)) {
  failure_details |>
    mutate(error_message = stringr::str_trunc(error_message, 120)) |>
    arrange(scenario, method, seed) |>
    kable(caption = "Failure details") |>
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE)
} else {
  cat("No method failures among completed jobs.\n")
}
```

```{r success-plot}
ggplot(method_summary, aes(x = method, y = 1 - fit_failure_rate, fill = scenario_label)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = NULL, y = "Fit success rate", fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Interpretation

The primary use of this sensitivity analysis is diagnostic rather than a new
performance benchmark. If failures concentrate in the original `intercept =
-3.0` condition and are attenuated in the higher-baseline condition, the `n =
100` failures can be described as being driven by rare binary outcomes after
the training/validation split and resampling, rather than by `n = 100` alone.

The companion CSV files are saved under:

```{r output-paths, echo=FALSE}
cat(normalizePath(TABLE_DIR), sep = "\n")
```
