---
title: "Comparison with Other Methods"
subtitle: "SGL-WQS vs WQS vs qgcomp vs groupWQS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison with Other Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  comment = "#>", 
  eval = FALSE,
  fig.width = 10,
  fig.height = 7,
  out.width = "100%",
  dpi = 150
)
N_BOOT <- 500
```

## Overview

This vignette compares SGL-WQS with established mixture methods.

| Method | Bidirectional | Variable Selection | Group Structure |
|--------|---------------|-------------------|-----------------|
| WQS (gWQS) | Yes (2-index) | No | No |
| qgcomp | Yes | No | No |
| groupWQS | Yes | No | Yes |
| **SGL-WQS** | Yes | **Yes** | **Yes** |

**Common settings**: Bootstrap = `r N_BOOT`, Validation split = 60/40

---

## Comparison 1: WQS vs SGL-WQS (PCB Data)

**Data**: `gWQS::wqs_data` (continuous outcome)

### gWQS (2-index model)

```{r wqs-gwqs}
library(gWQS)
data("wqs_data")
PCBs <- names(wqs_data)[grepl("^LBX", names(wqs_data))]

# 2-index model: positive AND negative directions
gwqs_fit <- gwqs(
  yLBX ~ pwqs + nwqs,  # Both positive and negative WQS indices
  mix_name = PCBs, 
  data = wqs_data, 
  q = 10, 
  validation = 0.6, 
  b = 500,
  b1_pos = TRUE, 
  rh = 1,
  family = "gaussian", 
  seed = 2016
)

summary(gwqs_fit)
gwqs_barplot(gwqs_fit)

# Extract weights for comparison
weights_gwqs_pos <- data.frame(
  variable = gwqs_fit$final_weights$mix_name,
  weight = gwqs_fit$final_weights$mean_weight_p,
  direction = "Positive",
  method = "gWQS"
)
weights_gwqs_neg <- data.frame(
  variable = gwqs_fit$final_weights$mix_name,
  weight = gwqs_fit$final_weights$mean_weight_n,
  direction = "Negative",
  method = "gWQS"
)
```

### SGL-WQS

```{r wqs-sglwqs}
library(sglwqs)
library(future)

plan(multisession, workers = 10)

sglwqs_fit <- sglwqs(
  X = wqs_data[, PCBs],
  y = wqs_data$yLBX,
  groups = list(PCBs = PCBs),
  n_quantiles = 10, 
  bootstrap = TRUE,
  n_boot = 500,
  parallel = TRUE,
  validation = TRUE,
  train_prop = 0.6,
  seed = 123
)

plan(sequential)

# Results
summary(sglwqs_fit)
plot_weights(sglwqs_fit)
inference_table(sglwqs_fit)
```

---

## Comparison 2: qgcomp vs SGL-WQS (Metals Data)

**Data**: `qgcomp::metals` (binary outcome)

### qgcomp

```{r qgcomp_noboot}
library(qgcomp)
data("metals", package = "qgcomp")

Xnm <- c('arsenic', 'barium', 'cadmium', 'calcium', 'chromium', 'copper',
         'iron', 'lead', 'magnesium', 'manganese', 'mercury', 'selenium', 
         'silver', 'sodium', 'zinc')

qc_noboot <- qgcomp.glm.noboot(
  disease_state ~ ., 
  expnms = Xnm, 
  data = metals[, c(Xnm, 'disease_state')], 
  family = binomial(), 
  q = 4
)

qc_noboot
plot(qc_noboot)
```

```{r qgcomp}
qgcomp_fit <- qgcomp.boot(
  disease_state ~ .,
  data = metals[, c("disease_state", Xnm)],
  family = binomial(),
  q = 10,
  B = 500,
  seed = 123
)

summary(qgcomp_fit)
plot(qgcomp_fit)

# Extract weights
weights_qgcomp <- data.frame(
  variable = c(names(qc_noboot$pos.weights), names(qc_noboot$neg.weights)),
  weight = c(qc_noboot$pos.weights, qc_noboot$neg.weights),
  direction = c(rep("Positive", length(qc_noboot$pos.weights)),
                rep("Negative", length(qc_noboot$neg.weights))),
  method = "qgcomp"
)
```

### SGL-WQS

```{r qgcomp-sglwqs}
plan(multisession, workers = 10)

sglwqs_fit2 <- sglwqs(
  X = metals[, Xnm],
  y = metals$disease_state,
  family = "binomial",
  groups = list(Metals = Xnm),
  n_quantiles = 10,
  bootstrap = TRUE,
  n_boot = 500,
  parallel = TRUE,
  validation = TRUE,
  train_prop = 0.6,
  seed = 123
)

plan(sequential)

summary(sglwqs_fit2)
plot_weights(sglwqs_fit2)
inference_table(sglwqs_fit2)
```

---

## Comparison 3: groupWQS vs SGL-WQS (Multiple Groups)

**Data**: `groupWQS::simdata` (binary outcome, 3 chemical groups)

### groupWQS

```{r groupwqs}
library(groupWQS)
data("simdata", package = "groupWQS")

PCBs_g <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_192")
metals_g <- c("as", "cu", "pb", "sn")
pesticides <- c("carbaryl", "propoxur", "methoxychlor", "diazinon", "chlorpyrifos")

all_vars_g <- c(PCBs_g, metals_g, pesticides)

group_list <- list(PCBs_g, metals_g, pesticides)
X_gwqs <- make.X(simdata, num.groups = 3, groups = group_list)
x.s <- make.x.s(simdata, num.groups = 3, groups = group_list)

n_total <- nrow(simdata)
n_train <- 700
Y.train <- simdata$Y[1:n_train]
Y.valid <- simdata$Y[(n_train + 1):n_total]
X.train <- X_gwqs[1:n_train, ]
X.valid <- X_gwqs[(n_train + 1):n_total, ]

gwqs_group_fit <- gwqs.fit(
  y = Y.valid, 
  y.train = Y.train, 
  x = X.valid, 
  x.train = X.train, 
  x.s = x.s, 
  B = N_BOOT,
  n.quantiles = 4, 
  func = "binary"
)

print(gwqs_group_fit)

# Extract weights
# Extract weights from groupWQS
extract_weights_groupwqs <- function(fit, var_names, group_list, method_name = "groupWQS") {

  # Get GLM coefficients (excluding Intercept)
  glm_coefs <- coef(fit$fit)
  gwqs_coefs <- glm_coefs[grep("^GWQS", names(glm_coefs))]
  
  # Get weights
  weights_list <- fit$weights
  
  # Data frame to store results
  result <- data.frame()
  
  for (i in seq_along(weights_list)) {
    grp_weights <- weights_list[[i]]
    grp_coef <- gwqs_coefs[i]
    
    # Determine direction based on coefficient sign
    if (grp_coef >= 0) {
      direction <- "Positive"
    } else {
      direction <- "Negative"
    }
    
    df_grp <- data.frame(
      variable = names(grp_weights),
      weight = as.numeric(grp_weights),
      direction = direction,
      method = method_name,
      stringsAsFactors = FALSE
    )
    
    result <- rbind(result, df_grp)
  }
  
  return(result)
}

weights_groupwqs <- extract_weights_groupwqs(gwqs_group_fit)
```

### SGL-WQS

```{r groupwqs-sglwqs, fig.height=9}
all_vars_g <- c(PCBs_g, metals_g, pesticides)

plan(multisession, workers = 10)

sglwqs_fit3 <- sglwqs(
  X = simdata[, all_vars_g],
  y = simdata$Y,
  family = "binomial",
  groups = list(
    PCBs = PCBs_g, 
    Metals = metals_g, 
    Pesticides = pesticides
  ),
  n_quantiles = 4,
  bootstrap = TRUE,
  n_boot = 500,
  parallel = TRUE,
  validation = TRUE,
  train_prop = 0.7,
  seed = 123
)

plan(sequential)

summary(sglwqs_fit3)
plot_weights(sglwqs_fit3)
inference_table(sglwqs_fit3)
```

```{r combined-plot, fig.width=12, fig.height=10}
plot_combined_results(sglwqs_fit3)
```

---

## Feature Comparison

| Feature | gWQS | qgcomp | groupWQS | SGL-WQS |
|---------|------|--------|----------|---------|
| Variable selection (sparse) | × | × | × | ○ |
| Bidirectional effects | ○ (2-index) | ○ | △ | ○ |
| Group structure | × | × | ○ | ○ |
| Train/Validation split | ○ | × | ○ | ○ |
| Bootstrap | ○ | ○ | ○ | ○ |
| Covariate adjustment | ○ | ○ | △ | ○ |
| Statistical inference | ○ | ○ | ○ | ○ |
| Parallel processing | × | × | × | ○ |
| Checkpoint recovery | × | × | × | ○ |
| Large data scalability | △ | △ | △ | ○ |

---

## Scalability and Computational Efficiency

SGL-WQS is designed for large-scale epidemiological studies with robust engineering:

### Batched Parallel Processing

SGL-WQS employs a batched parallelization strategy with memory management, enabling efficient bootstrapping even for large cohorts (N = 100,000) on standard workstations.

**Automatic memory management**: When data exceeds 100MB, SGL-WQS automatically adjusts the `future.globals.maxSize` setting to prevent worker errors.

```{r large-scale-example, eval=FALSE}
library(sglwqs)
library(future)

plan(multisession, workers = 10)

# For large datasets, sglwqs auto-detects and adjusts memory settings
fit <- sglwqs(
  X = large_data[, exposures],  # e.g., N = 100,000
  y = large_data$outcome,
  groups = groups,
  family = "binomial",
  bootstrap = TRUE,
  n_boot = 500,
  parallel = TRUE,
  validation = TRUE,
  checkpoint_dir = "sglwqs_checkpoint",    # Save progress periodically
  checkpoint_interval = 50,                 # Every 50 iterations
  # future_globals_max_size = NULL,         # Auto-detect (default)
  # future_globals_max_size = 2000 * 1024^2,  # Or specify manually: 2GB
  seed = 123
)
# Output: "Large dataset detected (250 MB). Auto-setting future.globals.maxSize to 1000 MB"

plan(sequential)
```

### Comparison with Other Methods

In our testing with N = 100,000 and 500 bootstrap iterations:

| Method | Memory Usage | Crash Recovery | Completion |
|--------|--------------|----------------|------------|
| gWQS | High (all in memory) | No | May fail |
| qgcomp | High | No | May fail |
| groupWQS | High | No | May fail |
| **SGL-WQS** | Managed (batched) | **Yes** | Stable |

Key advantages:
- **Memory management**: Results saved to disk periodically, reducing memory pressure
- **Crash recovery**: Resume from checkpoint if interrupted
- **Progress monitoring**: Check completed iterations via checkpoint file
- **Configurable data transfer**: `future_globals_max_size` prevents worker errors

### Recommended Settings by Data Size

| Sample Size | Bootstrap | Checkpoint | Workers | Estimated Time |
|-------------|-----------|------------|---------|----------------|
| N < 10,000 | 500 | Optional | 4-8 | < 30 min |
| N = 10,000-50,000 | 500 | Recommended | 8-10 | 1-2 hours |
| N > 50,000 | 500 | Required | 10+ | 2-4 hours |
| N = 100,000 | 500 | Required | 10+ | 3-5 hours |

Note: Times are approximate and depend on hardware, number of exposures, and complexity.

---

## Recommendations

| Scenario | Recommended Method |
|----------|-------------------|
| Simple exploratory analysis | qgcomp |
| Traditional WQS comparison | gWQS (2-index) |
| Clear group structure | groupWQS or SGL-WQS |
| Variable selection needed | SGL-WQS |
| Groups + individual importance | SGL-WQS |
| Missing data | sglwqs_mice |
