---
title: "Convergence and failure-rate summary"
subtitle: "Unified failure table for qgcomp, gWQS, groupWQS, and SGL-WQS"
author: "SGL-WQS reviewer response"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)

repo_root <- normalizePath(file.path(getwd(), if (dir.exists("analysis")) "." else ".."))
source(file.path(repo_root, "analysis", "_sglwqs_review_helpers.R"))
load_review_packages(c(
  "MASS", "Matrix", "dplyr", "tidyr", "ggplot2", "knitr", "kableExtra",
  "qgcomp", "gWQS", "groupWQS", "pkgload"
))
sglwqs_source <- load_review_sglwqs(root = repo_root)

RUN_MODE <- review_run_mode()
IS_FULL <- identical(RUN_MODE, "full")
N_WORKERS <- review_workers(RUN_MODE)
N_BOOT_SMALL <- as.integer(Sys.getenv("SGLWQS_FAILURE_N_BOOT", if (IS_FULL) 50 else 5))
N_SEEDS_SMALL <- as.integer(Sys.getenv("SGLWQS_FAILURE_SEEDS", if (IS_FULL) 30 else 2))
NFOLDS <- as.integer(Sys.getenv("SGLWQS_NFOLDS", if (IS_FULL) 5 else 3))
NLAMBDA <- as.integer(Sys.getenv("SGLWQS_NLAMBDA", if (IS_FULL) 25 else 8))
SMALL_NS <- as.integer(strsplit(Sys.getenv("SGLWQS_FAILURE_NS", "100,200"), ",")[[1]])

groups <- review_groups()
exposures <- review_exposures(groups)
output_dir <- file.path(repo_root, "analysis", "outputs")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
```

# Configuration

```{r configuration}
config <- data.frame(
  item = c("run_mode", "sglwqs_source", "workers", "small_run_n",
           "small_run_seeds", "small_run_bootstraps", "nfolds", "nlambda"),
  value = c(RUN_MODE, sglwqs_source$source, N_WORKERS,
            paste(SMALL_NS, collapse = ", "), N_SEEDS_SMALL,
            N_BOOT_SMALL, NFOLDS, NLAMBDA)
)
knitr::kable(config, caption = "Analysis configuration") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Existing cached comparison results

```{r cache-loaders}
cache_bases <- c(
  file.path(repo_root, "final_res", "compare_mixture_methods_by_samplesize_30seeds_cache",
            "html", "run-analysis_eddc57c06de07419047d1c0dd34ae45b"),
  file.path(repo_root, "first_res", "compare_mixture_methods_by_samplesize_30seeds_cache",
            "html", "run-analysis_eddc57c06de07419047d1c0dd34ae45b"),
  file.path(repo_root, "final_res", "compare_mixture_methods_43vars_30seeds_cache",
            "html", "run-analysis_78a57f39df73ee0be1914af6f57fcc6e"),
  file.path(repo_root, "first_res", "compare_mixture_methods_43vars_30seeds_cache",
            "html", "run-analysis_78a57f39df73ee0be1914af6f57fcc6e")
)

load_comparison_cache <- function(base) {
  loaded <- lazy_load_cache(base)
  if (is.null(loaded) || is.null(loaded$all_results)) {
    return(NULL)
  }
  loaded$all_results
}

cached_result_sets <- lapply(cache_bases, load_comparison_cache)
names(cached_result_sets) <- basename(dirname(dirname(dirname(cache_bases))))
cached_result_sets <- Filter(Negate(is.null), cached_result_sets)

data.frame(
  cache = names(cached_result_sets),
  n_result_objects = vapply(cached_result_sets, length, integer(1))
) %>%
  knitr::kable(caption = "Cached result sets found") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r cached-failure-table}
extract_cached_failures <- function(results, source_label) {
  dplyr::bind_rows(lapply(results, function(res) {
    if (is.null(res$n) || is.null(res$seed)) {
      return(data.frame())
    }
    methods <- c(qgcomp = "qgcomp", gwqs = "gWQS",
                 groupwqs = "groupWQS", sglwqs = "SGL-WQS")
    dplyr::bind_rows(lapply(names(methods), function(key) {
      err <- res[[paste0(key, "_error")]]
      success_key <- switch(
        key,
        qgcomp = "qgcomp_weights",
        gwqs = "gwqs_weights",
        groupwqs = "groupwqs_weights",
        sglwqs = "sglwqs_weights"
      )
      data.frame(
        source = source_label,
        n = res$n,
        seed = res$seed,
        method = methods[[key]],
        attempted = TRUE,
        succeeded = is.null(err) && !is.null(res[[success_key]]),
        error = if (is.null(err)) NA_character_ else as.character(err),
        error_class = if (is.null(err)) NA_character_ else classification_from_error(err),
        stringsAsFactors = FALSE
      )
    }))
  }))
}

cached_failures <- dplyr::bind_rows(Map(extract_cached_failures,
                                        cached_result_sets,
                                        names(cached_result_sets)))

cached_failure_summary <- cached_failures %>%
  dplyr::group_by(source, n, method) %>%
  dplyr::summarise(
    attempted = dplyr::n(),
    succeeded = sum(succeeded),
    failed = attempted - succeeded,
    failure_rate = failed / attempted,
    .groups = "drop"
  )

knitr::kable(
  cached_failure_summary %>%
    dplyr::mutate(failure_rate = sprintf("%.1f%%", 100 * failure_rate)),
  caption = "Failure rates reconstructed from cached 30-seed comparison results"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Additional n = 100/200 failure-diagnostic run

```{r small-grid}
small_grid <- tidyr::expand_grid(
  n = SMALL_NS,
  seed = review_seeds(N_SEEDS_SMALL)
) %>%
  dplyr::mutate(row_id = dplyr::row_number())

knitr::kable(small_grid, caption = "Additional small-n diagnostic grid") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r small-run}
run_qgcomp_failure <- function(dat) {
  form <- stats::as.formula(
    paste("Y ~", paste(exposures, collapse = " + "), "+ sex + age + bmi")
  )
  tryCatch({
    fit <- qgcomp::qgcomp.glm.noboot(
      form, expnms = exposures, data = dat, family = binomial(), q = 4
    )
    list(ok = TRUE, error = NA_character_, extra = list(psi = fit$psi))
  }, error = function(e) {
    list(ok = FALSE, error = conditionMessage(e), extra = list())
  })
}

run_gwqs_failure <- function(dat, seed) {
  tryCatch({
    fit <- gWQS::gwqs(
      Y ~ pwqs + nwqs + sex + age + bmi,
      mix_name = exposures,
      data = dat,
      q = 4,
      validation = 0.4,
      b = N_BOOT_SMALL,
      b1_pos = TRUE,
      rh = 1,
      family = "binomial",
      seed = seed,
      plan_strategy = "sequential"
    )
    list(ok = TRUE, error = NA_character_, extra = list(converged = fit$fit$converged))
  }, error = function(e) {
    list(ok = FALSE, error = conditionMessage(e), extra = list())
  })
}

run_groupwqs_failure <- function(dat, seed) {
  tryCatch({
    group_list <- unname(groups)
    X_gw <- groupWQS::make.X(dat, num.groups = length(group_list), groups = group_list)
    x_s <- groupWQS::make.x.s(dat, num.groups = length(group_list), groups = group_list)
    set.seed(seed)
    train_idx <- sample(seq_len(nrow(dat)), size = round(nrow(dat) * 0.6))
    valid_idx <- setdiff(seq_len(nrow(dat)), train_idx)
    fit <- groupWQS::gwqs.fit(
      y = dat$Y[valid_idx],
      y.train = dat$Y[train_idx],
      x = X_gw[valid_idx, , drop = FALSE],
      x.train = X_gw[train_idx, , drop = FALSE],
      x.s = x_s,
      B = N_BOOT_SMALL,
      n.quantiles = 4,
      func = "binary"
    )
    list(ok = TRUE, error = NA_character_, extra = list(rank = fit$fit$rank))
  }, error = function(e) {
    list(ok = FALSE, error = conditionMessage(e), extra = list())
  })
}

run_sgl_failure <- function(dat, seed) {
  fit_res <- safe_sglwqs(
    data = dat,
    exposures = exposures,
    groups = groups,
    family = "binomial",
    validation = TRUE,
    bootstrap = TRUE,
    n_boot = N_BOOT_SMALL,
    parallel = FALSE,
    seed = seed,
    nfolds = NFOLDS,
    nlambda = NLAMBDA,
    minor_threshold = 0.10,
    verbose = FALSE
  )
  if (!isTRUE(fit_res$ok)) {
    return(list(ok = FALSE, error = fit_res$error, diag = data.frame()))
  }
  list(ok = TRUE, error = NA_character_,
       diag = extract_sglwqs_diagnostics_row(fit_res$fit))
}

run_one_small <- function(row) {
  load_review_sglwqs(root = repo_root)
  dat <- simulate_review_mixture(
    n = row$n,
    seed = row$seed,
    correlation = 0.5,
    outcome = "binomial",
    scenario = "active"
  )

  qg <- run_qgcomp_failure(dat)
  gw <- run_gwqs_failure(dat, row$seed + 1000L)
  gr <- run_groupwqs_failure(dat, row$seed + 2000L)
  sg <- run_sgl_failure(dat, row$seed + 3000L)

  base <- dplyr::bind_rows(
    data.frame(n = row$n, seed = row$seed, method = "qgcomp",
               succeeded = qg$ok, error = qg$error),
    data.frame(n = row$n, seed = row$seed, method = "gWQS",
               succeeded = gw$ok, error = gw$error),
    data.frame(n = row$n, seed = row$seed, method = "groupWQS",
               succeeded = gr$ok, error = gr$error),
    data.frame(n = row$n, seed = row$seed, method = "SGL-WQS",
               succeeded = sg$ok, error = sg$error)
  ) %>%
    dplyr::mutate(
      source = "additional_n100_n200",
      attempted = TRUE,
      error_class = vapply(error, classification_from_error, character(1))
    )

  if (nrow(sg$diag) > 0L) {
    base <- base %>%
      dplyr::left_join(
        cbind(data.frame(n = row$n, seed = row$seed, method = "SGL-WQS"), sg$diag),
        by = c("n", "seed", "method")
      )
  }
  base
}

small_failures <- dplyr::bind_rows(
  review_lapply(split(seq_len(nrow(small_grid)), seq_len(nrow(small_grid))), function(i) {
    run_one_small(small_grid[i, , drop = FALSE])
  }, workers = if (IS_FULL) N_WORKERS else 1L)
)

if (requireNamespace("readr", quietly = TRUE)) {
  readr::write_csv(small_failures,
                   file.path(output_dir, "convergence_failure_small_runs.csv"))
} else {
  utils::write.csv(small_failures,
                   file.path(output_dir, "convergence_failure_small_runs.csv"),
                   row.names = FALSE)
}
```

```{r small-summary}
small_failure_summary <- small_failures %>%
  dplyr::group_by(n, method) %>%
  dplyr::summarise(
    attempted = dplyr::n(),
    succeeded = sum(succeeded),
    failed = attempted - succeeded,
    failure_rate = failed / attempted,
    .groups = "drop"
  )

knitr::kable(
  small_failure_summary %>%
    dplyr::mutate(failure_rate = sprintf("%.1f%%", 100 * failure_rate)),
  caption = "Additional small-n failure rates"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# SGL-WQS failure subtypes and diagnostics

```{r sgl-subtypes}
sgl_subtypes <- small_failures %>%
  dplyr::filter(method == "SGL-WQS") %>%
  dplyr::mutate(
    failure_subtype = dplyr::case_when(
      !succeeded ~ error_class,
      all_zero_weights %in% TRUE ~ "all_zero_weights",
      rank_deficient %in% TRUE ~ "rank_deficiency",
      validation_estimable %in% FALSE ~ "validation_not_estimable",
      is.finite(bootstrap_success_rate) & bootstrap_success_rate < 1 ~ "partial_bootstrap_failure",
      lambda_at_path_edge %in% TRUE ~ "lambda_path_edge",
      TRUE ~ "succeeded_no_flag"
    )
  ) %>%
  dplyr::count(n, failure_subtype, name = "n_runs")

knitr::kable(
  sgl_subtypes,
  caption = "SGL-WQS diagnostic subtypes in the additional small-n run"
) %>%
  kableExtra::kable_styling(full_width = FALSE)

sgl_diag_summary <- small_failures %>%
  dplyr::filter(method == "SGL-WQS", succeeded) %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(
    median_bootstrap_success_rate = stats::median(bootstrap_success_rate, na.rm = TRUE),
    all_zero_rate = mean(all_zero_weights, na.rm = TRUE),
    rank_deficiency_rate = mean(rank_deficient, na.rm = TRUE),
    validation_not_estimable_rate = mean(!validation_estimable, na.rm = TRUE),
    lambda_edge_rate = mean(lambda_at_path_edge, na.rm = TRUE),
    median_nonzero_weights = stats::median(n_nonzero, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  sgl_diag_summary %>%
    dplyr::mutate(dplyr::across(
      c(median_bootstrap_success_rate, all_zero_rate, rank_deficiency_rate,
        validation_not_estimable_rate, lambda_edge_rate),
      ~ sprintf("%.1f%%", 100 * .x)
    )),
  caption = "SGL-WQS diagnostic rates among successful small-n fits"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Unified reviewer-facing table

```{r unified-table}
unified <- dplyr::bind_rows(
  cached_failures %>%
    dplyr::select(source, n, seed, method, attempted, succeeded, error, error_class),
  small_failures %>%
    dplyr::select(source, n, seed, method, attempted, succeeded, error, error_class)
) %>%
  dplyr::group_by(source, n, method) %>%
  dplyr::summarise(
    attempted = dplyr::n(),
    succeeded = sum(succeeded),
    failed = attempted - succeeded,
    failure_rate = failed / attempted,
    most_common_error = {
      errs <- error_class[!is.na(error_class)]
      if (length(errs) == 0L) NA_character_ else names(sort(table(errs), decreasing = TRUE))[1]
    },
    .groups = "drop"
  )

knitr::kable(
  unified %>%
    dplyr::mutate(failure_rate = sprintf("%.1f%%", 100 * failure_rate)) %>%
    dplyr::arrange(n, method, source),
  caption = "Unified failure-rate table"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r unified-plot}
if (nrow(unified) > 0L) {
  ggplot(unified, aes(x = factor(n), y = failure_rate, fill = method)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    facet_wrap(~source, scales = "free_x") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(x = "Sample size", y = "Failure rate",
         fill = "Method",
         title = "Failure rates by method and sample size") +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

# Reviewer-language summary target

```{r reviewer-summary}
reviewer_summary <- unified %>%
  dplyr::filter(n %in% c(100, 200)) %>%
  dplyr::select(source, n, method, attempted, failed, failure_rate, most_common_error) %>%
  dplyr::arrange(n, method)

knitr::kable(
  reviewer_summary %>%
    dplyr::mutate(failure_rate = sprintf("%.1f%%", 100 * failure_rate)),
  caption = "n < 200 reviewer-summary table"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

This table is designed to support cautious wording for very small samples:
SGL-WQS remains useful for structured, sparse index estimation, but at
`n < 200` the validation and bootstrap diagnostics should be inspected and
qgcomp can be a more robust default when the analysis priority is a stable
overall mixture effect estimate rather than structured variable selection.

# Session information

```{r session-info}
sessionInfo()
```
