---
title: "Effect-estimate bias, RMSE, and coverage"
subtitle: "Common all-exposure quantile contrast where estimands are comparable by construction"
author: "SGL-WQS reviewer response"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)

repo_root <- normalizePath(file.path(getwd(), if (dir.exists("analysis")) "." else ".."))
source(file.path(repo_root, "analysis", "_sglwqs_review_helpers.R"))
load_review_packages(c(
  "MASS", "Matrix", "dplyr", "tidyr", "ggplot2", "knitr", "kableExtra",
  "qgcomp", "gWQS", "groupWQS", "pkgload"
))
sglwqs_source <- load_review_sglwqs(root = repo_root)

RUN_MODE <- review_run_mode()
IS_FULL <- identical(RUN_MODE, "full")
N_WORKERS <- review_workers(RUN_MODE)
N <- as.integer(Sys.getenv("SGLWQS_EFFECT_N", if (IS_FULL) 1000 else 180))
N_SEEDS <- as.integer(Sys.getenv("SGLWQS_EFFECT_SEEDS", if (IS_FULL) 30 else 3))
N_BOOT <- as.integer(Sys.getenv("SGLWQS_EFFECT_BOOT", if (IS_FULL) 50 else 5))
NFOLDS <- as.integer(Sys.getenv("SGLWQS_NFOLDS", if (IS_FULL) 5 else 3))
NLAMBDA <- as.integer(Sys.getenv("SGLWQS_NLAMBDA", if (IS_FULL) 25 else 8))

groups <- review_groups()
exposures <- review_exposures(groups)
output_dir <- file.path(repo_root, "analysis", "outputs")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
```

# Configuration

```{r configuration}
config <- data.frame(
  item = c("run_mode", "sglwqs_source", "workers", "n", "seeds",
           "bootstrap_iterations_for_WQS_methods", "nfolds", "nlambda"),
  value = c(RUN_MODE, sglwqs_source$source, N_WORKERS, N, N_SEEDS,
            N_BOOT, NFOLDS, NLAMBDA)
)
knitr::kable(config, caption = "Analysis configuration") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

The outcome is generated from quantized exposures, so the common target is the
link-scale contrast for increasing every exposure by one quantile. qgcomp targets
this contrast most directly. gWQS, groupWQS, and SGL-WQS estimate index-based
contrasts; for comparability here we compute the implied all-exposure contrast
from their fitted downstream index coefficients and weights. These rows are
therefore annotated as index-implied approximations.

# Simulation grid

```{r grid}
grid <- data.frame(
  seed = review_seeds(N_SEEDS),
  row_id = seq_len(N_SEEDS)
)

knitr::kable(grid, caption = "Seeds") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Method runners

```{r runners}
normal_row <- function(method, seed, true_target, estimate, se,
                       estimand_note, ok = TRUE, error = NA_character_) {
  ci_lower <- estimate - stats::qnorm(0.975) * se
  ci_upper <- estimate + stats::qnorm(0.975) * se
  data.frame(
    method = method,
    seed = seed,
    true_target = true_target,
    estimate = estimate,
    std_error = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper,
    covered = ci_lower <= true_target & ci_upper >= true_target,
    ok = ok,
    error = error,
    estimand_note = estimand_note,
    stringsAsFactors = FALSE
  )
}

error_row <- function(method, seed, true_target, error, estimand_note) {
  data.frame(
    method = method,
    seed = seed,
    true_target = true_target,
    estimate = NA_real_,
    std_error = NA_real_,
    ci_lower = NA_real_,
    ci_upper = NA_real_,
    covered = NA,
    ok = FALSE,
    error = error,
    estimand_note = estimand_note,
    stringsAsFactors = FALSE
  )
}

run_qgcomp_effect <- function(dat, seed, true_target) {
  form <- stats::as.formula(
    paste("Y ~", paste(exposures, collapse = " + "), "+ sex + age + bmi")
  )
  tryCatch({
    fit <- qgcomp::qgcomp.glm.noboot(
      form, expnms = exposures, data = dat, family = gaussian(), q = 4
    )
    normal_row(
      method = "qgcomp",
      seed = seed,
      true_target = true_target,
      estimate = as.numeric(fit$psi),
      se = sqrt(as.numeric(fit$var.psi)),
      estimand_note = "Direct all-exposure one-quantile contrast"
    )
  }, error = function(e) {
    error_row("qgcomp", seed, true_target, conditionMessage(e),
              "Direct all-exposure one-quantile contrast")
  })
}

run_gwqs_effect <- function(dat, seed, true_target) {
  tryCatch({
    fit <- gWQS::gwqs(
      Y ~ pwqs + nwqs + sex + age + bmi,
      mix_name = exposures,
      data = dat,
      q = 4,
      validation = 0.4,
      b = N_BOOT,
      b1_pos = TRUE,
      rh = 1,
      family = "gaussian",
      seed = seed,
      plan_strategy = "sequential"
    )
    co <- stats::coef(fit$fit)
    vc <- stats::vcov(fit$fit)
    terms <- intersect(c("pwqs", "nwqs"), names(co))
    estimate <- sum(co[terms])
    se <- sqrt(sum(vc[terms, terms, drop = FALSE]))
    normal_row(
      method = "gWQS",
      seed = seed,
      true_target = true_target,
      estimate = as.numeric(estimate),
      se = as.numeric(se),
      estimand_note = "Two-index WQS implied all-exposure contrast"
    )
  }, error = function(e) {
    error_row("gWQS", seed, true_target, conditionMessage(e),
              "Two-index WQS implied all-exposure contrast")
  })
}

run_groupwqs_effect <- function(dat, seed, true_target) {
  tryCatch({
    group_list <- unname(groups)
    X_gw <- groupWQS::make.X(dat, num.groups = length(group_list), groups = group_list)
    x_s <- groupWQS::make.x.s(dat, num.groups = length(group_list), groups = group_list)
    set.seed(seed)
    train_idx <- sample(seq_len(nrow(dat)), size = round(nrow(dat) * 0.6))
    valid_idx <- setdiff(seq_len(nrow(dat)), train_idx)
    fit <- groupWQS::gwqs.fit(
      y = dat$Y[valid_idx],
      y.train = dat$Y[train_idx],
      x = X_gw[valid_idx, , drop = FALSE],
      x.train = X_gw[train_idx, , drop = FALSE],
      x.s = x_s,
      B = N_BOOT,
      n.quantiles = 4,
      func = "continuous"
    )
    co <- stats::coef(fit$fit)
    vc <- stats::vcov(fit$fit)
    terms <- grep("^GWQS", names(co), value = TRUE)
    estimate <- sum(co[terms])
    se <- sqrt(sum(vc[terms, terms, drop = FALSE]))
    normal_row(
      method = "groupWQS",
      seed = seed,
      true_target = true_target,
      estimate = as.numeric(estimate),
      se = as.numeric(se),
      estimand_note = "Group-index implied all-exposure contrast"
    )
  }, error = function(e) {
    error_row("groupWQS", seed, true_target, conditionMessage(e),
              "Group-index implied all-exposure contrast")
  })
}

run_sglwqs_effect <- function(dat, seed, true_target) {
  fit_res <- safe_sglwqs(
    data = dat,
    exposures = exposures,
    groups = groups,
    family = "gaussian",
    covariates = c("sex", "age", "bmi"),
    validation = TRUE,
    bootstrap = FALSE,
    seed = seed,
    nfolds = NFOLDS,
    nlambda = NLAMBDA,
    minor_threshold = 0.10,
    verbose = FALSE
  )
  if (!isTRUE(fit_res$ok)) {
    return(error_row("SGL-WQS", seed, true_target, fit_res$error,
                     "Sparse group index-implied all-exposure contrast"))
  }
  fit <- fit_res$fit
  vals <- lapply(names(groups), function(grp) {
    gv <- fit$validation_info$group_results[[grp]]
    pos_mass <- fit$pos_index_sum_by_group[[grp]] %||% 0
    neg_mass <- fit$neg_index_sum_by_group[[grp]] %||% 0
    data.frame(
      estimate_part = c(gv$pos_estimate * pos_mass, gv$neg_estimate * neg_mass),
      se_part = c(gv$pos_se * pos_mass, gv$neg_se * neg_mass)
    )
  })
  parts <- dplyr::bind_rows(vals)
  estimate <- sum(parts$estimate_part, na.rm = TRUE)
  se <- sqrt(sum(parts$se_part^2, na.rm = TRUE))
  normal_row(
    method = "SGL-WQS",
    seed = seed,
    true_target = true_target,
    estimate = estimate,
    se = se,
    estimand_note = "Sparse group index-implied all-exposure contrast"
  )
}
```

# Run analysis

```{r run-analysis}
run_one_seed <- function(row) {
  load_review_sglwqs(root = repo_root)
  dat <- simulate_quantile_estimand_data(
    n = N,
    seed = row$seed,
    correlation = 0.5,
    noise_sd = 2.5
  )
  true_target <- attr(dat, "true_all_exposure_contrast")
  dplyr::bind_rows(
    run_qgcomp_effect(dat, row$seed, true_target),
    run_gwqs_effect(dat, row$seed + 1000L, true_target),
    run_groupwqs_effect(dat, row$seed + 2000L, true_target),
    run_sglwqs_effect(dat, row$seed + 3000L, true_target)
  )
}

effect_results <- dplyr::bind_rows(
  review_lapply(split(seq_len(nrow(grid)), seq_len(nrow(grid))), function(i) {
    run_one_seed(grid[i, , drop = FALSE])
  }, workers = if (IS_FULL) N_WORKERS else 1L)
)

effect_results$error_class <- vapply(effect_results$error, classification_from_error, character(1))

if (requireNamespace("readr", quietly = TRUE)) {
  readr::write_csv(effect_results,
                   file.path(output_dir, "effect_estimate_bias_coverage.csv"))
} else {
  utils::write.csv(effect_results,
                   file.path(output_dir, "effect_estimate_bias_coverage.csv"),
                   row.names = FALSE)
}
```

# Bias, RMSE, and coverage

```{r performance}
failure_summary <- effect_results %>%
  dplyr::group_by(method) %>%
  dplyr::summarise(
    attempted = dplyr::n(),
    succeeded = sum(ok),
    failed = attempted - succeeded,
    failure_rate = failed / attempted,
    .groups = "drop"
  )

knitr::kable(
  failure_summary %>%
    dplyr::mutate(failure_rate = sprintf("%.1f%%", 100 * failure_rate)),
  caption = "Effect-estimate run success/failure counts"
) %>%
  kableExtra::kable_styling(full_width = FALSE)

performance <- effect_results %>%
  dplyr::filter(ok, is.finite(estimate), is.finite(std_error)) %>%
  dplyr::mutate(
    bias = estimate - true_target,
    squared_error = bias^2
  ) %>%
  dplyr::group_by(method, estimand_note) %>%
  dplyr::summarise(
    n_success = dplyr::n(),
    true_target = mean(true_target),
    mean_estimate = mean(estimate),
    bias = mean(bias),
    rmse = sqrt(mean(squared_error)),
    mean_se = mean(std_error),
    coverage_95 = mean(covered, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  performance %>%
    dplyr::mutate(dplyr::across(
      c(true_target, mean_estimate, bias, rmse, mean_se, coverage_95),
      ~ round(.x, 3)
    )),
  caption = "Bias, RMSE, and 95% CI coverage for the common contrast"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r estimate-plot}
plot_df <- effect_results %>% dplyr::filter(ok, is.finite(estimate))
if (nrow(plot_df) > 0L) {
  ggplot(plot_df, aes(x = method, y = estimate, fill = method)) +
    geom_hline(aes(yintercept = true_target), linetype = "dashed", color = "grey35") +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_point(position = position_jitter(width = 0.08), size = 1.7, alpha = 0.8) +
    labs(x = NULL, y = "Estimated all-exposure contrast",
         title = "Distribution of method-specific contrast estimates") +
    theme_minimal() +
    theme(legend.position = "none")
}
```

```{r coverage-plot}
if (nrow(performance) > 0L) {
  ggplot(performance, aes(x = method, y = coverage_95, fill = method)) +
    geom_col(width = 0.65) +
    geom_hline(yintercept = 0.95, linetype = "dashed", color = "firebrick") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
    labs(x = NULL, y = "95% CI coverage",
         title = "Coverage for the common contrast") +
    theme_minimal() +
    theme(legend.position = "none")
}
```

# Estimand notes

```{r notes}
notes <- effect_results %>%
  dplyr::distinct(method, estimand_note) %>%
  dplyr::arrange(method)

knitr::kable(notes, caption = "Estimand notes") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Session information

```{r session-info}
sessionInfo()
```
