---
title: "Minor direction threshold sensitivity"
subtitle: "Controlled minor/major coefficient-mass ratio DGM; SGL-WQS only"
author: "SGL-WQS reviewer response"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)

repo_root <- normalizePath(file.path(getwd(), if (dir.exists("analysis")) "." else ".."))
source(file.path(repo_root, "analysis", "_sglwqs_review_helpers.R"))
load_review_packages(c(
  "MASS", "Matrix", "dplyr", "tidyr", "ggplot2", "knitr", "kableExtra", "pkgload"
))
sglwqs_source <- load_review_sglwqs(root = repo_root)

RUN_MODE <- review_run_mode()
IS_FULL <- identical(RUN_MODE, "full")
N_WORKERS <- review_workers(RUN_MODE)
N <- as.integer(Sys.getenv("SGLWQS_MINOR_N", if (IS_FULL) 900 else 160))
N_SEEDS <- as.integer(Sys.getenv("SGLWQS_MINOR_SEEDS", if (IS_FULL) 30 else 4))
NFOLDS <- as.integer(Sys.getenv("SGLWQS_NFOLDS", if (IS_FULL) 5 else 3))
NLAMBDA <- as.integer(Sys.getenv("SGLWQS_NLAMBDA", if (IS_FULL) 25 else 8))
RATIOS <- as.numeric(strsplit(Sys.getenv("SGLWQS_MINOR_RATIOS", "0.05,0.10,0.15,0.25,0.40"), ",")[[1]])
THRESHOLDS <- as.numeric(strsplit(Sys.getenv("SGLWQS_MINOR_THRESHOLDS", "0,0.10,0.25,0.40"), ",")[[1]])

mix_vars <- paste0("mix_", seq_len(8))
groups <- list(Mixture = mix_vars)
output_dir <- file.path(repo_root, "analysis", "outputs")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
```

# Configuration

```{r configuration}
config <- data.frame(
  item = c("run_mode", "sglwqs_source", "workers", "n", "seeds",
           "true_minor_major_ratios", "thresholds", "nfolds", "nlambda"),
  value = c(RUN_MODE, sglwqs_source$source, N_WORKERS, N, N_SEEDS,
            paste(RATIOS, collapse = ", "), paste(THRESHOLDS, collapse = ", "),
            NFOLDS, NLAMBDA)
)
knitr::kable(config, caption = "Analysis configuration") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

The data-generating model contains one exposure group with both positive and
negative coefficients. The negative coefficient mass is scaled so that the
true minor/major mass ratio is approximately 0.05, 0.10, 0.15, 0.25, or 0.40.
The default SGL-WQS rule excludes the fitted minor direction from the validation
GLM when the fitted minor/major mass ratio is below `minor_threshold = 0.10`.

# Simulation grid

```{r grid}
grid <- tidyr::expand_grid(
  true_ratio = RATIOS,
  threshold = THRESHOLDS,
  seed = review_seeds(N_SEEDS)
) %>%
  dplyr::mutate(row_id = dplyr::row_number())

knitr::kable(head(grid, 12), caption = "First rows of the threshold grid") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Run SGL-WQS fits

```{r run-grid}
run_one_threshold <- function(row) {
  load_review_sglwqs(root = repo_root)
  dat <- simulate_minor_ratio_data(
    n = N,
    seed = row$seed,
    ratio = row$true_ratio,
    correlation = 0.5,
    noise_sd = 1.0
  )
  fit_res <- safe_sglwqs(
    data = dat,
    exposures = mix_vars,
    groups = groups,
    family = "gaussian",
    covariates = c("z1", "z2"),
    validation = TRUE,
    bootstrap = FALSE,
    seed = row$seed + 500000L + round(row$threshold * 1000),
    nfolds = NFOLDS,
    nlambda = NLAMBDA,
    minor_threshold = row$threshold,
    verbose = FALSE
  )

  if (!isTRUE(fit_res$ok)) {
    return(data.frame(
      true_ratio = row$true_ratio,
      threshold = row$threshold,
      seed = row$seed,
      ok = FALSE,
      error = fit_res$error,
      error_class = classification_from_error(fit_res$error),
      fitted_ratio = NA_real_,
      fitted_minor_direction = NA_character_,
      excluded_minor = NA,
      pos_estimate = NA_real_,
      pos_pvalue = NA_real_,
      neg_estimate = NA_real_,
      neg_pvalue = NA_real_,
      contrast_estimate = NA_real_,
      true_contrast = NA_real_,
      stringsAsFactors = FALSE
    ))
  }

  fit <- fit_res$fit
  pos_mass <- fit$pos_index_sum_by_group$Mixture %||% 0
  neg_mass <- fit$neg_index_sum_by_group$Mixture %||% 0
  fitted_ratio <- if (max(pos_mass, neg_mass) > 0) {
    min(pos_mass, neg_mass) / max(pos_mass, neg_mass)
  } else {
    NA_real_
  }
  fitted_minor_direction <- if (!is.finite(fitted_ratio)) {
    NA_character_
  } else if (pos_mass < neg_mass) {
    "positive"
  } else {
    "negative"
  }

  gv <- fit$validation_info$group_results$Mixture
  pos_excluded <- isTRUE(gv$pos_excluded)
  neg_excluded <- isTRUE(gv$neg_excluded)
  excluded_minor <- (identical(fitted_minor_direction, "positive") && pos_excluded) ||
    (identical(fitted_minor_direction, "negative") && neg_excluded)

  true_beta <- attr(dat, "true_beta")
  true_contrast <- sum(true_beta)
  contrast_estimate <- sum(c(
    (gv$pos_estimate %||% NA_real_) * pos_mass,
    (gv$neg_estimate %||% NA_real_) * neg_mass
  ), na.rm = TRUE)

  data.frame(
    true_ratio = row$true_ratio,
    threshold = row$threshold,
    seed = row$seed,
    ok = TRUE,
    error = NA_character_,
    error_class = NA_character_,
    fitted_ratio = fitted_ratio,
    fitted_minor_direction = fitted_minor_direction,
    excluded_minor = excluded_minor,
    pos_estimate = gv$pos_estimate,
    pos_pvalue = gv$pos_pvalue,
    neg_estimate = gv$neg_estimate,
    neg_pvalue = gv$neg_pvalue,
    contrast_estimate = contrast_estimate,
    true_contrast = true_contrast,
    stringsAsFactors = FALSE
  )
}

threshold_results <- dplyr::bind_rows(
  review_lapply(split(seq_len(nrow(grid)), seq_len(nrow(grid))), function(i) {
    run_one_threshold(grid[i, , drop = FALSE])
  }, workers = if (IS_FULL) N_WORKERS else 1L)
)

if (requireNamespace("readr", quietly = TRUE)) {
  readr::write_csv(threshold_results,
                   file.path(output_dir, "minor_direction_threshold_results.csv"))
} else {
  utils::write.csv(threshold_results,
                   file.path(output_dir, "minor_direction_threshold_results.csv"),
                   row.names = FALSE)
}
```

# Exclusion behavior

```{r exclusion-summary}
failure_summary <- threshold_results %>%
  dplyr::count(ok, error_class, name = "n_runs")

knitr::kable(failure_summary, caption = "Run success/failure counts") %>%
  kableExtra::kable_styling(full_width = FALSE)

exclusion_summary <- threshold_results %>%
  dplyr::filter(ok) %>%
  dplyr::group_by(true_ratio, threshold) %>%
  dplyr::summarise(
    n_runs = dplyr::n(),
    median_fitted_ratio = stats::median(fitted_ratio, na.rm = TRUE),
    exclusion_rate = mean(excluded_minor, na.rm = TRUE),
    minor_estimable_rate = mean(
      dplyr::case_when(
        fitted_minor_direction == "positive" ~ is.finite(pos_estimate),
        fitted_minor_direction == "negative" ~ is.finite(neg_estimate),
        TRUE ~ FALSE
      ),
      na.rm = TRUE
    ),
    .groups = "drop"
  )

knitr::kable(
  exclusion_summary %>%
    dplyr::mutate(
      median_fitted_ratio = round(median_fitted_ratio, 3),
      exclusion_rate = sprintf("%.1f%%", 100 * exclusion_rate),
      minor_estimable_rate = sprintf("%.1f%%", 100 * minor_estimable_rate)
    ),
  caption = "Minor-direction exclusion and estimability by true ratio and threshold"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r exclusion-plot}
plot_excl <- exclusion_summary
if (nrow(plot_excl) > 0L) {
  ggplot(plot_excl, aes(x = true_ratio, y = exclusion_rate,
                        color = factor(threshold), group = threshold)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    labs(x = "True minor/major coefficient-mass ratio",
         y = "Fitted minor direction excluded",
         color = "threshold",
         title = "Threshold rule behavior across controlled minor-direction mass") +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

# Effect-estimate sensitivity

For this one-group Gaussian DGM, the contrast below is the approximate
validation-stage effect for increasing all quantized exposures by one unit,
computed as the sum of each retained direction's validation coefficient times
its fitted coefficient mass. Rows where a direction is excluded omit that
direction by design.

```{r contrast-summary}
contrast_summary <- threshold_results %>%
  dplyr::filter(ok) %>%
  dplyr::mutate(
    bias = contrast_estimate - true_contrast,
    covered_direction = sign(contrast_estimate) == sign(true_contrast)
  ) %>%
  dplyr::group_by(true_ratio, threshold) %>%
  dplyr::summarise(
    n_runs = dplyr::n(),
    true_contrast = mean(true_contrast),
    mean_estimate = mean(contrast_estimate, na.rm = TRUE),
    bias = mean(bias, na.rm = TRUE),
    rmse = sqrt(mean(bias^2, na.rm = TRUE)),
    direction_agreement = mean(covered_direction, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  contrast_summary %>%
    dplyr::mutate(dplyr::across(
      c(true_contrast, mean_estimate, bias, rmse, direction_agreement),
      ~ round(.x, 3)
    )),
  caption = "Approximate all-exposure contrast by threshold"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r contrast-plot}
if (nrow(threshold_results %>% dplyr::filter(ok)) > 0L) {
  ggplot(threshold_results %>% dplyr::filter(ok),
         aes(x = factor(threshold), y = contrast_estimate,
             fill = factor(threshold))) +
    geom_hline(aes(yintercept = true_contrast), linetype = "dashed",
               color = "grey40") +
    geom_boxplot(outlier.shape = NA, alpha = 0.65) +
    geom_point(position = position_jitter(width = 0.08), size = 1.5, alpha = 0.8) +
    facet_wrap(~true_ratio, labeller = label_both) +
    labs(x = "minor_threshold", y = "Approximate contrast estimate",
         title = "Effect-estimate sensitivity to minor-direction threshold") +
    theme_minimal() +
    theme(legend.position = "none")
}
```

# Interpretation target

```{r interpretation-table}
interpretation <- exclusion_summary %>%
  dplyr::filter(threshold == 0.10) %>%
  dplyr::mutate(
    reviewer_use = dplyr::case_when(
      true_ratio <= 0.10 ~ "Default threshold usually removes a very small fitted opposite direction.",
      true_ratio >= 0.15 & true_ratio <= 0.40 ~
        "Minor direction is material enough that reporting sensitivity analyses is advisable.",
      TRUE ~ "Intermediate behavior."
    )
  ) %>%
  dplyr::select(true_ratio, median_fitted_ratio, exclusion_rate,
                minor_estimable_rate, reviewer_use)

knitr::kable(
  interpretation %>%
    dplyr::mutate(
      median_fitted_ratio = round(median_fitted_ratio, 3),
      exclusion_rate = sprintf("%.1f%%", 100 * exclusion_rate),
      minor_estimable_rate = sprintf("%.1f%%", 100 * minor_estimable_rate)
    ),
  caption = "Default threshold = 0.10 interpretation table"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Session information

```{r session-info}
sessionInfo()
```
