---
title: "SGL-WQS asparse sensitivity under high exposure correlation"
subtitle: "r = 0.95 correlation robustness scenario; sglwqs-main analysis version"
author: "SGL-WQS reviewer response"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 150
)

repo_root <- normalizePath(file.path(getwd(), if (dir.exists("analysis")) "." else ".."))
source(file.path(repo_root, "analysis", "_sglwqs_review_helpers.R"))
load_review_packages(c(
  "MASS", "Matrix", "dplyr", "tidyr", "ggplot2", "knitr", "kableExtra", "pkgload"
))
sglwqs_source <- load_review_sglwqs(root = repo_root)

RUN_MODE <- review_run_mode()
IS_FULL <- identical(RUN_MODE, "full")
N_WORKERS <- review_workers(RUN_MODE)
N <- as.integer(Sys.getenv("SGLWQS_ASPARSE_N", if (IS_FULL) 1000 else 180))
N_SEEDS <- as.integer(Sys.getenv("SGLWQS_ASPARSE_SEEDS", if (IS_FULL) 30 else 4))
NFOLDS <- as.integer(Sys.getenv("SGLWQS_NFOLDS", if (IS_FULL) 5 else 3))
NLAMBDA <- as.integer(Sys.getenv("SGLWQS_NLAMBDA", if (IS_FULL) 25 else 8))
ASPARSE_VALUES <- as.numeric(strsplit(Sys.getenv("SGLWQS_ASPARSE_VALUES", "0.05,0.5,0.95"), ",")[[1]])

groups <- review_groups()
exposures <- review_exposures(groups)
true_beta <- attr(simulate_review_mixture(n = 20, seed = 1), "true_beta")
active_vars <- names(true_beta)[abs(true_beta) > 0]
null_vars <- names(true_beta)[abs(true_beta) == 0]
output_dir <- file.path(repo_root, "analysis", "outputs")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
```

# Configuration

```{r configuration}
config <- data.frame(
  item = c("run_mode", "sglwqs_source", "workers", "n", "seeds",
           "correlation", "asparse_values", "nfolds", "nlambda"),
  value = c(RUN_MODE, sglwqs_source$source, N_WORKERS, N, N_SEEDS,
            0.95, paste(ASPARSE_VALUES, collapse = ", "), NFOLDS, NLAMBDA)
)
knitr::kable(config, caption = "Analysis configuration") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

Reviewer comments used the term "alpha" for the sparse-group lasso group-vs-
individual mixing parameter. In the analysis version (`sglwqs-main`), that
parameter is passed through `...` as `asparse` to `sparsegl::cv.sparsegl()`.
It is distinct from the newer development-branch `alpha_en` elastic-net mixing
parameter.

# Simulation grid

```{r grid}
grid <- tidyr::expand_grid(
  asparse = ASPARSE_VALUES,
  seed = review_seeds(N_SEEDS)
) %>%
  dplyr::mutate(row_id = dplyr::row_number())

knitr::kable(head(grid, 12), caption = "First rows of the asparse grid") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Run SGL-WQS fits

```{r run-grid}
run_one_asparse <- function(row) {
  load_review_sglwqs(root = repo_root)
  dat <- simulate_review_mixture(
    n = N,
    seed = row$seed,
    correlation = 0.95,
    outcome = "binomial",
    scenario = "active"
  )
  fit_res <- safe_sglwqs(
    data = dat,
    exposures = exposures,
    groups = groups,
    family = "binomial",
    validation = TRUE,
    bootstrap = FALSE,
    seed = row$seed + 100000L,
    nfolds = NFOLDS,
    nlambda = NLAMBDA,
    minor_threshold = 0.10,
    asparse = row$asparse,
    verbose = FALSE
  )
  if (!isTRUE(fit_res$ok)) {
    return(list(
      summary = data.frame(
        asparse = row$asparse, seed = row$seed, ok = FALSE,
        error = fit_res$error, error_class = classification_from_error(fit_res$error),
        direction_accuracy_active = NA_real_,
        active_weight_concentration = NA_real_,
        null_selected_fraction = NA_real_,
        n_nonzero = NA_real_,
        lambda_at_path_edge = NA
      ),
      weights = data.frame(),
      validation = data.frame()
    ))
  }

  fit <- fit_res$fit
  weights <- sglwqs::extract_weights(fit, direction = "both") %>%
    dplyr::rename(variable = variable, weight = weight, direction = direction) %>%
    dplyr::mutate(asparse = row$asparse, seed = row$seed)

  wide_w <- weights %>%
    dplyr::select(variable, direction, weight) %>%
    tidyr::pivot_wider(names_from = direction, values_from = weight, values_fill = 0)
  if (!"positive" %in% names(wide_w)) wide_w$positive <- 0
  if (!"negative" %in% names(wide_w)) wide_w$negative <- 0
  wide_w <- wide_w %>%
    dplyr::mutate(
      true_beta = true_beta[variable],
      active = abs(true_beta) > 0,
      detected_direction = dplyr::case_when(
        positive > negative ~ "positive",
        negative > positive ~ "negative",
        TRUE ~ "none"
      ),
      true_direction = dplyr::case_when(
        true_beta > 0 ~ "positive",
        true_beta < 0 ~ "negative",
        TRUE ~ "none"
      ),
      max_weight = pmax(positive, negative)
    )

  diag_row <- extract_sglwqs_diagnostics_row(fit)
  val <- extract_validation_df(fit) %>%
    dplyr::mutate(asparse = row$asparse, seed = row$seed)

  summary_row <- data.frame(
    asparse = row$asparse,
    seed = row$seed,
    ok = TRUE,
    error = NA_character_,
    error_class = NA_character_,
    direction_accuracy_active = mean(
      wide_w$detected_direction[wide_w$active] ==
        wide_w$true_direction[wide_w$active],
      na.rm = TRUE
    ),
    active_weight_concentration =
      sum(wide_w$max_weight[wide_w$active], na.rm = TRUE) /
      sum(wide_w$max_weight, na.rm = TRUE),
    null_selected_fraction = mean(wide_w$max_weight[!wide_w$active] > 1e-6, na.rm = TRUE),
    n_nonzero = diag_row$n_nonzero,
    lambda_at_path_edge = diag_row$lambda_at_path_edge,
    stringsAsFactors = FALSE
  )

  list(summary = summary_row, weights = weights, validation = val)
}

results <- review_lapply(split(seq_len(nrow(grid)), seq_len(nrow(grid))), function(i) {
  run_one_asparse(grid[i, , drop = FALSE])
}, workers = if (IS_FULL) N_WORKERS else 1L)

summary_df <- dplyr::bind_rows(lapply(results, `[[`, "summary"))
weights_df <- dplyr::bind_rows(lapply(results, `[[`, "weights"))
validation_df <- dplyr::bind_rows(lapply(results, `[[`, "validation"))

if (requireNamespace("readr", quietly = TRUE)) {
  readr::write_csv(summary_df, file.path(output_dir, "asparse_highcorr_summary.csv"))
  readr::write_csv(weights_df, file.path(output_dir, "asparse_highcorr_weights.csv"))
  readr::write_csv(validation_df, file.path(output_dir, "asparse_highcorr_validation.csv"))
} else {
  utils::write.csv(summary_df, file.path(output_dir, "asparse_highcorr_summary.csv"), row.names = FALSE)
  utils::write.csv(weights_df, file.path(output_dir, "asparse_highcorr_weights.csv"), row.names = FALSE)
  utils::write.csv(validation_df, file.path(output_dir, "asparse_highcorr_validation.csv"), row.names = FALSE)
}
```

# Failure rate

```{r failure-rate}
failure_table <- summary_df %>%
  dplyr::group_by(asparse) %>%
  dplyr::summarise(
    attempted = dplyr::n(),
    succeeded = sum(ok),
    failed = sum(!ok),
    failure_rate = failed / attempted,
    lambda_edge_rate = mean(lambda_at_path_edge, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  failure_table %>%
    dplyr::mutate(
      failure_rate = sprintf("%.1f%%", 100 * failure_rate),
      lambda_edge_rate = sprintf("%.1f%%", 100 * lambda_edge_rate)
    ),
  caption = "SGL-WQS fit failure and selected-lambda edge rates"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Selection and weight concentration

```{r performance-summary}
performance_summary <- summary_df %>%
  dplyr::filter(ok) %>%
  dplyr::group_by(asparse) %>%
  dplyr::summarise(
    direction_accuracy_mean = mean(direction_accuracy_active, na.rm = TRUE),
    direction_accuracy_sd = stats::sd(direction_accuracy_active, na.rm = TRUE),
    active_concentration_mean = mean(active_weight_concentration, na.rm = TRUE),
    active_concentration_sd = stats::sd(active_weight_concentration, na.rm = TRUE),
    null_selected_mean = mean(null_selected_fraction, na.rm = TRUE),
    n_nonzero_median = stats::median(n_nonzero, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  performance_summary %>%
    dplyr::mutate(
      direction_accuracy = sprintf("%.1f%% (%.1f%%)",
                                   100 * direction_accuracy_mean,
                                   100 * direction_accuracy_sd),
      active_concentration = sprintf("%.1f%% (%.1f%%)",
                                     100 * active_concentration_mean,
                                     100 * active_concentration_sd),
      null_selected = sprintf("%.1f%%", 100 * null_selected_mean)
    ) %>%
    dplyr::select(asparse, direction_accuracy, active_concentration,
                  null_selected, n_nonzero_median),
  caption = "Selection performance under r = 0.95"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r performance-plot}
plot_summary <- summary_df %>% dplyr::filter(ok)
if (nrow(plot_summary) > 0L) {
  plot_long <- plot_summary %>%
    dplyr::select(asparse, seed, direction_accuracy_active,
                  active_weight_concentration, null_selected_fraction) %>%
    tidyr::pivot_longer(
      cols = c(direction_accuracy_active, active_weight_concentration,
               null_selected_fraction),
      names_to = "metric",
      values_to = "value"
    )

  ggplot(plot_long, aes(x = factor(asparse), y = value, fill = factor(asparse))) +
    geom_boxplot(outlier.shape = NA, alpha = 0.6) +
    geom_point(position = position_jitter(width = 0.08), size = 1.8, alpha = 0.8) +
    facet_wrap(~metric, scales = "free_y") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(x = "asparse", y = NULL,
         title = "SGL-WQS asparse sensitivity at r = 0.95") +
    theme_minimal() +
    theme(legend.position = "none")
} else {
  cat("No successful asparse fits available for plotting.\n")
}
```

# Null-group p-values

```{r null-pfas}
pfas_val <- validation_df %>%
  dplyr::filter(group == "PFASs")

pfas_summary <- pfas_val %>%
  dplyr::group_by(asparse, direction) %>%
  dplyr::summarise(
    n_estimable = sum(is.finite(p_value)),
    median_p = stats::median(p_value, na.rm = TRUE),
    type1_0_05 = mean(p_value < 0.05, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(
  pfas_summary %>%
    dplyr::mutate(
      median_p = round(median_p, 3),
      type1_0_05 = sprintf("%.1f%%", 100 * type1_0_05)
    ),
  caption = "Null PFAS validation p-values by asparse"
) %>%
  kableExtra::kable_styling(full_width = FALSE)
```

```{r pfas-plot}
if (nrow(pfas_val %>% dplyr::filter(is.finite(p_value))) > 0L) {
  ggplot(pfas_val %>% dplyr::filter(is.finite(p_value)),
         aes(x = factor(asparse), y = p_value, color = direction)) +
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "firebrick") +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitter(width = 0.08), alpha = 0.8) +
    labs(x = "asparse", y = "PFAS validation p-value",
         title = "Null-group p-values under high correlation") +
    theme_minimal() +
    theme(legend.position = "bottom")
} else {
  cat("No finite PFAS validation p-values were available.\n")
}
```

# Session information

```{r session-info}
sessionInfo()
```
