---
title: "Introduction to sglwqs"
subtitle: "Sparse Group Lasso Weighted Quantile Sum Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to sglwqs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  comment = "#>", 
  eval = FALSE,
  fig.width = 10,
  fig.height = 7,
  out.width = "100%",
  dpi = 150
)
```

## Overview

The **sglwqs** package implements Sparse Group Lasso Weighted Quantile Sum (SGL-WQS) regression for analyzing the health effects of chemical mixtures.

### Key Features

| Feature | Traditional WQS | SGL-WQS |
|---------|-----------------|---------|
| Effect direction | One direction per model | Bidirectional in single model |
| Variable selection | All variables included | Automatic selection via penalty |
| Group structure | Not supported | Supports chemical groups |

## Installation

```{r install}
install.packages("sglwqs_0.8.10.tar.gz", repos = NULL, type = "source")
```

## Quick Start (Unified API)

```{r workflow}
library(sglwqs)
library(future)

# 1. Fit model
plan(multisession, workers = 4)

fit <- sglwqs(
  X = exposures,
  y = outcome,
  groups = list(PCBs = pcb_vars, Metals = metal_vars),
  bootstrap = TRUE,
  n_boot = 500,
  validation = TRUE,
  parallel = TRUE,
  seed = 123
)

plan(sequential)

# 2. View results
summary(fit)

# 3. Visualize
plot_weights(fit)
plot_combined_results(fit)

# 4. Export for publication
inference_table(fit)
```

## Core Functions

All functions work identically for both `sglwqs` and `sglwqs_mids` objects:

| Function | Purpose |
|----------|---------|
| `sglwqs()` / `sglwqs_mice()` | Fit model |
| `summary()` | Display model summary |
| `plot_weights()` | Butterfly chart of weights |
| `inference_table()` | Publication-ready table |
| `plot_combined_results()` | Multi-panel figure |
| `extract_weights()` | Get weights as data frame |

## Example with Multiple Chemical Groups

```{r example}
library(sglwqs)
library(groupWQS)
library(future)

data("simdata", package = "groupWQS")

# Define chemical groups
groups <- list(
  PCBs = c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_192"),
  Metals = c("as", "cu", "pb", "sn"),
  Pesticides = c("carbaryl", "propoxur", "methoxychlor", "diazinon", "chlorpyrifos")
)

# Fit model
plan(multisession, workers = 10)

fit <- sglwqs(
  X = simdata[, 1:14],
  y = simdata$Y,
  family = "binomial",
  groups = groups,
  bootstrap = TRUE,
  n_boot = 500,
  parallel = TRUE,
  validation = TRUE,
  seed = 123
)

plan(sequential)

# Results
summary(fit)
inference_table(fit)
```

```{r example-plots, fig.height=8}
plot_weights(fit)
```

```{r example-combined, fig.width=12, fig.height=10}
plot_combined_results(fit, top_n = 5)
```

## Parallel Processing

```{r parallel}
library(future)
plan(multisession, workers = parallel::detectCores() - 1)
# ... fit model with parallel = TRUE ...
plan(sequential)
```

## Troubleshooting

**Slow computation**: Enable parallel processing and reduce `n_boot` for exploration.

**All weights are zero**: Try `lambda = "lambda.min"` or check exposure-outcome associations.

**Memory issues**: Use `keep_boot_matrices = FALSE`.

## References

1. Carrico C, et al. (2014). J Biol Agricul Environ Stat.
2. Simon N, et al. (2013). J Comput Graph Stat.
3. Keil AP, et al. (2020). Environ Health Perspect.
