---
title: "Sample Size Effects on Mixture Methods (30-Seed Replication)"
subtitle: "qgcomp vs gWQS vs groupWQS vs SGL-WQS across different n with Monte Carlo Replication"
author: "Validation Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 150,
  cache = TRUE   
)

# Publication figure output directory
fig_dir <- "figures"
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)

N_BOOT <- 200
N_QUANTILES <- 4
SAMPLE_SIZES <- c(100, 500, 1000, 5000, 10000, 50000)
SEEDS <- c(71, 42, 123, 256, 314, 500, 617, 789, 888, 999,
              1001, 1123, 1234, 1357, 1500, 1618, 1729, 1847, 1963, 2048,
              2222, 2345, 2500, 2718, 2801, 3001, 3141, 3333, 3500, 3777)
N_SEEDS <- length(SEEDS)

# Use all but one core for parallel methods (gWQS, SGL-WQS)
N_WORKERS <- max(parallel::detectCores() - 1L, 1L)
cat(sprintf("Parallel workers: %d / %d cores\n", N_WORKERS, parallel::detectCores()))
```

# Overview

This document examines how sample size affects the performance of mixture analysis methods, replicated across **`r N_SEEDS` independent seeds** per sample size.

**Sample sizes:** `r paste(format(SAMPLE_SIZES, big.mark=","), collapse = ", ")`

**Methods compared:** qgcomp, gWQS (2-index), groupWQS, SGL-WQS

**True Data Structure:**

| Group | Variables | True Effects |
|-------|-----------|--------------|
| PCBs | pcb_118, pcb_138, pcb_153, pcb_180, pcb_187 | All positive (+0.04 to +0.20) |
| Metals | cd, pb, hg, se, mg | Mixed (cd/pb negative, hg/se positive, mg ~0) |
| PFASs | PFOA, PFNA, PFOS | No effect (null) |

---

# Setup

```{r load-packages, cache=FALSE}
library(MASS)
library(qgcomp)
library(gWQS)
library(groupWQS)
library(sglwqs)
library(future)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(tictoc)
library(tidyverse)
```

```{r data-generation-function}
generate_sglwqs_simdata <- function(n = 100000, seed = 71) {
  set.seed(seed)
  
  sex <- rbinom(n, 1, 0.5)
  age <- pmax(pmin(round(rnorm(n, 50, 12)), 80), 20)
  bmi <- pmax(pmin(round(22 + 0.05*age + 1.5*sex + rnorm(n, 0, 4), 1), 45), 15)
  
  cor_pcb <- matrix(c(1.00, 0.60, 0.70, 0.65, 0.60,
                      0.60, 1.00, 0.75, 0.70, 0.65,
                      0.70, 0.75, 1.00, 0.80, 0.70,
                      0.65, 0.70, 0.80, 1.00, 0.75,
                      0.60, 0.65, 0.70, 0.75, 1.00), 5, 5)
  
  pcb <- MASS::mvrnorm(n, c(3.5, 3.5, 4.0, 4.5, 3.0), 
                       diag(c(1.5, 1.5, 1.8, 2.0, 1.5)) %*% cor_pcb %*% diag(c(1.5, 1.5, 1.8, 2.0, 1.5)))
  colnames(pcb) <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
  
  cor_metal <- matrix(c(
    1.00, 0.60, 0.15, 0.10, 0.20,
    0.60, 1.00, 0.10, 0.15, 0.25,
    0.15, 0.10, 1.00, 0.55, 0.20,
    0.10, 0.15, 0.55, 1.00, 0.30,
    0.20, 0.25, 0.20, 0.30, 1.00
  ), 5, 5, byrow = TRUE)
  
  metal_raw <- MASS::mvrnorm(n, log(c(0.5, 2, 1, 100, 20)), 
                             diag(c(0.6, 0.8, 0.5, 0.3, 0.25)) %*% cor_metal %*% 
                               diag(c(0.6, 0.8, 0.5, 0.3, 0.25)))
  metal <- exp(metal_raw)
  colnames(metal) <- c("cd", "pb", "hg", "se", "mg")
  
  pfas <- pmax(MASS::mvrnorm(n, c(3, 1.5, 5), diag(c(2, 1, 3.5))), 0.1)
  colnames(pfas) <- c("PFOA", "PFNA", "PFOS")
  
  beta_pcb <- c(0.04, 0.15, 0.20, 0.08, 0.05)
  beta_metal <- c(-0.12, -0.18, +0.10, +0.14, -0.02)
  beta_pfas <- c(0, 0, 0)
  
  eta <- -3.0 + 
    scale(pcb) %*% beta_pcb + 
    scale(metal) %*% beta_metal +
    scale(pfas) %*% beta_pfas + 
    sex * 0.3 + (age - 50) / 10 * 0.02 + (bmi - 25) / 5 * 0.05
  
  Y <- rbinom(n, 1, 1 / (1 + exp(-eta)))
  
  result <- data.frame(pcb, metal, pfas, sex = sex, age = age, bmi = bmi, Y = Y)
  attr(result, "true_beta") <- list(
    pcb = setNames(beta_pcb, colnames(pcb)),
    metal = setNames(beta_metal, colnames(metal)),
    pfas = setNames(beta_pfas, colnames(pfas))
  )
  return(result)
}

# Variable definitions
PCBs <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
Metals <- c("cd", "pb", "hg", "se", "mg")
PFASs <- c("PFOA", "PFNA", "PFOS")
all_exposures <- c(PCBs, Metals, PFASs)
groups <- list(PCBs = PCBs, Metals = Metals, PFASs = PFASs)

true_directions <- data.frame(
  Variable = all_exposures,
  True_Beta = c(0.04, 0.15, 0.20, 0.08, 0.05, -0.12, -0.18, 0.10, 0.14, -0.02, 0, 0, 0),
  Group = c(rep("PCBs", 5), rep("Metals", 5), rep("PFASs", 3))
) %>%
  mutate(True_Direction = case_when(
    True_Beta > 0.01 ~ "Positive",
    True_Beta < -0.01 ~ "Negative",
    TRUE ~ "None"
  ))
```

### True Coefficients

```{r true-coef-table}
kable(true_directions, digits = 3, caption = "True Coefficients") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(which(true_directions$True_Direction == "Positive"), background = "#E3F2FD") %>%
  row_spec(which(true_directions$True_Direction == "Negative"), background = "#FFEBEE")
```

---

# Analysis Function

```{r analysis-function}
run_one_scenario <- function(n, seed) {
  simdata <- generate_sglwqs_simdata(n = n, seed = seed)
  
  result <- list(n = n, seed = seed)
  
  # --- qgcomp (deterministic, no parallel) ---
  qgcomp_formula <- as.formula(
    paste("Y ~", paste(all_exposures, collapse = " + "), "+ sex + age + bmi")
  )
  
  tryCatch({
    qc <- qgcomp.glm.noboot(qgcomp_formula, expnms = all_exposures,
                              data = simdata, family = binomial(), q = N_QUANTILES)
    
    result$qgcomp_weights <- data.frame(
      Variable = c(names(qc$pos.weights), names(qc$neg.weights)),
      Weight = c(qc$pos.weights, qc$neg.weights),
      Direction = c(rep("Positive", length(qc$pos.weights)),
                    rep("Negative", length(qc$neg.weights))),
      Method = "qgcomp", n = n, Seed = seed
    )
    result$qgcomp_psi <- qc$psi
    result$qgcomp_pos <- qc$pos.psi
    result$qgcomp_neg <- qc$neg.psi
    
    # Direction detection
    qc_dirs <- data.frame(Variable = all_exposures)
    qc_dirs$Detected <- ifelse(qc_dirs$Variable %in% names(qc$pos.weights), "Positive", "Negative")
    qc_dirs <- qc_dirs %>% left_join(true_directions %>% dplyr::select(Variable, True_Direction), by = "Variable")
    result$qgcomp_correct <- sum(qc_dirs$Detected == qc_dirs$True_Direction | 
                                   qc_dirs$True_Direction == "None")
    result$qgcomp_total <- nrow(qc_dirs %>% filter(True_Direction != "None"))
    result$qgcomp_accuracy <- result$qgcomp_correct / nrow(qc_dirs)
  }, error = function(e) {
    cat("    qgcomp failed:", e$message, "\n")
    result$qgcomp_error <<- e$message
  })
  
  # --- gWQS (2-index model, parallel) ---
  tryCatch({
    gwqs_formula <- as.formula(
      paste("Y ~ pwqs + nwqs + sex + age + bmi")
    )
    
    gwqs_fit <- withCallingHandlers(
      gwqs(gwqs_formula, mix_name = all_exposures, data = simdata,
           q = N_QUANTILES, validation = 0.4, b = N_BOOT,
           b1_pos = TRUE, rh = 1, family = "binomial", seed = seed,
           plan_strategy = "multisession"),
      warning = function(w) {
        if (grepl("Using formula\\(x\\) is deprecated|formula\\.character", conditionMessage(w)))
          invokeRestart("muffleWarning")
      }
    )
    
    fw <- gwqs_fit$final_weights
    gwqs_w <- bind_rows(
      data.frame(Variable = fw$mix_name,
                 Weight = fw$mean_weight_p,
                 Direction = "Positive", Method = "gWQS", n = n, Seed = seed),
      data.frame(Variable = fw$mix_name,
                 Weight = fw$mean_weight_n,
                 Direction = "Negative", Method = "gWQS", n = n, Seed = seed)
    )
    result$gwqs_weights <- gwqs_w
    
    gwqs_coef <- coef(gwqs_fit$fit)
    result$gwqs_pos <- gwqs_coef["pwqs"]
    result$gwqs_neg <- gwqs_coef["nwqs"]
    
    # Direction detection for gWQS (higher weight in pos vs neg index)
    gwqs_dirs <- data.frame(Variable = fw$mix_name)
    gwqs_dirs$Detected <- ifelse(fw$mean_weight_p >= fw$mean_weight_n, "Positive", "Negative")
    gwqs_dirs <- gwqs_dirs %>%
      left_join(true_directions %>% dplyr::select(Variable, True_Direction), by = "Variable")
    result$gwqs_correct <- sum(gwqs_dirs$Detected == gwqs_dirs$True_Direction |
                                 gwqs_dirs$True_Direction == "None")
    result$gwqs_accuracy <- result$gwqs_correct / nrow(gwqs_dirs)
  }, error = function(e) {
    cat("    gWQS failed:", e$message, "\n")
    result$gwqs_error <<- e$message
  })
  
  # --- groupWQS ---
  tryCatch({
    group_list <- list(PCBs, Metals, PFASs)
    X_gw <- make.X(simdata, num.groups = 3, groups = group_list)
    x.s <- make.x.s(simdata, num.groups = 3, groups = group_list)
    
    n_total <- nrow(simdata)
    n_train <- round(n_total * 0.6)
    set.seed(seed)
    train_idx <- sample(seq_len(n_total), size = n_train)
    valid_idx <- setdiff(seq_len(n_total), train_idx)
    
    gw_fit <- gwqs.fit(
      y = simdata$Y[valid_idx], y.train = simdata$Y[train_idx],
      x = X_gw[valid_idx, ], x.train = X_gw[train_idx, ],
      x.s = x.s, B = N_BOOT, n.quantiles = N_QUANTILES, func = "binary"
    )
    
    grp_w <- data.frame()
    for (i in seq_along(gw_fit$weights)) {
      grp_w <- rbind(grp_w, data.frame(
        Variable = names(gw_fit$weights[[i]]),
        Weight = as.numeric(gw_fit$weights[[i]]),
        Direction = "Combined",
        Method = "groupWQS", n = n, Seed = seed
      ))
    }
    result$groupwqs_weights <- grp_w
    result$groupwqs_coefs <- coef(gw_fit$fit)[grep("^GWQS", names(coef(gw_fit$fit)))]
  }, error = function(e) {
    cat("    groupWQS failed:", e$message, "\n")
    result$groupwqs_error <<- e$message
  })
  
  # --- SGL-WQS (parallel) ---
  tryCatch({
    plan(multisession, workers = N_WORKERS)
    
    sglwqs_fit <- sglwqs(
      X = simdata[, all_exposures], y = simdata$Y,
      covariates = simdata[, c("sex", "age", "bmi")],
      groups = groups, family = "binomial",
      n_quantiles = N_QUANTILES, bootstrap = TRUE,
      n_boot = N_BOOT, parallel = TRUE,
      validation = TRUE, train_prop = 0.6, seed = seed
    )
    plan(sequential)
    
    sw <- extract_weights(sglwqs_fit, direction = "both") %>%
      dplyr::select(Variable = variable, Weight = weight, Direction = direction) %>%
      mutate(Direction = tools::toTitleCase(Direction), Method = "SGL-WQS", n = n, Seed = seed)
    result$sglwqs_weights <- sw
    result$sglwqs_pos <- sglwqs_fit$pos_index_sum
    result$sglwqs_neg <- sglwqs_fit$neg_index_sum
    
    # Group-level index sums
    result$sglwqs_pos_by_group <- sglwqs_fit$pos_index_sum_by_group
    result$sglwqs_neg_by_group <- sglwqs_fit$neg_index_sum_by_group

    # Validation-stage group × direction inference
    if (!is.null(sglwqs_fit$validation_info) &&
        !is.null(sglwqs_fit$validation_info$group_results)) {
      result$sglwqs_group_val <- sglwqs_fit$validation_info$group_results
    }

    # Selection frequency from bootstrap
    if (!is.null(sglwqs_fit$boot_info)) {
      result$sglwqs_sel_freq_pos <- sglwqs_fit$boot_info$selection_freq_pos
      result$sglwqs_sel_freq_neg <- sglwqs_fit$boot_info$selection_freq_neg
    }
    
    # Direction detection for SGL-WQS
    sgl_dirs <- data.frame(Variable = all_exposures)
    pos_w <- sglwqs_fit$pos_weights
    neg_w <- sglwqs_fit$neg_weights
    sgl_dirs$Detected <- ifelse(pos_w[sgl_dirs$Variable] > neg_w[sgl_dirs$Variable], 
                                 "Positive", "Negative")
    sgl_dirs <- sgl_dirs %>% left_join(true_directions %>% dplyr::select(Variable, True_Direction), 
                                        by = "Variable")
    result$sglwqs_correct <- sum(sgl_dirs$Detected == sgl_dirs$True_Direction | 
                                   sgl_dirs$True_Direction == "None")
    result$sglwqs_accuracy <- result$sglwqs_correct / nrow(sgl_dirs)
  }, error = function(e) {
    cat("    SGL-WQS failed:", e$message, "\n")
    plan(sequential)
    result$sglwqs_error <<- e$message
  })
  
  return(result)
}
```

---

# Run Analysis

```{r run-analysis, cache=TRUE}
tic("Total analysis time")

all_results <- list()
idx <- 1

for (n in SAMPLE_SIZES) {
  for (s in seq_along(SEEDS)) {
    seed <- SEEDS[s]
    cat(sprintf("n=%s, seed=%d (%d/%d)...\n", format(n, big.mark=","), seed, s, N_SEEDS))
    
    tryCatch({
      all_results[[idx]] <- run_one_scenario(n, seed)
      idx <- idx + 1
    }, error = function(e) {
      cat("  FAILED:", e$message, "\n")
    })
  }
}

toc()
```

---

---


# Results

## Direction Detection Accuracy (Mean ± SD)

```{r direction-accuracy, cache=FALSE}
accuracy_df <- data.frame()

for (res in all_results) {
  if (!is.null(res$qgcomp_accuracy)) {
    accuracy_df <- rbind(accuracy_df, data.frame(
      n = res$n, Seed = res$seed, Method = "qgcomp", Accuracy = res$qgcomp_accuracy))
  }
  if (!is.null(res$gwqs_accuracy)) {
    accuracy_df <- rbind(accuracy_df, data.frame(
      n = res$n, Seed = res$seed, Method = "gWQS", Accuracy = res$gwqs_accuracy))
  }
  if (!is.null(res$groupwqs_coefs)) {
    gwqs_coefs <- res$groupwqs_coefs
    if (length(gwqs_coefs) >= 3) {
      grp_dirs <- c(
        setNames(rep(ifelse(gwqs_coefs[1] >= 0, "Positive", "Negative"), length(PCBs)), PCBs),
        setNames(rep(ifelse(gwqs_coefs[2] >= 0, "Positive", "Negative"), length(Metals)), Metals),
        setNames(rep(ifelse(gwqs_coefs[3] >= 0, "Positive", "Negative"), length(PFASs)), PFASs))
      grp_check <- data.frame(Variable = names(grp_dirs), Detected = grp_dirs) %>%
        left_join(true_directions %>% dplyr::select(Variable, True_Direction), by = "Variable")
      grp_acc <- sum(grp_check$Detected == grp_check$True_Direction |
                       grp_check$True_Direction == "None") / nrow(grp_check)
      accuracy_df <- rbind(accuracy_df, data.frame(
        n = res$n, Seed = res$seed, Method = "groupWQS", Accuracy = grp_acc))
    }
  }
  if (!is.null(res$sglwqs_accuracy)) {
    accuracy_df <- rbind(accuracy_df, data.frame(
      n = res$n, Seed = res$seed, Method = "SGL-WQS", Accuracy = res$sglwqs_accuracy))
  }
}

# gWQS success/failure
gwqs_attempted <- sum(sapply(all_results, function(r) !is.null(r$n)))
gwqs_succeeded <- sum(sapply(all_results, function(r) !is.null(r$gwqs_accuracy)))
gwqs_failed    <- sum(sapply(all_results, function(r) !is.null(r$gwqs_error)))
cat(sprintf("gWQS: %d/%d succeeded, %d failed\n", gwqs_succeeded, gwqs_attempted, gwqs_failed))

if (gwqs_failed > 0) {
  fail_df <- data.frame()
  for (res in all_results) {
    if (!is.null(res$gwqs_error))
      fail_df <- rbind(fail_df, data.frame(n = res$n, Seed = res$seed, Error = res$gwqs_error))
  }
  cat("\ngWQS failures by sample size:\n")
  print(table(fail_df$n))
}

method_order <- c("SGL-WQS", "gWQS", "groupWQS", "qgcomp")
# Match the method-color mapping used by main Figure 3
# (scale_fill_brewer(palette = "Set1") in the correlation robustness Rmd).
fig3_method_palette <- c(
  "SGL-WQS" = "#984EA3",
  "gWQS" = "#377EB8",
  "groupWQS" = "#E41A1C",
  "qgcomp" = "#4DAF4A"
)
accuracy_df <- accuracy_df %>%
  mutate(Method = factor(Method, levels = method_order))

accuracy_summary <- accuracy_df %>%
  group_by(n, Method) %>%
  summarize(Mean = mean(Accuracy, na.rm = TRUE),
            SD = sd(Accuracy, na.rm = TRUE), .groups = "drop") %>%
  mutate(`Mean (SD)` = sprintf("%.1f%% (%.1f%%)", Mean * 100, SD * 100)) %>%
  arrange(n, Method)

kable(accuracy_summary %>%
        dplyr::select(n, Method, `Mean (SD)`) %>%
        pivot_wider(names_from = Method, values_from = `Mean (SD)`),
      caption = paste0("Direction Detection Accuracy: Mean (SD) Across ", N_SEEDS, " Seeds")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

*Note: groupWQS assigns a single direction per group based on group coefficient signs. In this simulation, the metals group contains both positive (Hg, Se) and negative (Cd, Pb) effects, so groupWQS's theoretical maximum accuracy is approximately 85% (misclassifying 2/13 variables regardless of coefficient sign). This structural ceiling explains the plateau at ~81%.*

```{r accuracy-plot, fig.height=6, cache=FALSE}
p <- ggplot(accuracy_summary, aes(x = n, y = Mean, color = Method)) +
  geom_line(linewidth = 1.2) + geom_point(size = 3) +
  geom_errorbar(aes(ymin = pmax(Mean - SD, 0), ymax = pmin(Mean + SD, 1)),
                width = 0.05, linewidth = 0.8) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  scale_x_log10(breaks = SAMPLE_SIZES, labels = scales::comma) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  scale_color_manual(values = fig3_method_palette, breaks = method_order, drop = FALSE) +
  labs(title = paste0("Direction Detection Accuracy vs Sample Size (Mean ± SD, ", N_SEEDS, " seeds)"),
       x = "Sample Size (log scale)", y = "Accuracy") +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1))
print(p)

ggsave(file.path(fig_dir, "Fig_size_accuracy_ribbon.pdf"), p,
       width = 180, height = 100, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_accuracy_ribbon.tiff"), p,
       width = 180, height = 100, units = "mm", dpi = 300, compression = "lzw")
```

```{r accuracy-violin, fig.height=6, fig.width=12, cache=FALSE}
p <- ggplot(accuracy_df, aes(x = factor(n), y = Accuracy, fill = Method)) +
  geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
  geom_point(size = 1.5, alpha = 0.6,
             position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.8)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  scale_fill_manual(values = fig3_method_palette, breaks = method_order, drop = FALSE) +
  labs(title = paste0("Direction Detection Accuracy by Sample Size (", N_SEEDS, " seeds)"),
       x = "Sample Size", y = "Accuracy") +
  theme_minimal() + theme(legend.position = "bottom")
print(p)

ggsave(file.path(fig_dir, "Fig_size_accuracy_violin.pdf"), p,
       width = 180, height = 120, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_accuracy_violin.tiff"), p,
       width = 180, height = 120, units = "mm", dpi = 300, compression = "lzw")
```

## Weight Estimates Across Sample Sizes

```{r extract-weights, cache=FALSE}
all_wt <- data.frame()
for (res in all_results) {
  if (!is.null(res$qgcomp_weights))   all_wt <- rbind(all_wt, res$qgcomp_weights)
  if (!is.null(res$gwqs_weights))     all_wt <- rbind(all_wt, res$gwqs_weights)
  if (!is.null(res$groupwqs_weights)) all_wt <- rbind(all_wt, res$groupwqs_weights)
  if (!is.null(res$sglwqs_weights))   all_wt <- rbind(all_wt, res$sglwqs_weights)
}

all_wt <- all_wt %>%
  left_join(true_directions %>% dplyr::select(Variable, True_Beta, Group, True_Direction),
            by = "Variable")

# Active components (|beta| >= 0.10) for weight concentration metrics
active_vars <- c("pcb_138", "pcb_153", "cd", "pb", "hg", "se")
null_vars   <- setdiff(all_exposures, active_vars)
chance_level <- length(active_vars) / length(all_exposures)

# Max weight per variable across directions (comparable across all methods)
wt_max <- all_wt %>%
  group_by(Method, n, Seed, Variable) %>%
  summarize(MaxWeight = max(Weight, na.rm = TRUE), .groups = "drop")
```

## Weight Concentration on Active Components

```{r weight-concentration, fig.height=7, fig.width=14, cache=FALSE}
wt_conc <- wt_max %>%
  mutate(IsActive = Variable %in% active_vars) %>%
  group_by(Method, n, Seed, IsActive) %>%
  summarize(TotalWeight = sum(MaxWeight, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = IsActive, values_from = TotalWeight,
              names_prefix = "Active_") %>%
  mutate(Concentration = Active_TRUE / (Active_TRUE + Active_FALSE))

wt_conc_summary <- wt_conc %>%
  group_by(n, Method) %>%
  summarize(Mean = mean(Concentration, na.rm = TRUE),
            SD = sd(Concentration, na.rm = TRUE), .groups = "drop")

p <- ggplot(wt_conc, aes(x = factor(n), y = Concentration, fill = Method)) +
  geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
  geom_point(size = 1, alpha = 0.6,
             position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
  geom_hline(yintercept = chance_level, linetype = "dashed", color = "red") +
  annotate("text", x = 0.6, y = chance_level + 0.02,
           label = sprintf("Chance = %.0f%%", chance_level * 100),
           color = "red", size = 3, hjust = 0) +
  scale_fill_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = paste0("Weight Concentration on Active Components (", N_SEEDS, " seeds)"),
       subtitle = paste0(length(active_vars), " active (|β|≥0.10) / ",
                         length(all_exposures), " total"),
       x = "Sample Size", y = "Proportion of Total Weight on Active Components") +
  theme_minimal() + theme(legend.position = "bottom")
print(p)

ggsave(file.path(fig_dir, "Fig_size_weight_concentration.pdf"), p,
       width = 180, height = 120, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_weight_concentration.tiff"), p,
       width = 180, height = 120, units = "mm", dpi = 300, compression = "lzw")

kable(wt_conc_summary %>%
        mutate(`Mean (SD)` = sprintf("%.1f%% (%.1f%%)", Mean*100, SD*100)) %>%
        dplyr::select(n, Method, `Mean (SD)`) %>%
        pivot_wider(names_from = Method, values_from = `Mean (SD)`),
      caption = sprintf("Weight Concentration (chance = %.1f%%)", chance_level*100)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Active-to-Null Mean Weight Ratio

```{r weight-ratio, fig.height=7, fig.width=14, cache=FALSE}
wt_ratio <- wt_max %>%
  mutate(IsActive = Variable %in% active_vars) %>%
  group_by(Method, n, Seed, IsActive) %>%
  summarize(MeanWeight = mean(MaxWeight, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = IsActive, values_from = MeanWeight,
              names_prefix = "Active_") %>%
  mutate(Ratio = ifelse(Active_FALSE > 0, Active_TRUE / Active_FALSE, NA))

wt_ratio_summary <- wt_ratio %>%
  group_by(n, Method) %>%
  summarize(Mean = mean(Ratio, na.rm = TRUE),
            SD = sd(Ratio, na.rm = TRUE), .groups = "drop")

p <- ggplot(wt_ratio, aes(x = factor(n), y = Ratio, fill = Method)) +
  geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
  geom_point(size = 1, alpha = 0.6,
             position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
  geom_hline(yintercept = 1.0, linetype = "dashed", color = "red") +
  scale_fill_brewer(palette = "Set1") +
  labs(title = paste0("Active-to-Null Mean Weight Ratio (", N_SEEDS, " seeds)"),
       subtitle = "Higher = better. Red = no discrimination (1.0)",
       x = "Sample Size", y = "Mean Weight (Active) / Mean Weight (Null)") +
  theme_minimal() + theme(legend.position = "bottom")
print(p)

ggsave(file.path(fig_dir, "Fig_size_weight_ratio.pdf"), p,
       width = 180, height = 120, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_weight_ratio.tiff"), p,
       width = 180, height = 120, units = "mm", dpi = 300, compression = "lzw")

kable(wt_ratio_summary %>%
        mutate(`Mean (SD)` = sprintf("%.2f (%.2f)", Mean, SD)) %>%
        dplyr::select(n, Method, `Mean (SD)`) %>%
        pivot_wider(names_from = Method, values_from = `Mean (SD)`),
      caption = "Active-to-Null Weight Ratio (1.0 = no discrimination)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Weight Rank of Active Components

```{r weight-rank, fig.height=7, fig.width=14, cache=FALSE}
rank_df <- wt_max %>%
  group_by(Method, n, Seed) %>%
  mutate(Rank = rank(-MaxWeight, ties.method = "average"),
         NormRank = Rank / n()) %>%
  ungroup() %>%
  filter(Variable %in% active_vars)

rank_overall <- rank_df %>%
  group_by(n, Method, Seed) %>%
  summarize(MeanNormRank = mean(NormRank, na.rm = TRUE), .groups = "drop")

p <- ggplot(rank_overall, aes(x = factor(n), y = MeanNormRank, fill = Method)) +
  geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
  geom_point(size = 1, alpha = 0.6,
             position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  scale_fill_brewer(palette = "Set1") +
  scale_y_reverse(labels = scales::percent) +
  labs(title = paste0("Normalized Rank of Active Components (", N_SEEDS, " seeds)"),
       subtitle = "Lower (top) = active components ranked higher. 50% = random",
       x = "Sample Size", y = "Mean Normalized Rank (lower = better)") +
  theme_minimal() + theme(legend.position = "bottom")
print(p)

ggsave(file.path(fig_dir, "Fig_size_weight_rank.pdf"), p,
       width = 180, height = 120, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_weight_rank.tiff"), p,
       width = 180, height = 120, units = "mm", dpi = 300, compression = "lzw")
```

## Weight Distributions by Sample Size

### SGL-WQS Weights by Sample Size

```{r sglwqs-weights-violin, fig.height=10, fig.width=14, cache=FALSE}
sgl_wt <- all_wt %>% filter(Method == "SGL-WQS")

if (nrow(sgl_wt) > 0) {
  p <- ggplot(sgl_wt, aes(x = factor(n), y = Weight, fill = Direction)) +
    geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
    geom_point(size = 1, alpha = 0.6,
               position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
    facet_wrap(~Variable, scales = "free_y", ncol = 4) +
    scale_fill_manual(values = c("Positive" = "#0072B2", "Negative" = "#E69F00")) +
    labs(title = paste0("SGL-WQS: Weight Estimates by Sample Size (", N_SEEDS, " seeds)"),
         subtitle = "Violin + dots show distribution across seeds",
         x = "Sample Size", y = "Weight") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom", strip.text = element_text(size = 8))
  print(p)

  ggsave(file.path(fig_dir, "Fig_size_sglwqs_weights.pdf"), p,
         width = 180, height = 200, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, "Fig_size_sglwqs_weights.tiff"), p,
         width = 180, height = 200, units = "mm", dpi = 300, compression = "lzw")
}
```

### gWQS Weights by Sample Size

```{r gwqs-weights-violin, fig.height=10, fig.width=14, cache=FALSE}
gwqs_wt <- all_wt %>% filter(Method == "gWQS")

if (nrow(gwqs_wt) > 0) {
  p <- ggplot(gwqs_wt, aes(x = factor(n), y = Weight, fill = Direction)) +
    geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
    geom_point(size = 1, alpha = 0.6,
               position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
    facet_wrap(~Variable, scales = "free_y", ncol = 4) +
    scale_fill_manual(values = c("Positive" = "#0072B2", "Negative" = "#E69F00")) +
    labs(title = paste0("gWQS: Weight Estimates by Sample Size (", N_SEEDS, " seeds)"),
         x = "Sample Size", y = "Weight") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom", strip.text = element_text(size = 8))
  print(p)

  ggsave(file.path(fig_dir, "Fig_size_gwqs_weights.pdf"), p,
         width = 180, height = 200, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, "Fig_size_gwqs_weights.tiff"), p,
         width = 180, height = 200, units = "mm", dpi = 300, compression = "lzw")
} else {
  cat("gWQS produced no successful weight results.\n")
}
```

### groupWQS Weights by Sample Size

```{r groupwqs-weights-violin, fig.height=10, fig.width=14, cache=FALSE}
grpwqs_wt <- all_wt %>% filter(Method == "groupWQS")

if (nrow(grpwqs_wt) > 0) {
  p <- ggplot(grpwqs_wt, aes(x = factor(n), y = Weight, fill = Direction)) +
    geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
    geom_point(size = 1, alpha = 0.6,
               position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
    facet_wrap(~Variable, scales = "free_y", ncol = 4) +
    scale_fill_manual(values = c("Combined" = "#56B4E9", "Positive" = "#0072B2", "Negative" = "#E69F00")) +
    labs(title = paste0("groupWQS: Weight Estimates by Sample Size (", N_SEEDS, " seeds)"),
         x = "Sample Size", y = "Weight") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom", strip.text = element_text(size = 8))
  print(p)

  ggsave(file.path(fig_dir, "Fig_size_groupwqs_weights.pdf"), p,
         width = 180, height = 200, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, "Fig_size_groupwqs_weights.tiff"), p,
         width = 180, height = 200, units = "mm", dpi = 300, compression = "lzw")
}
```

### qgcomp Weights by Sample Size

```{r qgcomp-weights-violin, fig.height=10, fig.width=14, cache=FALSE}
qc_wt <- all_wt %>% filter(Method == "qgcomp")

if (nrow(qc_wt) > 0) {
  p <- ggplot(qc_wt %>% filter(!is.na(Weight)),
         aes(x = factor(n), y = Weight, fill = Direction)) +
    geom_violin(alpha = 0.25, position = position_dodge(width = 0.8), trim = FALSE) +
    geom_point(size = 1, alpha = 0.6,
               position = position_jitterdodge(jitter.width = 0.06, dodge.width = 0.8)) +
    facet_wrap(~Variable, scales = "free_y", ncol = 4) +
    scale_fill_manual(values = c("Positive" = "#0072B2", "Negative" = "#E69F00")) +
    labs(title = paste0("qgcomp: Weight Estimates by Sample Size (", N_SEEDS, " seeds)"),
         x = "Sample Size", y = "Weight") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom", strip.text = element_text(size = 8))
  print(p)

  ggsave(file.path(fig_dir, "Fig_size_qgcomp_weights.pdf"), p,
         width = 180, height = 200, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, "Fig_size_qgcomp_weights.tiff"), p,
         width = 180, height = 200, units = "mm", dpi = 300, compression = "lzw")
}
```

## Mixture Effect Estimates

```{r mixture-effects, cache=FALSE}
effects_df <- data.frame()

for (res in all_results) {
  if (!is.null(res$qgcomp_psi)) {
    effects_df <- rbind(effects_df, data.frame(
      n = res$n, Seed = res$seed, Method = "qgcomp",
      Effect_Type = c("Overall", "Positive", "Negative"),
      Estimate = c(res$qgcomp_psi, res$qgcomp_pos, res$qgcomp_neg)))
  }
  if (!is.null(res$gwqs_pos)) {
    effects_df <- rbind(effects_df, data.frame(
      n = res$n, Seed = res$seed, Method = "gWQS",
      Effect_Type = c("Positive Index", "Negative Index"),
      Estimate = c(res$gwqs_pos, res$gwqs_neg)))
  }
  if (!is.null(res$sglwqs_pos)) {
    effects_df <- rbind(effects_df, data.frame(
      n = res$n, Seed = res$seed, Method = "SGL-WQS",
      Effect_Type = c("Positive Index", "Negative Index"),
      Estimate = c(res$sglwqs_pos, -res$sglwqs_neg)))
  }
  if (!is.null(res$groupwqs_coefs)) {
    gc <- res$groupwqs_coefs
    if (length(gc) >= 3) {
      effects_df <- rbind(effects_df, data.frame(
        n = res$n, Seed = res$seed, Method = "groupWQS",
        Effect_Type = c("PCBs Index", "Metals Index", "PFASs Index"),
        Estimate = as.numeric(gc[1:3])))
    }
  }
}

effects_summary <- effects_df %>%
  group_by(n, Method, Effect_Type) %>%
  summarize(Mean = mean(Estimate, na.rm = TRUE),
            SD = sd(Estimate, na.rm = TRUE), .groups = "drop") %>%
  mutate(`Mean (SD)` = sprintf("%.3f (%.3f)", Mean, SD))

kable(effects_summary %>%
        dplyr::select(n, Method, Effect_Type, `Mean (SD)`) %>%
        pivot_wider(names_from = n, values_from = `Mean (SD)`),
      caption = paste0("Mixture Effect Estimates: Mean (SD) Across ", N_SEEDS, " Seeds")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r effects-ribbon, fig.height=8, fig.width=12, cache=FALSE}
p <- ggplot(effects_summary, aes(x = n, y = Mean, color = Effect_Type)) +
  geom_line(linewidth = 1) + geom_point(size = 2) +
  geom_ribbon(aes(ymin = Mean - SD, ymax = Mean + SD, fill = Effect_Type),
              alpha = 0.15, color = NA) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  facet_wrap(~Method, scales = "free_y", ncol = 2) +
  scale_x_log10(breaks = SAMPLE_SIZES, labels = scales::comma) +
  scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
  labs(title = paste0("Mixture Effect Estimates vs Sample Size (Mean ± SD, ", N_SEEDS, " seeds)"),
       x = "Sample Size (log scale)", y = "Effect Estimate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
print(p)

ggsave(file.path(fig_dir, "Fig_size_effects_ribbon.pdf"), p,
       width = 180, height = 140, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_size_effects_ribbon.tiff"), p,
       width = 180, height = 140, units = "mm", dpi = 300, compression = "lzw")
```

---

# Error Summary

```{r error-summary, cache=FALSE}
error_df <- data.frame()
for (res in all_results) {
  for (method in c("qgcomp", "gwqs", "groupwqs", "sglwqs")) {
    err_key <- paste0(method, "_error")
    if (!is.null(res[[err_key]])) {
      error_df <- rbind(error_df, data.frame(
        n = res$n, Seed = res$seed,
        Method = switch(method, qgcomp = "qgcomp", gwqs = "gWQS",
                        groupwqs = "groupWQS", sglwqs = "SGL-WQS"),
        Error = res[[err_key]]))
    }
  }
}

if (nrow(error_df) > 0) {
  cat(sprintf("Total errors: %d\n\n", nrow(error_df)))
  kable(error_df %>% group_by(Method, n) %>%
          summarize(Failures = n(), .groups = "drop") %>%
          pivot_wider(names_from = n, values_from = Failures, values_fill = 0),
        caption = "Number of Failures by Method and Sample Size") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
} else {
  cat("All methods completed successfully for all scenarios.\n")
}
```

---

# Consolidated Summary

```{r summary-table, cache=FALSE}
summary_items <- data.frame()

if (nrow(accuracy_summary) > 0) {
  summary_items <- rbind(summary_items,
    accuracy_summary %>% dplyr::select(n, Method, `Mean (SD)`) %>%
      mutate(Metric = "Direction Accuracy"))
}
if (exists("wt_conc_summary") && nrow(wt_conc_summary) > 0) {
  summary_items <- rbind(summary_items,
    wt_conc_summary %>%
      mutate(`Mean (SD)` = sprintf("%.1f%% (%.1f%%)", Mean*100, SD*100)) %>%
      dplyr::select(n, Method, `Mean (SD)`) %>%
      mutate(Metric = "Weight Concentration"))
}
if (exists("wt_ratio_summary") && nrow(wt_ratio_summary) > 0) {
  summary_items <- rbind(summary_items,
    wt_ratio_summary %>%
      mutate(`Mean (SD)` = sprintf("%.2f (%.2f)", Mean, SD)) %>%
      dplyr::select(n, Method, `Mean (SD)`) %>%
      mutate(Metric = "Active/Null Weight Ratio"))
}

if (nrow(summary_items) > 0) {
  kable(summary_items %>%
          pivot_wider(names_from = n, values_from = `Mean (SD)`) %>%
          arrange(Metric, Method),
        caption = "Consolidated Performance Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
    collapse_rows(columns = 1, valign = "top")
}
```

---

## SGL-WQS Validation-Stage Group Inference

```{r sglwqs-validation, cache=FALSE}
val_df <- data.frame()

for (res in all_results) {
  if (!is.null(res$sglwqs_group_val)) {
    for (grp_name in names(res$sglwqs_group_val)) {
      gv <- res$sglwqs_group_val[[grp_name]]
      val_df <- rbind(val_df, data.frame(
        n = res$n, Seed = res$seed, Group = grp_name,
        Direction = "Positive",
        Estimate = gv$pos_estimate, SE = gv$pos_se, Pvalue = gv$pos_pvalue))
      val_df <- rbind(val_df, data.frame(
        n = res$n, Seed = res$seed, Group = grp_name,
        Direction = "Negative",
        Estimate = gv$neg_estimate, SE = gv$neg_se, Pvalue = gv$neg_pvalue))
    }
  }
}

if (nrow(val_df) > 0) {
  val_summary <- val_df %>%
    filter(!is.na(Estimate)) %>%
    group_by(n, Group, Direction) %>%
    summarize(
      Median_Est = median(Estimate, na.rm = TRUE),
      IQR_Est = sprintf("[%.3f, %.3f]",
                        quantile(Estimate, 0.25, na.rm = TRUE),
                        quantile(Estimate, 0.75, na.rm = TRUE)),
      Sig_Rate = sprintf("%d/%d", sum(Pvalue < 0.05, na.rm = TRUE), n()),
      .groups = "drop"
    ) %>%
    mutate(Summary = paste0(round(Median_Est, 3), " ", IQR_Est, " (", Sig_Rate, ")"))

  kable(val_summary %>%
          mutate(GroupDir = paste0(Group, " (", Direction, ")")) %>%
          dplyr::select(n, GroupDir, Summary) %>%
          pivot_wider(names_from = n, values_from = Summary),
        caption = "SGL-WQS Validation-Stage Inference: Median [IQR] (sig/total)") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
} else {
  cat("No validation-stage group results available.\n")
}
```

## SGL-WQS Selection Frequency Analysis

```{r sel-freq-samplesize, fig.height=10, fig.width=16, cache=FALSE}
sel_freq_df <- data.frame()
for (res in all_results) {
  if (!is.null(res$sglwqs_sel_freq_pos) && !is.null(res$sglwqs_sel_freq_neg)) {
    sf_pos <- res$sglwqs_sel_freq_pos
    sf_neg <- res$sglwqs_sel_freq_neg
    for (v in all_exposures) {
      sp <- if (v %in% names(sf_pos)) sf_pos[v] else 0
      sn <- if (v %in% names(sf_neg)) sf_neg[v] else 0
      sel_freq_df <- rbind(sel_freq_df, data.frame(
        Variable = v, n = res$n, Seed = res$seed,
        SelFreq_Pos = sp, SelFreq_Neg = sn,
        SelFreq_Max = max(sp, sn)))
    }
  }
}

if (nrow(sel_freq_df) > 0) {
  sel_freq_df <- sel_freq_df %>%
    mutate(IsActive = Variable %in% active_vars)

  # Stable Selection Rate by sample size
  ss_by_n <- sel_freq_df %>%
    mutate(StablySelected = SelFreq_Max > 0.5) %>%
    group_by(n, Seed, IsActive) %>%
    summarize(Rate = mean(StablySelected), .groups = "drop") %>%
    group_by(n, IsActive) %>%
    summarize(Mean = mean(Rate), SD = sd(Rate), .groups = "drop")

  p1 <- ggplot(ss_by_n, aes(x = factor(n), y = Mean, fill = IsActive)) +
    geom_col(position = position_dodge(width = 0.7), width = 0.6) +
    geom_errorbar(aes(ymin = pmax(Mean - SD, 0), ymax = pmin(Mean + SD, 1)),
                  position = position_dodge(width = 0.7), width = 0.2) +
    scale_fill_manual(values = c("FALSE" = "gray60", "TRUE" = "#D73027"),
                      labels = c("Null", "Active")) +
    scale_y_continuous(labels = scales::percent) +
    labs(title = paste0("SGL-WQS Stable Selection Rate by Sample Size (", N_SEEDS, " seeds)"),
         subtitle = "Selected in >50% of bootstraps",
         x = "Sample Size", y = "Stable Selection Rate", fill = NULL) +
    theme_minimal() + theme(legend.position = "bottom")
  print(p1)

  kable(ss_by_n %>%
          mutate(Status = ifelse(IsActive, "Active", "Null"),
                 `Mean (SD)` = sprintf("%.1f%% (%.1f%%)", Mean*100, SD*100)) %>%
          dplyr::select(n, Status, `Mean (SD)`) %>%
          pivot_wider(names_from = Status, values_from = `Mean (SD)`),
        caption = "Stable Selection Rate: Active vs Null") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

  # Selection-Weighted Concentration by sample size
  sgl_wt <- all_wt %>% filter(Method == "SGL-WQS")
  if (nrow(sgl_wt) > 0) {
    sgl_max <- sgl_wt %>%
      group_by(n, Seed, Variable) %>%
      summarize(MaxWeight = max(Weight, na.rm = TRUE), .groups = "drop")

    sw_conc <- sgl_max %>%
      left_join(sel_freq_df %>%
                  group_by(n, Seed, Variable) %>%
                  summarize(SelFreq = mean(SelFreq_Max), .groups = "drop"),
                by = c("n", "Seed", "Variable")) %>%
      mutate(SelFreq = ifelse(is.na(SelFreq), 0, SelFreq),
             AdjWeight = MaxWeight * SelFreq,
             IsActive = Variable %in% active_vars) %>%
      group_by(n, Seed, IsActive) %>%
      summarize(TotalAdjWeight = sum(AdjWeight, na.rm = TRUE), .groups = "drop") %>%
      pivot_wider(names_from = IsActive, values_from = TotalAdjWeight,
                  names_prefix = "Active_") %>%
      mutate(SelWtConc = Active_TRUE / (Active_TRUE + Active_FALSE))

    sw_conc_summary <- sw_conc %>%
      group_by(n) %>%
      summarize(Mean = mean(SelWtConc, na.rm = TRUE),
                SD = sd(SelWtConc, na.rm = TRUE), .groups = "drop")

    raw_conc <- wt_conc_summary %>% filter(Method == "SGL-WQS")

    comparison <- raw_conc %>%
      dplyr::select(n, Raw_Mean = Mean, Raw_SD = SD) %>%
      left_join(sw_conc_summary %>% rename(SelWt_Mean = Mean, SelWt_SD = SD), by = "n")

    kable(comparison %>%
            mutate(Raw = sprintf("%.1f%% (%.1f%%)", Raw_Mean*100, Raw_SD*100),
                   `Selection-Weighted` = sprintf("%.1f%% (%.1f%%)", SelWt_Mean*100, SelWt_SD*100)) %>%
            dplyr::select(n, Raw, `Selection-Weighted`),
          caption = sprintf("SGL-WQS Weight Concentration: Raw vs Selection-Weighted (chance=%.1f%%)",
                            chance_level*100)) %>%
      kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
  }

  # Heatmap
  sf_heat <- sel_freq_df %>%
    left_join(true_directions %>% dplyr::select(Variable, True_Beta, Group), by = "Variable") %>%
    group_by(Variable, n, Group) %>%
    summarize(MeanSelFreq = mean(SelFreq_Max, na.rm = TRUE), .groups = "drop")

  var_order <- true_directions %>%
    arrange(Group, desc(abs(True_Beta))) %>% pull(Variable)
  sf_heat$Variable <- factor(sf_heat$Variable, levels = rev(var_order))

  p2 <- ggplot(sf_heat, aes(x = factor(n), y = Variable, fill = MeanSelFreq)) +
    geom_tile(color = "white", linewidth = 0.3) +
    scale_fill_gradient2(low = "white", mid = "#FDD49E", high = "#D73027",
                         midpoint = 0.5, limits = c(0, 1), name = "Selection\nFrequency") +
    labs(title = paste0("SGL-WQS Bootstrap Selection Frequency (", N_SEEDS, " seeds)"),
         x = "Sample Size", y = NULL) +
    theme_minimal() + theme(axis.text.y = element_text(size = 7), panel.grid = element_blank())
  print(p2)

  ggsave(file.path(fig_dir, "Fig_size_sglwqs_stable_selection.pdf"), p1,
         width = 180, height = 100, units = "mm", dpi = 300)
  ggsave(file.path(fig_dir, "Fig_size_sglwqs_selection_freq_heatmap.pdf"), p2,
         width = 180, height = 180, units = "mm", dpi = 300)
} else {
  cat("No selection frequency data. Re-run with updated SGL-WQS collection code.\n")
}
```

---

# Session Info

```{r session-info}
sessionInfo()
```
