---
title: "SGL-WQS Analysis with Complete Data"
subtitle: "Large-Scale Simulation Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SGL-WQS Analysis with Complete Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  comment = "#>", 
  eval = TRUE,
  fig.width = 10,
  fig.height = 7,
  out.width = "100%",
  dpi = 150
)

# Publication figure output directory
fig_dir <- "figures"
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)
```

## Overview

This vignette demonstrates SGL-WQS analysis with large-scale data (n=100,000) having **known true effects** in this simulation:

- **PCBs**: Positive effect
- **Metals**: Positive/Negative effect
- **PFASs**: No effect

## Simulation Data

```{r generate-data}
library(MASS); library(tictoc); library(tidyverse)

generate_sglwqs_simdata <- function(n = 100000, seed = 71) {
  set.seed(seed)
  
  # Covariates
  sex <- rbinom(n, 1, 0.5)
  age <- pmax(pmin(round(rnorm(n, 50, 12)), 80), 20)
  bmi <- pmax(pmin(round(22 + 0.05*age + 1.5*sex + rnorm(n, 0, 4), 1), 45), 15)
  
  # PCBs (positive effect, high correlation)
  # Updated to 5 congeners to match Robustness Test (added pcb_118)
  cor_pcb <- matrix(c(1.00, 0.60, 0.70, 0.65, 0.60,  # pcb_118 (new)
                      0.60, 1.00, 0.75, 0.70, 0.65,  # pcb_138
                      0.70, 0.75, 1.00, 0.80, 0.70,  # pcb_153
                      0.65, 0.70, 0.80, 1.00, 0.75,  # pcb_180
                      0.60, 0.65, 0.70, 0.75, 1.00), # pcb_187
                    5, 5)
                    
  pcb <- MASS::mvrnorm(n, c(3.5, 3.5, 4.0, 4.5, 3.0), 
                       diag(c(1.5, 1.5, 1.8, 2.0, 1.5)) %*% cor_pcb %*% diag(c(1.5, 1.5, 1.8, 2.0, 1.5)))
  colnames(pcb) <- c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187")
  
  # Metals (mixed effect, moderate correlation)
  cor_metal <- matrix(c(1, .4, .5, .3, .3,
                        .4, 1, .4, .2, .2,
                        .5, .4, 1, .3, .2,
                        .3, .2, .3, 1, .1,
                        .3, .2, .2, .1, 1), 5, 5)
  metal_raw <- MASS::mvrnorm(n, log(c(0.5, 2, 1, 100, 20)), 
                             diag(c(.6, .8, .5, .3, .25)) %*% cor_metal %*% diag(c(.6, .8, .5, .3, .25)))
  metal <- exp(metal_raw)
  colnames(metal) <- c("cd", "pb", "hg", "se", "mg")
  
  # PFASs (no effect, low correlation)
  cor_pfas <- matrix(c(1, .3, .3,
                       .3, 1, .3,
                       .3, .3, 1), 3, 3)
  pfas_raw <- MASS::mvrnorm(n, log(c(2, 0.5, 5)), 
                            diag(c(.4, .5, .6)) %*% cor_pfas %*% diag(c(.4, .5, .6)))
  pfas <- exp(pfas_raw)
  colnames(pfas) <- c("PFOA", "PFNA", "PFOS")
  
  # Data Frame
  X <- cbind(pcb, metal, pfas)
  covariates <- data.frame(sex = sex, age = age, bmi = bmi)
  
  # True Effects (Log-Odds)
  # pcb_118 has 0 effect (innocent bystander) to maintain similar theoretical results
  beta_pcb <- c(0.04, 0.10, 0.20, 0.03, 0.02)  # 118, 138, 153, 180, 187
  beta_metal <- c(-0.08, -0.18, 0.05, 0.10, 0.00) # cd, pb, hg, se, mg
  beta_pfas <- c(0, 0, 0)
  beta_cov <- c(0.2, 0.01, 0.02) # sex, age, bmi
  
  # Linear Predictor
  # Standardize X for generation to match beta scale roughly
  X_sc <- scale(X)
  
  lp <- -3 + 
    X_sc[, 1:5] %*% beta_pcb + 
    X_sc[, 6:10] %*% beta_metal + 
    X_sc[, 11:13] %*% beta_pfas +
    as.matrix(covariates) %*% beta_cov
  
  # Probability & Outcome
  prob <- 1 / (1 + exp(-lp))
  Y <- rbinom(n, 1, prob)
  
  result <- data.frame(Y = Y, covariates, pcb, metal, pfas)
  
  attr(result, "true_beta") <- list(
    pcb = setNames(beta_pcb, colnames(pcb)),
    metal = setNames(beta_metal, colnames(metal)),
    pfas = setNames(beta_pfas, colnames(pfas))
  )
  
  return(result)
}

simdata <- generate_sglwqs_simdata(n = 100000, seed = 71)
```

## SGL-WQS Analysis

```{r analysis}
library(sglwqs)
library(future)

groups <- list(
  PCBs = c("pcb_118", "pcb_138", "pcb_153", "pcb_180", "pcb_187"),
  Metals = c("cd", "pb", "hg", "se", "mg"),
  PFASs = c("PFOA", "PFNA", "PFOS")
)

tic()
plan(multisession, workers = 10)


fit <- sglwqs(
  X = simdata[, unlist(groups)],
  y = simdata$Y,
  covariates = simdata[, c("sex", "age", "bmi")],
  groups = groups,
  family = "binomial",
  bootstrap = TRUE,
  n_boot = 200,
  parallel = TRUE,
  validation = TRUE,
  train_prop = 0.6,
  seed = 71
)


plan(sequential)
toc()
```

## Results

```{r results}
# Summary
summary(fit)

# Publication-ready table
inference_table(fit)
```

```{r results-plot, fig.height=9}
# Weight visualization
p_weights <- plot_weights(fit)
print(p_weights)

# Publication output (180mm = 2-column, 220mm height for 13 vars × 3 groups)
ggsave(file.path(fig_dir, "Fig_sglwqs_weights.pdf"), p_weights,
       width = 180, height = 220, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_sglwqs_weights.tiff"), p_weights,
       width = 180, height = 220, units = "mm", dpi = 300, compression = "lzw")
```

```{r combined-plot, fig.width=12, fig.height=10}
# Combined visualization
p_combined <- plot_combined_results(fit)
print(p_combined)

# Publication output (180mm × 180mm, 2-column full-width)
ggsave(file.path(fig_dir, "Fig_sglwqs_combined.pdf"), p_combined,
       width = 180, height = 180, units = "mm", dpi = 300)
ggsave(file.path(fig_dir, "Fig_sglwqs_combined.tiff"), p_combined,
       width = 180, height = 180, units = "mm", dpi = 300, compression = "lzw")
```

## Expected Findings

| Group | Direction | Expected Result |
|-------|-----------|-----------------|
| PCBs | Positive | Significant (p < 0.05) |
| Metals (Hg, Se) | Positive | Significant (p < 0.05) |
| Metals (Pb, Cd) | Negative | Significant (p < 0.05) |
| PFASs | Either | Not significant |

The method correctly identifies which chemicals have positive, negative, or no effects.
